### 2021-07-12 Solent Mapping_v2.Rmd
initial commit

title: "Test Maps"
author: Meghan Kinglsey-Walsh
date: 'Last run at: 'r Sys.time()''
output:
output:
  pdf_document: default
  html_document: default
  word_document: default

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(sf)
library(spData)
library(spDataLarge)
library(dplyr)
dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/"
```

##Examine World Dataset
```{r Mapping population of the world (using ggplot2)}
head(world)
library(ggplot2)
ggplot2::ggplot(world)+
  geom_sf(aes(fill = pop))#draws blue map
ggplot2::ggplot(world) + 
  geom_sf(aes(fill = pop/1000000)) +
  scale_fill_continuous(name="Population (millions)",
                        low = "green",
                        high = "red") #changing colours

```

##Mapping the Local Authority
###Mapping Domestic

####Mapping the Electricity Consumption
```{r loading in Local Authority electricity consumption data}
library(readr)
inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
la_elecData <- readr::read_csv(inFile)
summary(la_elecData)

```
```{r Loading in the Boundary Data for local authorities we are intrested in}
geo_query <- "https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Local_Authority_Districts_December_2018_Boundaries_UK_BGC/MapServer/0/query?where=lad18nm%20IN%20(%27Southampton%27,%27Portsmouth%27,%27Winchester%27,%27Eastleigh%27,%27Isle%20of%20Wight%27,%27Fareham%27,%27Gosport%27,%27Test%20Valley%27,%27East%20Hampshire%27,%27Havant%27,%27New%20Forest%27,%27Hart%27,%27Basingstoke%20and%20Deane%27)&outFields=lad18cd,lad18nm,long,lat&outSR=4326&f=geojson"
#This only includes the ones we are interested in i.e the Solent
message("Loading LA geometry from ONS Open Geography API") #Specifying the location message
la_sf_data <- sf::st_read(geo_query)
head(la_sf_data)
```
```{r Mapping the local authority electricty consumption}
library(ggplot2)
la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
la_merged_sf <- merge(la_sf_data, la_elecData)#Merge the local Authority boundaries and the consumption data
ggplot2::ggplot(la_merged_sf) +
  geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")

```
###Mapping Transport
```{r Loading the Transport consumption data}

```

##Mapping the Middle Layer Super Output Areas (MSOA)
###Mapping Domestic
####Mapping the Electricity Consumption
```{r Loading in the MSOA electricity consumption data}
# electricity consumption data at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_DOM_ELEC_2019.csv")
msoa_elecData <- readr::read_csv(inFile)
head(msoa_elecData)
```

```{r Loading in the Boundary Data for the MSOA}
inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
message("Loading Middle Layer Super Output Area (MSOA) from the ONS Open Georgraphy API")
#When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
msoa_sf_data <- sf::read_sf(inf) 
head (msoa_sf_data)
table(msoa_sf_data$LAD11NM)#how many MSOAs are in each LA
```
```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```

##Mapping the Lower Layer Super Output Area (LSOA)
###mapping Domestic
####Mapping Electricity consumption
```{r Loading in the LSOA electricty consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
lsoa_elecData <- readr::read_csv(inFile)
lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
head(msoa_elecData)
```

```{r Loading in boundary data for the LSOA}
#The LSOA boundaries for the Solent have been pre-downloaded
inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
message ("Loading LSOA boundaries from ONS Open geography API")
lsoa_sf_data <- sf::read_sf(inf)
head(lsoa_sf_data)
table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
```
```{r Mapping the electricty consumption of the LSOAs}
lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
ggplot2::ggplot(lsoa_merged_sf) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all LSOAs)")
#Mapping it
```
#####Looking at cities in more detail
```{r Looking at the cities in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
library(dplyr) # for filter, had to install this package
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")

# plotting the elctricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```

###Mapping the Indices of Multiple Deprivation (JUST PLACE HOLDER DOESN'T WORK)
```{r Loading in the Indices of Multiple Deprivation data}
# Multiple deprivation data at MSOA pre downloaded
inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
lsoa_multidep <- readr::read_csv (inFile)
head(lsoa_multidep)
```
```{r Mapping the Indices of deprevation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf)+geom_sf(aes(fill=IMDScore))+scale_fill_continuous(name="(Text)IMDScore", low="green",high="red")+labs(caption ="Solent (all MSOAs)")
```

### 2021-07-14 Solent Mapping_v2.Rmd
lastest edits - added transport: freight & personal travel

@@
 ###Mapping Domestic
-
 ####Mapping the Electricity Consumption
@@
 summary(la_elecData)
-
 ```
@@
 ###Mapping Transport
-```{r Loading the Transport consumption data}
-
+####Freight
+```{r Loading the  Freight Transport consumption data for the Local Autority}
+inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
+la_Transport <- readr::read_csv(inFile)
+summary(la_Transport)
+head(la_Transport)
+```
+```{r Mapping the local authority electricty consumption (Freight)}
+library(ggplot2)
+la_Transport$lad18cd <- la_Transport$`Freight`#Creating a variable with the local authority code in the same name of the consumption data
+la_merged_Transp <- merge(la_sf_data, la_Transport)#Merge the local Authority boundaries and the Transport data
+ggplot2::ggplot(la_merged_sf) +
+  geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")
+```
+####Personal
+```{r Mapping the local authority electricty consumption (Personal)}
+library(ggplot2)
+la_Transport$lad18cd <- la_Transport$`Personal`#Creating a variable with the local authority code in the same name of the consumption data
+la_merged_Transp <- merge(la_sf_data, la_Transport)#Merge the local Authority boundaries and the Transport data
+ggplot2::ggplot(la_merged_sf) +
+  geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")  
 ```
@@
 ```
+####Mapping the Gas
+```{r Loading in the MSOA gas consumption data}
+# gas consumption data at MSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_GAs_2019.csv")
+msoa_gasData <- readr::read_csv(inFile)
+head(msoa_gasData)
+```
+```{r Mapping the gas consumption of the MSOAs}
+msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
+ggplot2::ggplot(msoa_merged_sf_domgas) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all MSOAs)")
+#mapping it
+```
+
+###Mapping Commercial
+####Mapping Electricty
+```{r Loading in the MSOA electricity consumption data for industry }
+# electricity consumption data for industry at MSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
+msoa_elecDatanondom <- readr::read_csv(inFile)
+head(msoa_elecDatanondom)
+```
+
+```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
+msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
+ggplot2::ggplot(msoa_merged_sf_nondom) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all MSOAs)")
+#mapping it
+```
+####Mapping Gas
+```{r Loading in the MSOA gas consumption data for industry }
+# gas consumption data for industry at MSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
+msoa_gasDatanondom <- readr::read_csv(inFile)
+head(msoa_gasDatanondom)
+```
+```{r Mapping the gas consumption of the MSOAs Industrial Sector}
+msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
+ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all MSOAs)")
+#mapping it
+```
 
 ##Mapping the Lower Layer Super Output Area (LSOA)
-###mapping Domestic
+###Mapping Domestic
 ####Mapping Electricity consumption
@@
 ```
+####Mapping Gas
+```{r Loading in the LSOA gas consumption data}
+#Electricty consumption data LSOA pre downloaded
+inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
+lsoa_gasData <- readr::read_csv(inFile)
+lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
+head(lsoa_gasData)
+```
 
-###Mapping the Indices of Multiple Deprivation (JUST PLACE HOLDER DOESN'T WORK)
+```{r Mapping the gas consumption of the LSOAs}
+lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
+ggplot2::ggplot(lsoa_merged_sf_gas) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all LSOAs)")
+#Mapping it
+```
+
+###Mapping Industrial
+####Mapping Electricity consumption
+```{r Loading in the LSOA electricity consumption data for industry }
+# electricity consumption data for industry at LSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
+msoa_elecDatanondom <- readr::read_csv(inFile)
+head(msoa_elecDatanondom)
+```
+
+###Mapping the Indices of Multiple Deprivation
 ```{r Loading in the Indices of Multiple Deprivation data}

### 2021-07-14 Solent Mapping_v2.Rmd
fixed yaml headers (now uses bookdown for floating ToC etc); fixed dataFolder for different platforms; checked maps plot what we think they do (some didn't); re-run

--- 2021-07-12 Solent Mapping_v2.Rmd
@@
+---
 title: "Test Maps"
-author: Meghan Kinglsey-Walsh
-date: 'Last run at: 'r Sys.time()''
+author: "Meghan Kinglsey-Walsh"
+date: 'Last run at: `r Sys.time()`'
 output:
-output:
-  pdf_document: default
-  html_document: default
-  word_document: default
+  bookdown::html_document2:
+    fig_caption: yes
+    code_folding: hide
+    number_sections: yes
+    toc: yes
+    toc_depth: 4
+    toc_float: TRUE
+  bookdown::pdf_document2:
+    toc: yes
+    fig_caption: yes
+    number_sections: yes
+  bookdown::word_document2: 
+    fig_caption: yes
+    number_sections: yes
+    toc: yes
+    toc_depth: 4
+    fig_width: 5
+---
 
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE) # set this to FALSE if you don't want the code in the final oputput
+
+# useful R libraries
+library(ggplot2)
+library(readr)
+library(dplyr)
+
+# GIS libraries
 library(raster)
@@
 library(spDataLarge)
-library(dplyr)
-dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/"
+
+dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/" # default for Meghan
+user <- Sys.info()[[7]] # who are we logged in as?
+if(user == "ben"){
+  dataFolder <- path.expand("~/University of Southampton/HCC Energy Landscape Mapping project - Documents/General/data/")
+}
+
+# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
+message("User: ", user)
+message("dataFolder: ", dataFolder)
 ```
 
-##Examine World Dataset
-```{r Mapping population of the world (using ggplot2)}
-head(world)
-library(ggplot2)
-ggplot2::ggplot(world)+
-  geom_sf(aes(fill = pop))#draws blue map
-ggplot2::ggplot(world) + 
-  geom_sf(aes(fill = pop/1000000)) +
-  scale_fill_continuous(name="Population (millions)",
-                        low = "green",
-                        high = "red") #changing colours
+## Mapping the Local Authority
 
-```
+### Mapping Domestic
 
-##Mapping the Local Authority
-###Mapping Domestic
+#### Mapping Electricity Consumption
 
-####Mapping the Electricity Consumption
 ```{r loading in Local Authority electricity consumption data}
-library(readr)
 inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
@@
 summary(la_elecData)
+```
 
-```
 ```{r Loading in the Boundary Data for local authorities we are intrested in}
-geo_query <- "https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Local_Authority_Districts_December_2018_Boundaries_UK_BGC/MapServer/0/query?where=lad18nm%20IN%20(%27Southampton%27,%27Portsmouth%27,%27Winchester%27,%27Eastleigh%27,%27Isle%20of%20Wight%27,%27Fareham%27,%27Gosport%27,%27Test%20Valley%27,%27East%20Hampshire%27,%27Havant%27,%27New%20Forest%27,%27Hart%27,%27Basingstoke%20and%20Deane%27)&outFields=lad18cd,lad18nm,long,lat&outSR=4326&f=geojson"
-#This only includes the ones we are interested in i.e the Solent
-message("Loading LA geometry from ONS Open Geography API") #Specifying the location message
-la_sf_data <- sf::st_read(geo_query)
+# geo_query <- "https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Local_Authority_Districts_December_2018_Boundaries_UK_BGC/MapServer/0/query?where=lad18nm%20IN%20(%27Southampton%27,%27Portsmouth%27,%27Winchester%27,%27Eastleigh%27,%27Isle%20of%20Wight%27,%27Fareham%27,%27Gosport%27,%27Test%20Valley%27,%27East%20Hampshire%27,%27Havant%27,%27New%20Forest%27,%27Hart%27,%27Basingstoke%20and%20Deane%27)&outFields=lad18cd,lad18nm,long,lat&outSR=4326&f=geojson"
+# #This only includes the ones we are interested in i.e the Solent
+# message("Loading LA geometry from ONS Open Geography API") #Specifying the location message
+# la_sf_data <- sf::st_read(geo_query)
+
+# The above is very clever but it takes time
+# Load from file
+la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
+la_sf_data <- sf::st_read(la_shpFile)
 head(la_sf_data)
 ```
+
 ```{r Mapping the local authority electricty consumption}
-library(ggplot2)
 la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
@@
 ```
-###Mapping Transport
-```{r Loading the Transport consumption data}
 
+### Mapping Transport
+
+#### Freight
+```{r Loading the  Freight Transport consumption data for the Local Autority}
+inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
+la_Transport <- readr::read_csv(inFile)
+summary(la_Transport)
+head(la_Transport)
 ```
 
-##Mapping the Middle Layer Super Output Areas (MSOA)
-###Mapping Domestic
-####Mapping the Electricity Consumption
+```{r Mapping the local authority energy consumption (Freight)}
+
+la_Transport$lad18cd <- la_Transport$Code # Creating a variable with the local authority code in the same name of the consumption data
+la_merged_Transp <- merge(la_sf_data, la_Transport)# Merge the local Authority boundaries and the Transport data
+ggplot2::ggplot(la_merged_Transp) +
+  geom_sf(aes(fill = Freight)) +
+  scale_fill_gradient(name = "Freight: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red")
+```
+
+#### Personal
+
+Note: this data is not per household/person so it will correlate (to some extent) with population size.
+
+```{r Mapping the local authority energy consumption (Personal)}
+# re-use the merged dataset
+ggplot2::ggplot(la_merged_Transp) +
+  geom_sf(aes(fill = Personal)) +
+  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
+```
+
+## Mapping the Middle Layer Super Output Areas (MSOA)
+
+### Mapping Domestic
+
+#### Mapping the Electricity Consumption
+
 ```{r Loading in the MSOA electricity consumption data}
@@
 inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
-message("Loading Middle Layer Super Output Area (MSOA) from the ONS Open Georgraphy API")
+message("Loading Middle Layer Super Output Area (MSOA) from file")
 #When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
@@
 ```
+
 ```{r Mapping the electrcity consumption of the MSOAs}
@@
   geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
   labs(caption = "Solent (all MSOAs)")
@@
 
-##Mapping the Lower Layer Super Output Area (LSOA)
-###mapping Domestic
-####Mapping Electricity consumption
+#### Mapping the Gas
+```{r Loading in the MSOA gas consumption data}
+# gas consumption data at MSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
+msoa_gasData <- readr::read_csv(inFile)
+head(msoa_gasData)
+```
+```{r Mapping the gas consumption of the MSOAs}
+msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
+ggplot2::ggplot(msoa_merged_sf_domgas) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all MSOAs)")
+#mapping it
+```
+> Does this match to non-gas areas??
+
+### Mapping Commercial
+#### Mapping Electricty
+```{r Loading in the MSOA electricity consumption data for industry }
+# electricity consumption data for industry at MSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
+msoa_elecDatanondom <- readr::read_csv(inFile)
+head(msoa_elecDatanondom)
+```
+
+```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
+msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
+ggplot2::ggplot(msoa_merged_sf_nondom) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all MSOAs)")
+#mapping it
+```
+#### Mapping Gas
+
+```{r Loading in the MSOA gas consumption data for industry }
+# gas consumption data for industry at MSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
+msoa_gasDatanondom <- readr::read_csv(inFile)
+head(msoa_gasDatanondom)
+```
+
+```{r Mapping the gas consumption of the MSOAs Industrial Sector}
+msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
+ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all MSOAs)")
+#mapping it
+```
+> The holes tell you where there is no non-domestic gas use
+
+## Mapping the Lower Layer Super Output Area (LSOA)
+
+### Mapping Domestic
+
+#### Mapping Electricity consumption
 ```{r Loading in the LSOA electricty consumption data}
@@
 inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
-message ("Loading LSOA boundaries from ONS Open geography API")
+message ("Loading LSOA boundaries from file")
 lsoa_sf_data <- sf::read_sf(inf)
@@
 ```
+
 ```{r Mapping the electricty consumption of the LSOAs}
@@
 ```
-#####Looking at cities in more detail
+
+##### Looking at cities in more detail
 ```{r Looking at the cities in more detail}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-library(dplyr) # for filter, had to install this package
 mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
 
-# plotting the elctricity consumption of Southampton in more detail
+# plotting the electricity consumption of Southampton in more detail
 ggplot2::ggplot(mapData) + 
@@
 
-###Mapping the Indices of Multiple Deprivation (JUST PLACE HOLDER DOESN'T WORK)
+#### Mapping Gas
+
+```{r Loading in the LSOA gas consumption data}
+#Electricty consumption data LSOA pre downloaded
+inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
+lsoa_gasData <- readr::read_csv(inFile)
+lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
+head(lsoa_gasData)
+```
+
+```{r Mapping the gas consumption of the LSOAs}
+lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
+ggplot2::ggplot(lsoa_merged_sf_gas) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Solent (all LSOAs)")
+#Mapping it
+```
+
+> Aha - this one shows where there is no gas :-)
+
+### Mapping Industrial
+#### Mapping Electricity consumption
+
+> didn't we already do this in the MSOA section?
+
+```{r Loading in the LSOA electricity consumption data for industry }
+# electricity consumption data for industry at LSOA level (pre downloaded)
+inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
+msoa_elecDatanondom <- readr::read_csv(inFile)
+head(msoa_elecDatanondom)
+```
+
+### Mapping the Indices of Multiple Deprivation
+
 ```{r Loading in the Indices of Multiple Deprivation data}
@@
 ```
-```{r Mapping the Indices of deprevation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LA code in the same name as in sf_data
+
+```{r Mapping the Indices of deprivation for the LSOA}
+lsoa_multidep$LSOA11CD <- lsoa_multidep$`LSOA code (2011)` #creating a variable with the LSOA code in the same name as in sf_data
 head(lsoa_multidep)
 lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf)+geom_sf(aes(fill=IMDScore))+scale_fill_continuous(name="(Text)IMDScore", low="green",high="red")+labs(caption ="Solent (all MSOAs)")
+ggplot2::ggplot(lsoa_multidep_merged_sf) +
+  geom_sf(aes(fill=`Index of Multiple Deprivation (IMD) Rank`))+ # which data set has the scores?
+  scale_fill_continuous(name="IMD Rank", low="green",high="red")+
+  labs(caption ="Solent (all MSOAs)")
 ```
+
+# The end
+
+```{r environment}
+R.Version()
+
+```

### 2021-07-14 Solent Mapping_v2.Rmd
fixed heading structure

@@
 
-## Mapping the Local Authority
+# Mapping the Local Authority
 
-### Mapping Domestic
-
-#### Mapping Electricity Consumption
+## Mapping Domestic Electricity Consumption
 
@@
 
-### Mapping Transport
+## Mapping Transport
 
@@
 
-## Mapping the Middle Layer Super Output Areas (MSOA)
+# Mapping the Middle Layer Super Output Areas (MSOA)
 
-### Mapping Domestic
+## Mapping Domestic
 
-#### Mapping the Electricity Consumption
+### Mapping the Electricity Consumption
 
@@
 
-#### Mapping the Gas
+### Mapping the Gas
 ```{r Loading in the MSOA gas consumption data}
@@
 
-### Mapping Commercial
-#### Mapping Electricty
+## Mapping Commercial
+### Mapping Electricty
 ```{r Loading in the MSOA electricity consumption data for industry }
@@
 ```
-#### Mapping Gas
+### Mapping Gas
 
@@
 
-## Mapping the Lower Layer Super Output Area (LSOA)
+# Mapping the Lower Layer Super Output Area (LSOA)
 
-### Mapping Domestic
+## Mapping Domestic
 
-#### Mapping Electricity consumption
+### Mapping Electricity consumption
 ```{r Loading in the LSOA electricty consumption data}
@@
 
-##### Looking at cities in more detail
+#### Looking at cities in more detail
 ```{r Looking at the cities in more detail}
@@
 
-#### Mapping Gas
+### Mapping Gas
 
@@
 
-### Mapping Industrial
-#### Mapping Electricity consumption
-
-> didn't we already do this in the MSOA section?
-
-```{r Loading in the LSOA electricity consumption data for industry }
-# electricity consumption data for industry at LSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
-msoa_elecDatanondom <- readr::read_csv(inFile)
-head(msoa_elecDatanondom)
-```
-
-### Mapping the Indices of Multiple Deprivation
+## Mapping the Indices of Multiple Deprivation
 

### 2021-07-14 Solent_Mapping_v2.Rmd
fixed file names & re-ran

--- 2021-07-14 Solent Mapping_v2.Rmd
@@
 ---
-title: "Test Maps"
+title: "Solent region: Test Maps"
 author: "Meghan Kinglsey-Walsh"
@@
 ### Mapping Electricity consumption
+
 ```{r Loading in the LSOA electricty consumption data}

### 2021-07-15 Solent_Mapping_v2.Rmd
Changed the titles and varibale names for linking to work

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE) # set this to FALSE if you don't want the code in the final oputput
+knitr::opts_chunk$set(echo = TRUE) # set this to FALSE if you don't want the code in the final output
 
@@
 ```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$`LSOA code (2011)` #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
 head(lsoa_multidep)
@@
 ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`Index of Multiple Deprivation (IMD) Rank`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Rank", low="green",high="red")+
+  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
+  scale_fill_continuous(name="IMD Score", low="green",high="red")+
   labs(caption ="Solent (all MSOAs)")

### 2021-07-16 Solent_Mapping_v2.Rmd
Mapping the fuel poverty for LA and LSOA added however there is a "Error: Discrete value supplied to continuous scale"

@@
   scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
+```
+## Mapping Fuel Poverty 
+###2021 Proportion of Population
+```{r Loading in the 2021 Local Authority Fuel Poverty Data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2021 LA_Fuel_Poverty.csv")
+la_fuelpov_2021<-readr::read_csv(inFile)
+head(la_fuelpov_2021)
+```
+```{r Mapping Local Authority Fuel Poverty 2021}
+la_fuelpov_2021$lad18cd <- la_Transport$"Area Codes" # Creating a variable with the local authority code in the same name 
+la_merged_Fuelpov2021 <- merge(la_sf_data, la_fuelpov_2021)# Merge the local Authority boundaries and the Fuel Poverty data
+ggplot2::ggplot(la_merged_Fuelpov2021) +
+  geom_sf(aes(fill = "Proportion of households fuel poor (%)")) +
+  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
 ```
@@
 
-## Mapping the Indices of Multiple Deprivation
+### Mapping the Indices of Multiple Deprivation
 
@@
 ```
+###Mapping Fuel Poverty
+####2021 Fuel Poverty
+```{r Loading in the LSOA 2021 Fuel Poverty data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
+lsoa_fuelpov_2021<-readr::read_csv (inFile)
+head(lsoa_fuelpov_2021)
+```
+```{r Mapping the LSOA 2021 Fuel Poverty}
+lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
+ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
+  geom_sf(aes(fill="Proportion of households fuel poor (%)"))+ # which data set has the scores?
+  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
+  labs(caption ="Solent (all LSOAs)")
+```
+```
 

### 2021-07-16 Solent_Mapping_v2.Rmd
fixed error caused by importing a variable/column as a character

--- 2021-07-15 Solent_Mapping_v2.Rmd
@@
   scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
+```
+## Mapping Fuel Poverty 
+### 2021 Proportion of Population
+
+```{r Loading in the 2021 Local Authority Fuel Poverty Data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2021 LA_Fuel_Poverty.csv")
+la_fuelpov_2021<-readr::read_csv(inFile)
+head(la_fuelpov_2021)
+```
+```{r Mapping Local Authority Fuel Poverty 2021}
+la_fuelpov_2021$lad18cd <- la_fuelpov_2021$`Area Codes` # Creating a variable with the local authority code in the same name 
+la_merged_Fuelpov2021 <- merge(la_sf_data, la_fuelpov_2021)# Merge the local Authority boundaries and the Fuel Poverty data
+la_merged_Fuelpov2021$pcFP <- as.numeric(la_merged_Fuelpov2021$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+ggplot2::ggplot(la_merged_Fuelpov2021) +
+  geom_sf(aes(fill = pcFP)) +
+  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
 ```
@@
 
+### Mapping Fuel Poverty
+#### 2021 Fuel Poverty
+```{r Loading in the LSOA 2021 Fuel Poverty data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
+lsoa_fuelpov_2021<-readr::read_csv (inFile)
+head(lsoa_fuelpov_2021)
+```
+
+```{r Mapping the LSOA 2021 Fuel Poverty}
+lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
+# as above - why does it load as a char?
+lsoa_fuelpov_2021_merged$pcFP <- as.numeric(lsoa_fuelpov_2021_merged$`Proportion of households fuel poor (%)`)
+ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
+  geom_sf(aes(fill=pcFP))+ 
+  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
+  labs(caption ="Solent (all LSOAs)")
+```
+
 # The end

### 2021-07-21 Solent_Mapping_v2.Rmd
Changing the year for the fuel poverty to 2019 to reflect what the data is

--- 2021-07-15 Solent_Mapping_v2.Rmd
@@
 ```
+## Mapping Fuel Poverty 
+### 2019 Proportion of Population
+
+```{r Loading in the 2019 Local Authority Fuel Poverty Data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
+la_fuelpov_2019<-readr::read_csv(inFile)
+head(la_fuelpov_2019)
+```
+```{r Mapping Local Authority Fuel Poverty 2021}
+la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
+la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
+la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+ggplot2::ggplot(la_merged_Fuelpov2019) +
+  geom_sf(aes(fill = pcFP)) +
+  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
+```
+
+### Actual Difference between 2012-2019
+```{r Loading in the difference data}
+#Green indicates a smaller increase in fuel poverty from 2012 to 2019
+#Red indicates an increase in fuel poverty from 2012 to 2019
+```
+
+###Difference in proportion between 2012-2019
 
@@
 
+### Mapping Fuel Poverty
+#### 2019 Fuel Poverty
+```{r Loading in the LSOA 2021 Fuel Poverty data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
+lsoa_fuelpov_2021<-readr::read_csv (inFile)
+head(lsoa_fuelpov_2021)
+```
+
+```{r Mapping the LSOA 2021 Fuel Poverty}
+lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
+# as above - why does it load as a char?
+lsoa_fuelpov_2021_merged$pcFP <- as.numeric(lsoa_fuelpov_2021_merged$`Proportion of households fuel poor (%)`)
+ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
+  geom_sf(aes(fill=pcFP))+ 
+  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
+  labs(caption ="Solent (all LSOAs)")
+```
+
 # The end

### 2021-07-23 mappingSotonEnergyDeprivation.Rmd
added new file (version of the Solent code) to map energy use & deprivation in Southampton only. MNot part of MSc... just borrwoing code :-)

---
title: "Southampton: Mapping Energy Poverty & Deprivation"
author: "Ben Anderson"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # set this to FALSE if you don't want the code in the final output

# useful R libraries
library(ggplot2)
library(readr)
library(dplyr)

# GIS libraries
library(raster)
library(sf)
library(spData)
library(spDataLarge)

dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/" # default for Meghan
user <- Sys.info()[[7]] # who are we logged in as?
if(user == "ben"){
  dataFolder <- path.expand("~/University of Southampton/HCC Energy Landscape Mapping project - Documents/General/data/")
}

# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
message("User: ", user)
message("dataFolder: ", dataFolder)
```

# Intro

Mapping fuel poverty, deprivation & doemstic energy use in Southampton to focus on areas which are high fp & high deprivation.

Based on:

 * [Meghan Kinglsey-Walsh's MSc](https://github.com/dataknut/energyMapping) project code
 * Tom Rushby's [open geography](https://dataknut.github.io/mapping-with-r/ONS-open-geography.html) example.

# Mapping Domestic Electricity consumption (LSOAs)

```{r Loading in the LSOA electricty consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
library(data.table)
lsoa_elecData_dt <- data.table::as.data.table(readr::read_csv(inFile))
lsoa_elecData_dt$LSOA11CD <- lsoa_elecData_dt$`Lower Layer Super Output Area (LSOA) Code`

selectSoton <- function(dt){
  # function we can re-use
  # assumes a data.table
  # assumes LA name = la_name (may need to make new var first)
  select_dt <- dt[la_name %like% "Southampton"]
  return(select_dt)
}

lsoa_elecData_dt$la_name <- lsoa_elecData_dt$`Local Authority Name`
# filter Soton
lsoa_soton_elecData_dt <- selectSoton(lsoa_elecData_dt)

```

```{r Loading in boundary data for the LSOA}
#The LSOA boundaries for the Solent have been pre-downloaded
inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
message ("Loading LSOA boundaries from file")
lsoa_sf_data <- sf::read_sf(inf)
table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
```

Focus on Southampton

```{r Mapping the electricty consumption of the LSOAs}
lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_soton_elecData_dt) #merging the boundaries and energy data
ggplot2::ggplot(lsoa_merged_sf) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all LSOAs)")
#Mapping it
```

# Mapping Domestic Gas (LSOAs)

```{r Loading in the LSOA gas consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
lsoa_gasData_dt <- as.data.table(readr::read_csv(inFile))
lsoa_gasData_dt$LSOA11CD <- lsoa_gasData_dt$`Lower Layer Super Output Area (LSOA) Code`
lsoa_gasData_dt$la_name <- lsoa_gasData_dt$`Local Authority Name`
# filter Soton
lsoa_soton_gas_dt <- selectSoton(lsoa_gasData_dt)
```

```{r Mapping the gas consumption of the LSOAs}
lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_soton_gas_dt) #merging the boundaries and energy data
ggplot2::ggplot(lsoa_merged_sf_gas) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton (all LSOAs)")
#Mapping it
```

> Some areas are very high gas...

### Correlating gas & elecricity

```{r gaselecCorr}
setkey(lsoa_soton_elecData_dt, LSOA11CD)
lsoa_soton_elecData_dt[, meanEleckWh := `Mean domestic electricity consumption \n(kWh per meter)`]
setkey(lsoa_soton_gas_dt, LSOA11CD)
lsoa_soton_gas_dt[, meanGaskWh := `Mean consumption (kWh per meter)`]
dt <- lsoa_soton_elecData_dt[lsoa_soton_gas_dt]
ggplot2::ggplot(dt, aes(x = meanEleckWh, y = meanGaskWh)) +
  geom_point()
```

# Mapping the Indices of Multiple Deprivation (LSOAs)

2019 data

Should be a negative correlation with gas & electricity

```{r Loading in the Indices of Multiple Deprivation data}
# Multiple deprivation data at MSOA pre downloaded
inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
lsoa_multidep_dt <- as.data.table(readr::read_csv (inFile))
lsoa_multidep_dt[, la_name := LADnm]
lsoa_multidepSoton_dt <- selectSoton(lsoa_multidep_dt)
```

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidepSoton_dt$LSOA11CD <- lsoa_multidepSoton_dt$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data

lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidepSoton_dt) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Southampton (all LSOAs)")
```

Check correlations with energy

```{r energyCorrIMD}
setkey(lsoa_multidepSoton_dt, LSOA11CD)
dt <- lsoa_soton_elecData_dt[lsoa_soton_gas_dt][lsoa_multidepSoton_dt]

plotDT <- dt[, .(meanEleckWh, meanGaskWh, IMDScore)]
pairs(plotDT)
```

> Much stronger relationship between mean gas use & IMD score in Southampton

# Mapping Fuel Poverty (LSOAs)

2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019_dt <- as.data.table(readr::read_csv (inFile))
lsoa_fuelpov_2019_dt[, la_name := `LA Name`]
lsoa_fuelpovSoton_2019_dt <- selectSoton(lsoa_fuelpov_2019_dt)
```

```{r Mapping the LSOA 2021 Fuel Poverty}
lsoa_fuelpovSoton_2019_dt[, pcFP := as.numeric(`Proportion of households fuel poor (%)`)]
lsoa_fuelpovSoton_2019_dt[, LSOA11CD := `LSOA Code`] #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpovSoton_2019_dt) #merging these
# as above - why does it load as a char?

ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Southampton (all LSOAs)")
```

# Correlating energy use & fuel poverty/deprivation

Figure \@ref(fig:energyCorrAll) shows correlation of fuel poverty & IMD & energy

```{r energyCorrAll, fig.cap="Correlation of IMD score, % in fuel poverty and mean energy demand (Southampton LSOAs)"}
setkey(lsoa_fuelpovSoton_2019_dt, LSOA11CD)
dt <- lsoa_soton_elecData_dt[lsoa_soton_gas_dt][lsoa_multidepSoton_dt][lsoa_fuelpovSoton_2019_dt]

plotDT <- dt[, .(`MSOA Name`, LSOA11CD, 
                 meanEleckWh, meanGaskWh, IMDScore, IMDRank0, IMDDec0, IncScore, pcFP)]
pairs(plotDT[, .(meanEleckWh, meanGaskWh, IMDScore, IncScore, pcFP)])
```

IMD & % in fuel poverty correlate. Less clear correlation with mean energy. Need to check definitions... Also we might expect more of a correlation with the Income score (although INC score seems to drive IMD score in Southampton so...)

# Selecting areas with high fuel poverty & high deprivation

Create a local quantile for each - where are the places with higest deprivation & fuel poverty?

```{r checkAreas}
# reuse plotDT from above
# create local IMD & fuel poverty quintiles (5) 0->20% etc
plotDT[, IMD_quinSoton := cut(IMDScore, quantile(IMDScore))]
plotDT[, pcFP_quinSoton := cut(pcFP, quantile(pcFP))]

# how many LSOAs are in each cell of the crosstab
t <- plotDT[, .(n = .N), keyby = .(IMD_quinSoton, pcFP_quinSoton)]

t
```

Strange - why are there NAs?

Select them...

```{r selectAreas}

sample <- plotDT[pcFP_quinSoton  == "(12,25]" & 
              IMD_quinSoton == "(36.1,67.2]"][order(-pcFP)]
sample[, .(LSOA11CD, IMDScore, IMDDec0, IMD_quinSoton, pcFP, pcFP_quinSoton)]
message("Which national IMD decile are they in & what is mean % FP?")
sample[, .(mean_pcFP = mean(pcFP),
           mean_IMDScore = mean(IMDScore),
           nLSOAs = .N), keyby = .(IMDDec0)]
```

 Map them

```{r map areas}
map_df <- merge(lsoa_sf_data, sample) #merging the boundaries and energy data
ggplot2::ggplot(map_df) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "% fuel poverty", low = "green", high = "red") +
  labs(caption = "Southampton (selected LSOAs)")

ggplot2::ggplot(map_df) + 
  geom_sf(aes(fill = IMDScore)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Southampton (selected LSOAs)")

library(plotly)
p <- ggplot2::ggplot(sample, aes(x = IMDScore, y = pcFP)) +
  geom_point(aes(label = LSOA11CD))

plotly::ggplotly(p)
```

> Note that some areas are high IMD but relatively low % fuel poverty

Figure \@ref(fig:mapLeaflet) shows a leaflet version for pretty background to identify locations

```{r mapLeaflet, fig.cap="Location of filtered LSOAs"}
# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
library(leaflet)

st_coord_sys <- st_crs(map_df) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

# transform the coord system if required
if(st_coord_sys$epsg != 4326){
  map_df_trans <- st_transform(map_df, "+proj=longlat +datum=WGS84")
}

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = "blue", fillColor = "blue", fillOpacity = 0.2, weight = 1.5, popup = ~(LSOA11CD), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

# The end

```{r environment}
R.Version()

```

### 2021-07-26 mappingSotonEnergyDeprivation.Rmd
added colour fill by variable to leaflet map h/t @twrushby

@@
 
-Figure \@ref(fig:mapLeaflet) shows a leaflet version for pretty background to identify locations
+Figure \@ref(fig:mapLeaflet) shows a leaflet version for pretty background to identify locations. When selected the LSOAs are coloured by their IMD Score.
 
-```{r mapLeaflet, fig.cap="Location of filtered LSOAs"}
+```{r mapLeaflet, fig.cap="Location of filtered LSOAs (coloured by IMD score)"}
 # https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
@@
 
+#h/t @tom_rushby - see also https://rstudio.github.io/leaflet/colors.html
+
+qpal <- colorNumeric("Reds", map_df_trans$IMDScore, n = 9)
+
 leaflet(map_df_trans) %>%
   addTiles() %>%  # Add default OpenStreetMap map tiles
-  addPolygons(color = "blue", fillColor = "blue", fillOpacity = 0.2, weight = 1.5, popup = ~(LSOA11CD), # popups clicked
+  addPolygons(color = ~qpal(IMDScore),
+              fillOpacity = 0.2, weight = 1.5, popup = ~(LSOA11CD), # popups clicked
               highlight = highlightOptions(

### 2021-07-29 mappingSotonEnergyDeprivation.Rmd
typo

@@
 2019 Fuel Poverty
+
 ```{r Loading in the LSOA 2021 Fuel Poverty data}

### 2021-07-29 Solent_Mapping_v2.Rmd
Added in the section mapping the difference in fuel poverty from 2012 to 2019, this needs chnaging to 2012 and 2018

@@
 ```{r Loading in the LSOA 2021 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2021<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2021)
+inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
+lsoa_fuelpov_2019<-readr::read_csv (inFile)
+head(lsoa_fuelpov_2019)
 ```
@@
 ```{r Mapping the LSOA 2021 Fuel Poverty}
-lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
+lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
 # as above - why does it load as a char?
-lsoa_fuelpov_2021_merged$pcFP <- as.numeric(lsoa_fuelpov_2021_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
+lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
+ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
   geom_sf(aes(fill=pcFP))+ 

### 2021-07-30 mergeLA_data_fp.R
test R code for merging two data files to analyse change over time

@@ -1,0 +1,45 @@
+# useful R libraries
+library(readr)
+library(dplyr)
+
+dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/" # default for Meghan
+user <- Sys.info()[[7]] # who are we logged in as?
+if(user == "ben"){
+  dataFolder <- path.expand("~/University of Southampton/HCC Energy Landscape Mapping project - Documents/General/data/")
+}
+
+# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
+message("User: ", user)
+message("dataFolder: ", dataFolder)
+
+fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
+
+fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
+
+merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
+
+names(merged_df)
+
+merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
+
+summary(merged_df)
+
+hist(merged_df$pc_diff)
+
+# GIS libraries
+library(raster)
+library(sf)
+library(spData)
+library(spDataLarge)
+
+la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
+la_sf_data <- sf::st_read(la_shpFile)
+head(la_sf_data)
+
+mapDF <- merge(la_sf_data, merged_df)
+
+nrow(la_sf_data)
+
+p <- ggplot2::ggplot(mapDF) +
+  geom_sf(aes(fill = pc_diff)) +
+  scale_fill_gradient(low="green",high="red")

### 2021-07-30 Solent_Mapping_v2.Rmd
Changed the fuel poverty comparision to 2012 and 2018 and mapped the fuel poverty change of the cities in more detail

@@
 ```
-```{r Mapping Local Authority Fuel Poverty 2021}
+```{r Mapping Local Authority Fuel Poverty 2019}
 la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
@@
 
-### Actual Difference between 2012-2019
-```{r Loading in the difference data}
+### Difference in proportion Fuel Poverty 2012 to 2019
+```{r Creating the idfference in proportion variable}
 #Green indicates a smaller increase in fuel poverty from 2012 to 2019
 #Red indicates an increase in fuel poverty from 2012 to 2019
+fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
+fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
+merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
+names(merged_df)
+merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
+```
+```{r Mapping the iddference in fuel poverty from 2012 to 2019}
+merged_df$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
+la_merged_Fuelpov20192012dif <- merge(la_sf_data,merged_df)# Merge the local Authority boundaries and the Fuel Poverty data
+la_merged_Fuelpov20192012dif$pcFP <- as.numeric(la_merged_Fuelpov20192012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+ggplot2::ggplot(la_merged_Fuelpov20192012dif) +
+  geom_sf(aes(fill = pc_diff)) +
+  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
 ```
@@
 
-```{r Mapping the LSOA 2021 Fuel Poverty}
+```{r Mapping the LSOA 2019 Fuel Poverty}
 lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
@@
 ```
+####Mapping the difference in proportion of fuel poverty from 2012 to 2018
 
-# The end
+```{r Creating the dfference in proportion variable}
+#Green indicates a smaller increase in fuel poverty from 2012 to 2018
+#Had to use 2018 as the metric for fuel poverty has changed in 2019 
+#Red indicates an increase in fuel poverty from 2012 to 2018
+fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
+fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
+fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
+fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
+merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
+names(merged_df)
+merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
+summary(merged_df)
+```
+```{r Mapping the change in Fuel Poverty}
+merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
+ggplot2::ggplot(lsoa_fuelpov20122018) +
+  geom_sf(aes(fill=pc_diff))+ 
+  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
+  labs(caption ="Solent (all LSOAs)")
+```
+##### Looking at cities in more detail
+```{r Looking at Southampton in more detail}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
 
-```{r environment}
-R.Version()
+# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pc_diff)) +
+  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Southampton")
+#Around Bargate and Freemantle increased fuel poverty
+```
+```{r Looking at Portsmouth in more detail}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")
 
+# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pc_diff)) +
+  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+#Charles Dickens increased fuel poverty
 ```
+```{r Looking at Winchester in more detail}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
+
+# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pc_diff)) +
+  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```

### 2021-07-30 Solent_Mapping_v2.Rmd
Added in looking at the cities in more detail for fuel poverty and also the 2018 fuel poverty map so straight comparisons can be made

@@
   scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
+  labs(caption ="Solent (all LSOAs)")
 ```
+#####Looking at the cities in more detail
+```{r Looking at Southampton in more detail}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
 
+# plotting the multiple scales on dep of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `IMDScore`)) +
+  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Looking at Portsmouth in more detail}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")
+
+# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `IMDScore`)) +
+  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Looking at Winchester in more detail}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")
+
+# plotting the fuel poverty 2019 of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `IMDScore`)) +
+  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```
 ### Mapping Fuel Poverty
@@
   labs(caption ="Solent (all LSOAs)")
+```
+#####Looking at the cities in more detail
+```{r Looking at Southampton in more detail}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")
+
+# plotting the fuel poverty 2019 of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pcFP)) +
+  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Looking at Portsmouth in more detail}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")
+
+# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pcFP)) +
+  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Looking at Winchester in more detail}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")
+
+# plotting the fuel poverty 2019 of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pcFP)) +
+  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```
+
+#### 2018 Fuel Poverty
+```{r Loading in the LSOA 2018 Fuel Poverty data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
+lsoa_fuelpov_2018<-readr::read_csv (inFile)
+head(lsoa_fuelpov_2018)
+```
+
+```{r Mapping the LSOA 2018 Fuel Poverty}
+lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
+# as above - why does it load as a char?
+lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
+ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
+  geom_sf(aes(fill=pcFP18))+ 
+  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
+  labs(caption ="Solent (all LSOAs) 2018")
+```
+#####Looking at the cities in more detail
+```{r Looking at Southampton in more detail}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")
+
+# plotting the fuel poverty 2019 of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pcFP18)) +
+  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Southampton 2018")
+```
+```{r Looking at Portsmouth in more detail}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")
+
+# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pcFP18)) +
+  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Portsmouth 2018")
+```
+```{r Looking at Winchester in more detail}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
+
+# plotting the fuel poverty 2019 of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = pcFP18)) +
+  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
+  labs(caption = "Winchester 2018")
 ```

### 2021-07-30 Solent_Mapping_v2.Rmd
Added section attempting to map change in domestic gas consumption from 2010 to 2019 but getting a momory error

@@
 ## Mapping Transport
-
 #### Freight
@@
 ```{r Mapping Local Authority Fuel Poverty 2019}
-la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
+la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
 la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
@@
 ```
-
 ### Difference in proportion Fuel Poverty 2012 to 2019
@@
 ```
-
-###Difference in proportion between 2012-2019
-
 # Mapping the Middle Layer Super Output Areas (MSOA)
-
 ## Mapping Domestic
-
 ### Mapping the Electricity Consumption
@@
 ```
-
 ### Mapping the Gas
@@
 > Does this match to non-gas areas??
+
+####Mapping the change in gas consumption from 2010 to 2019
+```{r Creating the dfference in consumption variable}
+#Green indicates a decrease in gas consumption from 2010 to 2019
+#Red indicates an increase in gas consumption from 2010 to 2019
+domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
+domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
+domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`
+domgas_MSOA_2019$domgas2019 <- domgas_MSOA_2019$`Mean consumption (kWh per meter)`
+merged_domgas <- merge(domgas_MSOA_2010, domgas_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
+names(merged_domgas)
+merged_domgas$mc_diff <-  as.numeric(merged_domgas$domgas2019) - merged_domgas$domgas2010
+summary(merged_domgas)
+```
+
+```{r Mapping the change in dom mean gas comsumption}
+merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
+ggplot2::ggplot(msoa_domgas20102019) +
+  geom_sf(aes(fill=mc_diff))+ 
+  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
+  labs(caption ="Solent (all MSOAs)")
+##Error saying "Could not reallocate memory"
+```
 
@@
 ```
+####
+
 ### Mapping Gas

### 2021-07-30 Solent_Mapping_v2.Rmd
Added in the title for the idfference in non domestic gas at MSOA level from 2010 to 2019

@@
 ### Mapping Gas
-
 ```{r Loading in the MSOA gas consumption data for industry }
@@
 > The holes tell you where there is no non-domestic gas use
+
+####Mapping the difference in non domestic gas from 2010 to 2019
 

### 2021-07-30 Solent_Mapping_v2.Rmd
Title for non dom gas diff 2010 and 2019
Tried to add the difference in fuel pov 2012- 2018 for LA but something has gone wrong

@@
 ```
-### Difference in proportion Fuel Poverty 2012 to 2019
-```{r Creating the idfference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2019
-#Red indicates an increase in fuel poverty from 2012 to 2019
+### Difference in proportion Fuel Poverty 2012 to 2018 (BROKEN)
+```{r Creating the difference in proportion variable}
+#Green indicates a smaller increase in fuel poverty from 2012 to 2018
+#Red indicates an increase in fuel poverty from 2012 to 2018
+#2018 has to be used as the metric for measuring fuel poverty changed in 2019
 fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
-fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
-merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
-names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
+fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
+fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
+fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
+
+merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
+names(merged_dfla)
+merged_dfla$pc_diff <-merged_dfla$pc2018la - merged_df$pc2012la
 ```
-```{r Mapping the iddference in fuel poverty from 2012 to 2019}
-merged_df$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
-la_merged_Fuelpov20192012dif <- merge(la_sf_data,merged_df)# Merge the local Authority boundaries and the Fuel Poverty data
-la_merged_Fuelpov20192012dif$pcFP <- as.numeric(la_merged_Fuelpov20192012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-ggplot2::ggplot(la_merged_Fuelpov20192012dif) +
-  geom_sf(aes(fill = pc_diff)) +
+```{r Mapping the difference in fuel poverty from 2012 to 2018}
+merged_dfla$lad18cd <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
+la_merged_Fuelpov20182012dif <- merge(la_sf_data,merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
+la_merged_Fuelpov20182012dif$pcFP <- as.numeric(la_merged_Fuelpov20182012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+ggplot2::ggplot(la_merged_Fuelpov20182012dif) +
+  geom_sf(aes(fill = pc_diffla)) +
   scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
@@
 ####Mapping the difference in non domestic gas from 2010 to 2019
+
+here here here
 

### 2021-07-30 Solent_Mapping_v2.Rmd
Added all the titles so know what needs finishing

@@
 # Mapping the Local Authority
-
 ## Mapping Domestic Electricity Consumption
@@
 ```
-
 ## Mapping Transport
-#### Freight
+### Freight
 ```{r Loading the  Freight Transport consumption data for the Local Autority}
@@
 
-#### Personal
-
+### Personal
 Note: this data is not per household/person so it will correlate (to some extent) with population size.
@@
 ## Mapping Fuel Poverty 
-### 2019 Proportion of Population
+### 2019
 
@@
   geom_sf(aes(fill = pcFP)) +
-  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
+  scale_fill_gradient(name = "Proportion of households fuel poor (%) 2019", low="green",high="red")
+```
+###2018
+```{r Loading in the 2018 Local Authority Fuel Poverty Data}
+inFile<-paste0(dataFolder, "Fuel Poverty/2018 LA_Fuel_Poverty.csv")
+la_fuelpov_2018<-readr::read_csv(inFile)
+head(la_fuelpov_2018)
+```
+```{r Mapping Local Authority Fuel Poverty 2018}
+la_fuelpov_2018$lad18cd <- la_fuelpov_2018$`Area Code` # Creating a variable with the local authority code in the same name 
+la_merged_Fuelpov2018 <- merge(la_sf_data, la_fuelpov_2018)# Merge the local Authority boundaries and the Fuel Poverty data
+la_merged_Fuelpov2018$pcFP <- as.numeric(la_merged_Fuelpov2018$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+ggplot2::ggplot(la_merged_Fuelpov2019) +
+  geom_sf(aes(fill = pcFP)) +
+  scale_fill_gradient(name = "Proportion of households fuel poor (%) 2018", low="green",high="red")
 ```
@@
 ### Mapping the Electricity Consumption
-
+####2019
 ```{r Loading in the MSOA electricity consumption data}
@@
 ```
+####Mapping the change from 2010 to 2019
+
 ### Mapping the Gas
+####2019
 ```{r Loading in the MSOA gas consumption data}
@@
 ### Mapping Electricty
+####2019
 ```{r Loading in the MSOA electricity consumption data for industry }
@@
 ```
-####
+####Difference from 2010 to 2019
 
 ### Mapping Gas
+####2019
 ```{r Loading in the MSOA gas consumption data for industry }
@@
 ### Mapping Electricity consumption
-
+####2019
 ```{r Loading in the LSOA electricty consumption data}
@@
 lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
-head(msoa_elecData)
+head(lsoa_elecData)
 ```
@@
 
-#### Looking at cities in more detail
-```{r Looking at the cities in more detail}
+##### Looking at cities in more detail
+```{r Southampton}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
+```{r Portsmouth}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
+
+# plotting the electricity consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")
+
+# plotting the electricity consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```
+####Difference between 2010 and 2019
+
+#####Cities in more detail
 
 ### Mapping Gas
-
+####2019
 ```{r Loading in the LSOA gas consumption data}
@@
 ```
-
 > Aha - this one shows where there is no gas :-)
 
+#####Cities in More detail
+```{r Southampton}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
+
+# plotting the gas consumption of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Portsmouth}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
+
+# plotting the gas consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
+
+# plotting the gas consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```
 ### Mapping the Indices of Multiple Deprivation
-
+####2019
 ```{r Loading in the Indices of Multiple Deprivation data}
@@
 ```
+####Difference from 2010 to 2019
+
 ### Mapping Fuel Poverty
-#### 2019 Fuel Poverty
+#### 2019
 ```{r Loading in the LSOA 2021 Fuel Poverty data}
@@
 
-#### 2018 Fuel Poverty
+#### 2018
 ```{r Loading in the LSOA 2018 Fuel Poverty data}
@@
 ####Mapping the difference in proportion of fuel poverty from 2012 to 2018
-
 ```{r Creating the dfference in proportion variable}

### 2021-08-05 Solent_Mapping_v2.Rmd
Fixed the first half of the Fuel poverty LA difference map

@@
 ```
-### Difference in proportion Fuel Poverty 2012 to 2018 (BROKEN)
+### Difference in proportion Fuel Poverty 2012 to 2018 (2nd half is BROKEN!)
 ```{r Creating the difference in proportion variable}
@@
 fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
-
 merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
 names(merged_dfla)
-merged_dfla$pc_diff <-merged_dfla$pc2018la - merged_df$pc2012la
+merged_dfla$pc_diff <-as.numeric(merged_dfla$pc2018la)- merged_dfla$pc2012la
+summary(merged_dfla)
 ```
+
 ```{r Mapping the difference in fuel poverty from 2012 to 2018}
-merged_dfla$lad18cd <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
-la_merged_Fuelpov20182012dif <- merge(la_sf_data,merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
-la_merged_Fuelpov20182012dif$pcFP <- as.numeric(la_merged_Fuelpov20182012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+##BROKEN
+merged_dfla$LA11CD <- merged_dfla$”LA Code” # Creating a variable with the local authority code in the same name 
+la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
 ggplot2::ggplot(la_merged_Fuelpov20182012dif) +
@@
   scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
+labs(caption=”Solent (all LA)”)
 ```
+
 # Mapping the Middle Layer Super Output Areas (MSOA)

### 2021-08-05 Solent_Mapping_v2.Rmd
fixed typos

@@
 ```
+
 ### Difference in proportion Fuel Poverty 2012 to 2018 (2nd half is BROKEN!)
+
 ```{r Creating the difference in proportion variable}
@@
 ##BROKEN
-merged_dfla$LA11CD <- merged_dfla$”LA Code” # Creating a variable with the local authority code in the same name 
+merged_dfla$LA11CD <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
 la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
@@
   geom_sf(aes(fill = pc_diffla)) +
-  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
-labs(caption=”Solent (all LA)”)
+  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
+labs(caption="Solent (all LA)")
 ```

### 2021-08-05 Solent_Mapping_v2.Rmd
fixed variable name used

@@
 merged_dfla$LA11CD <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
-la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla)# Merge the local Authority boundaries and the Fuel Poverty data
-ggplot2::ggplot(la_merged_Fuelpov20182012dif) +
-  geom_sf(aes(fill = pc_diffla)) +
+la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
+ggplot2::ggplot(la_Fuelpov20182012dif) +
+  geom_sf(aes(fill = pc_diff)) +
   scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +

### 2021-08-05 Solent_Mapping_v2.Rmd
Changing chunk names so there are no duplicates

@@
 ##BROKEN
-merged_dfla$LA11CD <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
+merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
 la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
@@
 ##### Looking at cities in more detail
-```{r Southampton}
+```{r Southampton LSOA Elec}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Portsmouth}
+```{r Portsmouth LSOA Elec}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Winchester}
+```{r Winchester LSOA Elec}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
@@
 #####Cities in More detail
-```{r Southampton}
+```{r Southampton LSOA Gas}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Portsmouth}
+```{r Portsmouth LSOA Gas}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Winchester}
+```{r Winchester LSOA Gas}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
@@
 #####Looking at the cities in more detail
-```{r Looking at Southampton in more detail}
+```{r Southampton LSOA Indices of dep}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Looking at Portsmouth in more detail}
+```{r Portsmouth LSOA Indices of dep}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
+# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
 ggplot2::ggplot(mapData) + 
@@
 ```
-```{r Looking at Winchester in more detail}
+```{r Winchester LSOA Indices of dep}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
@@
 
-# plotting the fuel poverty 2019 of Winchester in more detail
+# plotting the indices of dep 2019 of Winchester in more detail
 ggplot2::ggplot(mapData) + 
@@
 #### 2019
-```{r Loading in the LSOA 2021 Fuel Poverty data}
+```{r Loading in the LSOA 2019 Fuel Poverty data}
 inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
@@
 #####Looking at the cities in more detail
-```{r Looking at Southampton in more detail}
+```{r Southampton LSOA Fuel Pov 2019}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Looking at Portsmouth in more detail}
+```{r Portsmouth LSOA Fuel Pov 2019}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Looking at Winchester in more detail}
+```{r Winchester LSOA Fuel Pov}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
@@
 #####Looking at the cities in more detail
-```{r Looking at Southampton in more detail}
+```{r Southampton LSOA Fuel Pov 2018}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Looking at Portsmouth in more detail}
+```{r Portsmouth LSOA Fuel Pov 2018}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Looking at Winchester in more detail}
+```{r Winchester LOSA Fuel Pov 2018}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
@@
 ##### Looking at cities in more detail
-```{r Looking at Southampton in more detail}
+```{r Southampton LSOA Fuel Pov 2012 2018}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Looking at Portsmouth in more detail}
+```{r Portsmouth LSOA Fuel Pov 2012 2018}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Looking at Winchester in more detail}
+```{r Winchester LSOA Fuel Pov 2012 2018}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail

### 2021-08-09 Solent_Mapping_v2.Rmd
Adding in BROKEN

@@
 # Mapping the Local Authority
-## Mapping Domestic Electricity Consumption
-
+##Mapping Domestic Electricity Consumption
 ```{r loading in Local Authority electricity consumption data}
-inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
-la_elecData <- readr::read_csv(inFile)
-summary(la_elecData)
+#inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
+#la_elecData <- readr::read_csv(inFile)
+#summary(la_elecData)
 ```
@@
 # Load from file
-la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
-la_sf_data <- sf::st_read(la_shpFile)
-head(la_sf_data)
+#la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
+#la_sf_data <- sf::st_read(la_shpFile)
+#]head(la_sf_data)
 ```
@@
 ```{r Mapping the local authority electricty consumption}
-la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
-la_merged_sf <- merge(la_sf_data, la_elecData)#Merge the local Authority boundaries and the consumption data
-ggplot2::ggplot(la_merged_sf) +
-  geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")
+#la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
+#la_merged_sf <- merge(la_sf_data, la_elecData)#Merge the local Authority boundaries and the consumption data
+#ggplot2::ggplot(la_merged_sf) +
+ # geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")
 
@@
 ```{r Loading the  Freight Transport consumption data for the Local Autority}
-inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
-la_Transport <- readr::read_csv(inFile)
-summary(la_Transport)
-head(la_Transport)
+#inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
+#la_Transport <- readr::read_csv(inFile)
+#summary(la_Transport)
+#head(la_Transport)
 ```
@@
 
-la_Transport$lad18cd <- la_Transport$Code # Creating a variable with the local authority code in the same name of the consumption data
-la_merged_Transp <- merge(la_sf_data, la_Transport)# Merge the local Authority boundaries and the Transport data
-ggplot2::ggplot(la_merged_Transp) +
-  geom_sf(aes(fill = Freight)) +
-  scale_fill_gradient(name = "Freight: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red")
+#la_Transport$lad18cd <- la_Transport$Code # Creating a variable with the local authority code in the same name of the consumption data
+#la_merged_Transp <- merge(la_sf_data, la_Transport)# Merge the local Authority boundaries and the Transport data
+#ggplot2::ggplot(la_merged_Transp) +
+ # geom_sf(aes(fill = Freight)) +
+  #scale_fill_gradient(name = "Freight: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red")
 ```
@@
 # re-use the merged dataset
-ggplot2::ggplot(la_merged_Transp) +
-  geom_sf(aes(fill = Personal)) +
-  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
+#ggplot2::ggplot(la_merged_Transp) +
+ # geom_sf(aes(fill = Personal)) +
+  #scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
 ```
@@
 ```{r Loading in the 2019 Local Authority Fuel Poverty Data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
-la_fuelpov_2019<-readr::read_csv(inFile)
-head(la_fuelpov_2019)
+#inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
+#la_fuelpov_2019<-readr::read_csv(inFile)
+#head(la_fuelpov_2019)
 ```
 ```{r Mapping Local Authority Fuel Poverty 2019}
-la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
-la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
-la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-ggplot2::ggplot(la_merged_Fuelpov2019) +
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_gradient(name = "Proportion of households fuel poor (%) 2019", low="green",high="red")
+#la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
+#la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
+#la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+#ggplot2::ggplot(la_merged_Fuelpov2019) +
+ # geom_sf(aes(fill = pcFP)) +
+  #scale_fill_gradient(name = "Proportion of households fuel poor (%) 2019", low="green",high="red")
 ```
@@
 ```{r Loading in the 2018 Local Authority Fuel Poverty Data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LA_Fuel_Poverty.csv")
-la_fuelpov_2018<-readr::read_csv(inFile)
-head(la_fuelpov_2018)
+#inFile<-paste0(dataFolder, "Fuel Poverty/2018 LA_Fuel_Poverty.csv")
+#la_fuelpov_2018<-readr::read_csv(inFile)
+#head(la_fuelpov_2018)
 ```
 ```{r Mapping Local Authority Fuel Poverty 2018}
-la_fuelpov_2018$lad18cd <- la_fuelpov_2018$`Area Code` # Creating a variable with the local authority code in the same name 
-la_merged_Fuelpov2018 <- merge(la_sf_data, la_fuelpov_2018)# Merge the local Authority boundaries and the Fuel Poverty data
-la_merged_Fuelpov2018$pcFP <- as.numeric(la_merged_Fuelpov2018$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-ggplot2::ggplot(la_merged_Fuelpov2019) +
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_gradient(name = "Proportion of households fuel poor (%) 2018", low="green",high="red")
+#la_fuelpov_2018$lad18cd <- la_fuelpov_2018$`Area Code` # Creating a variable with the local authority code in the same name 
+#la_merged_Fuelpov2018 <- merge(la_sf_data, la_fuelpov_2018)# Merge the local Authority boundaries and the Fuel Poverty data
+#la_merged_Fuelpov2018$pcFP <- as.numeric(la_merged_Fuelpov2018$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
+#ggplot2::ggplot(la_merged_Fuelpov2019) +
+ # geom_sf(aes(fill = pcFP)) +
+  #scale_fill_gradient(name = "Proportion of households fuel poor (%) 2018", low="green",high="red")
 ```
 
-### Difference in proportion Fuel Poverty 2012 to 2018 (2nd half is BROKEN!)
+### Difference in proportion Fuel Poverty 2012 to 2018
 
@@
 #2018 has to be used as the metric for measuring fuel poverty changed in 2019
-fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
-fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
-fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
-fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
-merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
-names(merged_dfla)
-merged_dfla$pc_diff <-as.numeric(merged_dfla$pc2018la)- merged_dfla$pc2012la
-summary(merged_dfla)
+#fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
+#fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
+#fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
+#fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
+#merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
+#names(merged_dfla)
+#merged_dfla$pc_diff <-as.numeric(merged_dfla$pc2018la)- merged_dfla$pc2012la
+#summary(merged_dfla)
 ```
@@
 ##BROKEN
-merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
-la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
-ggplot2::ggplot(la_Fuelpov20182012dif) +
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
-labs(caption="Solent (all LA)")
+#merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
+#la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
+#ggplot2::ggplot(la_Fuelpov20182012dif) +
+ # geom_sf(aes(fill = pc_diff)) +
+  #scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
+#labs(caption="Solent (all LA)")
 ```
@@
   labs(caption ="Solent (all MSOAs)")
-##Error saying "Could not reallocate memory"
+##BROKEN
 ```

### 2021-08-09 Solent_Mapping_v2.Rmd
Adding in difference maps where there where gaps and attempting to fix some of the errors (unsucessfully)

@@
 ```{r Mapping the difference in fuel poverty from 2012 to 2018}
-##BROKEN
 #merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
@@
 ####Mapping the change from 2010 to 2019
+```{r Creating the difference in MSOA mean dom elec consumption variable}
+domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_DOM_ELEC_2010.csv"))
+domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "/energy/MSOA_DOM_ELEC_2019.csv"))
+domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
+domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
+merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE) ##BROKEN
+names(merged_domelec)
+merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
+summary(merged_domelec)
+```
+```{r Mapping the MSOA difference in mean dom elec consumption}
+merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
+msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
+ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton of domestic electricty per meter (kWh per meter",low="green",high="red")+labs(caption="Solent(all MSOAs)")
+```
 
@@
 ####Difference from 2010 to 2019
+```{r Creating the mean electricty consumption from the industrial sector MOSA}
+##BROKEN
+NONDOMELEC_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
+NONDOMELEC_MSOA_2019<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
+NONDOMELEC_MSOA_2010$nondomelec2010 <-NONDOMELEC_MSOA_2010$' Mean consumption (kWh per meter)'                                       
+NONDOMELEC_MSOA_2019$nondomeelec2019<-NONDOMELEC_MSOA_2019$' Mean consumption (kWh per meter) '
+merged_nondomelec <-merge(NONDOMELEC_MSOA_2010, NONDOMELEC_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_nondomelec)
+merged_nondomelec$nondomelec_diff<-merged_nondomelec$nondomeelec2019 - merged_nondomelec$nondomeelec2010
+summary(merged_nondomelec)
+```
+```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
+merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
+msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
+ggplot2::ggplot(msoa_nondom20102019) +
+  geom_sf(aes(fill=nondom_diff))+ 
+  scale_fill_continuous(name="Change in  mean electricty consumption for the industrial sector", low="green",high="red")+
+  labs(caption ="Solent (all MSOAs)")
+```
 
@@
 ####Mapping the difference in non domestic gas from 2010 to 2019 
+```{r Creating the difference in non domestic gas consumption in the MSOA}
+nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NonDom_Gas_2010.csv"))
+nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/MSOA_NonDom_Gas_2019.csv"))
+nondomgas_msoa_2010$nondomgas2010<-nondomgas_msoa_2010$' Mean consumption (kWh per meter)'
+nondomgas_msoa_2019$nondomgas2019<-nondomgas_msoa_2019$' Mean consumption (kWh per meter)'
+merged_nondomgas20102019<-merge(nondomgas_msoa_2010, nondomgas_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_nondomgas20102019)
+merged_nondomgas20102019$nondomgas_diff<-merged_nondomgas20102019$nondomgas2019 - merged_nondomgas20102019$nondomgas2010 ##BROKEN
+summary(merged_nondomgas20102019)
+```
 
-here here here
+```{r Mapping the change in non domestic gas usage in the MSOA}
+merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
+msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
+ggplot2::ggplot(msoa_nondomgas20102019) +
+  geom_sf(aes(fill=pc_diff))+ 
+  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
+  labs(caption ="Solent (all MSOAs)")
+```
 

### 2021-08-09 LA maps (not being used).Rmd
Splitting the doc (LA)

--- 2021-08-09 Solent_Mapping_v2.Rmd
@@
 ```
-
-# Mapping the Middle Layer Super Output Areas (MSOA)
-## Mapping Domestic
-### Mapping the Electricity Consumption
-####2019
-```{r Loading in the MSOA electricity consumption data}
-# electricity consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_DOM_ELEC_2019.csv")
-msoa_elecData <- readr::read_csv(inFile)
-head(msoa_elecData)
-```
-
-```{r Loading in the Boundary Data for the MSOA}
-inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
-message("Loading Middle Layer Super Output Area (MSOA) from file")
-#When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
-msoa_sf_data <- sf::read_sf(inf) 
-head (msoa_sf_data)
-table(msoa_sf_data$LAD11NM)#how many MSOAs are in each LA
-```
-
-```{r Mapping the electrcity consumption of the MSOAs}
-msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
-msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
-ggplot2::ggplot(msoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Mapping the change from 2010 to 2019
-
-### Mapping the Gas
-####2019
-```{r Loading in the MSOA gas consumption data}
-# gas consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
-msoa_gasData <- readr::read_csv(inFile)
-head(msoa_gasData)
-```
-```{r Mapping the gas consumption of the MSOAs}
-msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
-ggplot2::ggplot(msoa_merged_sf_domgas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> Does this match to non-gas areas??
-
-####Mapping the change in gas consumption from 2010 to 2019
-```{r Creating the dfference in consumption variable}
-#Green indicates a decrease in gas consumption from 2010 to 2019
-#Red indicates an increase in gas consumption from 2010 to 2019
-domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
-domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
-domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`
-domgas_MSOA_2019$domgas2019 <- domgas_MSOA_2019$`Mean consumption (kWh per meter)`
-merged_domgas <- merge(domgas_MSOA_2010, domgas_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
-names(merged_domgas)
-merged_domgas$mc_diff <-  as.numeric(merged_domgas$domgas2019) - merged_domgas$domgas2010
-summary(merged_domgas)
-```
-
-```{r Mapping the change in dom mean gas comsumption}
-merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
-ggplot2::ggplot(msoa_domgas20102019) +
-  geom_sf(aes(fill=mc_diff))+ 
-  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
-##BROKEN
-```
-
-## Mapping Commercial
-### Mapping Electricty
-####2019
-```{r Loading in the MSOA electricity consumption data for industry }
-# electricity consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
-msoa_elecDatanondom <- readr::read_csv(inFile)
-head(msoa_elecDatanondom)
-```
-
-```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
-msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Difference from 2010 to 2019
-
-### Mapping Gas
-####2019
-```{r Loading in the MSOA gas consumption data for industry }
-# gas consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
-msoa_gasDatanondom <- readr::read_csv(inFile)
-head(msoa_gasDatanondom)
-```
-
-```{r Mapping the gas consumption of the MSOAs Industrial Sector}
-msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> The holes tell you where there is no non-domestic gas use
-
-####Mapping the difference in non domestic gas from 2010 to 2019
-
-here here here
-
-# Mapping the Lower Layer Super Output Area (LSOA)
-
-## Mapping Domestic
-
-### Mapping Electricity consumption
-####2019
-```{r Loading in the LSOA electricty consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
-lsoa_elecData <- readr::read_csv(inFile)
-lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_elecData)
-```
-
-```{r Loading in boundary data for the LSOA}
-#The LSOA boundaries for the Solent have been pre-downloaded
-inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
-message ("Loading LSOA boundaries from file")
-lsoa_sf_data <- sf::read_sf(inf)
-head(lsoa_sf_data)
-table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
-```
-
-```{r Mapping the electricty consumption of the LSOAs}
-lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-
-##### Looking at cities in more detail        
-```{r Southampton LSOA Elec}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
-
-# plotting the electricity consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Elec}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the electricity consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Elec}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")
-
-# plotting the electricity consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference between 2010 and 2019
-
-#####Cities in more detail
-
-### Mapping Gas
-####2019
-```{r Loading in the LSOA gas consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
-lsoa_gasData <- readr::read_csv(inFile)
-lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_gasData)
-```
-
-```{r Mapping the gas consumption of the LSOAs}
-lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-> Aha - this one shows where there is no gas :-)
-
-#####Cities in More detail
-```{r Southampton LSOA Gas}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
-
-# plotting the gas consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Gas}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
-
-# plotting the gas consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Gas}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
-
-# plotting the gas consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-### Mapping the Indices of Multiple Deprivation
-####2019
-```{r Loading in the Indices of Multiple Deprivation data}
-# Multiple deprivation data at MSOA pre downloaded
-inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
-lsoa_multidep <- readr::read_csv (inFile)
-head(lsoa_multidep)
-```
-
-```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
-head(lsoa_multidep)
-lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Indices of dep}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
-
-# plotting the multiple scales on dep of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Indices of dep}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Indices of dep}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")
-
-# plotting the indices of dep 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference from 2010 to 2019
-
-### Mapping Fuel Poverty
-#### 2019
-```{r Loading in the LSOA 2019 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2019<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2019)
-```
-
-```{r Mapping the LSOA 2019 Fuel Poverty}
-lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
-  geom_sf(aes(fill=pcFP))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2019}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Fuel Pov 2019}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Fuel Pov}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-
-#### 2018
-```{r Loading in the LSOA 2018 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2018<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2018)
-```
-
-```{r Mapping the LSOA 2018 Fuel Poverty}
-lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
-  geom_sf(aes(fill=pcFP18))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs) 2018")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton 2018")
-```
-```{r Portsmouth LSOA Fuel Pov 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth 2018")
-```
-```{r Winchester LOSA Fuel Pov 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester 2018")
-```
-####Mapping the difference in proportion of fuel poverty from 2012 to 2018
-```{r Creating the dfference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Had to use 2018 as the metric for fuel poverty has changed in 2019 
-#Red indicates an increase in fuel poverty from 2012 to 2018
-fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
-fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
-merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
-names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
-summary(merged_df)
-```
-```{r Mapping the change in Fuel Poverty}
-merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
-ggplot2::ggplot(lsoa_fuelpov20122018) +
-  geom_sf(aes(fill=pc_diff))+ 
-  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-##### Looking at cities in more detail
-```{r Southampton LSOA Fuel Pov 2012 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-#Around Bargate and Freemantle increased fuel poverty
-```
-```{r Portsmouth LSOA Fuel Pov 2012 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-#Charles Dickens increased fuel poverty
-```
-```{r Winchester LSOA Fuel Pov 2012 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
-
-# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```

### 2021-08-09 LSOA domestic Elec and Gas.Rmd
Splitting it out LSOA domestc elec and gas

--- 2021-08-05 Solent_Mapping_v2.Rmd
@@
 
-# Mapping the Local Authority
-## Mapping Domestic Electricity Consumption
-
-```{r loading in Local Authority electricity consumption data}
-inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
-la_elecData <- readr::read_csv(inFile)
-summary(la_elecData)
-```
-
-```{r Loading in the Boundary Data for local authorities we are intrested in}
-# geo_query <- "https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Local_Authority_Districts_December_2018_Boundaries_UK_BGC/MapServer/0/query?where=lad18nm%20IN%20(%27Southampton%27,%27Portsmouth%27,%27Winchester%27,%27Eastleigh%27,%27Isle%20of%20Wight%27,%27Fareham%27,%27Gosport%27,%27Test%20Valley%27,%27East%20Hampshire%27,%27Havant%27,%27New%20Forest%27,%27Hart%27,%27Basingstoke%20and%20Deane%27)&outFields=lad18cd,lad18nm,long,lat&outSR=4326&f=geojson"
-# #This only includes the ones we are interested in i.e the Solent
-# message("Loading LA geometry from ONS Open Geography API") #Specifying the location message
-# la_sf_data <- sf::st_read(geo_query)
-
-# The above is very clever but it takes time
-# Load from file
-la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
-la_sf_data <- sf::st_read(la_shpFile)
-head(la_sf_data)
-```
-
-```{r Mapping the local authority electricty consumption}
-la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
-la_merged_sf <- merge(la_sf_data, la_elecData)#Merge the local Authority boundaries and the consumption data
-ggplot2::ggplot(la_merged_sf) +
-  geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")
-
-```
-## Mapping Transport
-### Freight
-```{r Loading the  Freight Transport consumption data for the Local Autority}
-inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
-la_Transport <- readr::read_csv(inFile)
-summary(la_Transport)
-head(la_Transport)
-```
-
-```{r Mapping the local authority energy consumption (Freight)}
-
-la_Transport$lad18cd <- la_Transport$Code # Creating a variable with the local authority code in the same name of the consumption data
-la_merged_Transp <- merge(la_sf_data, la_Transport)# Merge the local Authority boundaries and the Transport data
-ggplot2::ggplot(la_merged_Transp) +
-  geom_sf(aes(fill = Freight)) +
-  scale_fill_gradient(name = "Freight: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red")
-```
-
-### Personal
-Note: this data is not per household/person so it will correlate (to some extent) with population size.
-
-```{r Mapping the local authority energy consumption (Personal)}
-# re-use the merged dataset
-ggplot2::ggplot(la_merged_Transp) +
-  geom_sf(aes(fill = Personal)) +
-  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
-```
-## Mapping Fuel Poverty 
-### 2019
-
-```{r Loading in the 2019 Local Authority Fuel Poverty Data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
-la_fuelpov_2019<-readr::read_csv(inFile)
-head(la_fuelpov_2019)
-```
-```{r Mapping Local Authority Fuel Poverty 2019}
-la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
-la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
-la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-ggplot2::ggplot(la_merged_Fuelpov2019) +
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_gradient(name = "Proportion of households fuel poor (%) 2019", low="green",high="red")
-```
-###2018
-```{r Loading in the 2018 Local Authority Fuel Poverty Data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LA_Fuel_Poverty.csv")
-la_fuelpov_2018<-readr::read_csv(inFile)
-head(la_fuelpov_2018)
-```
-```{r Mapping Local Authority Fuel Poverty 2018}
-la_fuelpov_2018$lad18cd <- la_fuelpov_2018$`Area Code` # Creating a variable with the local authority code in the same name 
-la_merged_Fuelpov2018 <- merge(la_sf_data, la_fuelpov_2018)# Merge the local Authority boundaries and the Fuel Poverty data
-la_merged_Fuelpov2018$pcFP <- as.numeric(la_merged_Fuelpov2018$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-ggplot2::ggplot(la_merged_Fuelpov2019) +
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_gradient(name = "Proportion of households fuel poor (%) 2018", low="green",high="red")
-```
-
-### Difference in proportion Fuel Poverty 2012 to 2018 (2nd half is BROKEN!)
-
-```{r Creating the difference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Red indicates an increase in fuel poverty from 2012 to 2018
-#2018 has to be used as the metric for measuring fuel poverty changed in 2019
-fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
-fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
-fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
-fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
-merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
-names(merged_dfla)
-merged_dfla$pc_diff <-as.numeric(merged_dfla$pc2018la)- merged_dfla$pc2012la
-summary(merged_dfla)
-```
-
-```{r Mapping the difference in fuel poverty from 2012 to 2018}
-##BROKEN
-merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
-la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
-ggplot2::ggplot(la_Fuelpov20182012dif) +
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
-labs(caption="Solent (all LA)")
-```
-
-# Mapping the Middle Layer Super Output Areas (MSOA)
+# Mapping the Lower Layer Super Output Area (LSOA)
 ## Mapping Domestic
-### Mapping the Electricity Consumption
-####2019
-```{r Loading in the MSOA electricity consumption data}
-# electricity consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_DOM_ELEC_2019.csv")
-msoa_elecData <- readr::read_csv(inFile)
-head(msoa_elecData)
-```
-
-```{r Loading in the Boundary Data for the MSOA}
-inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
-message("Loading Middle Layer Super Output Area (MSOA) from file")
-#When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
-msoa_sf_data <- sf::read_sf(inf) 
-head (msoa_sf_data)
-table(msoa_sf_data$LAD11NM)#how many MSOAs are in each LA
-```
-
-```{r Mapping the electrcity consumption of the MSOAs}
-msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
-msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
-ggplot2::ggplot(msoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Mapping the change from 2010 to 2019
-
-### Mapping the Gas
-####2019
-```{r Loading in the MSOA gas consumption data}
-# gas consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
-msoa_gasData <- readr::read_csv(inFile)
-head(msoa_gasData)
-```
-```{r Mapping the gas consumption of the MSOAs}
-msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
-ggplot2::ggplot(msoa_merged_sf_domgas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> Does this match to non-gas areas??
-
-####Mapping the change in gas consumption from 2010 to 2019
-```{r Creating the dfference in consumption variable}
-#Green indicates a decrease in gas consumption from 2010 to 2019
-#Red indicates an increase in gas consumption from 2010 to 2019
-domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
-domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
-domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`
-domgas_MSOA_2019$domgas2019 <- domgas_MSOA_2019$`Mean consumption (kWh per meter)`
-merged_domgas <- merge(domgas_MSOA_2010, domgas_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
-names(merged_domgas)
-merged_domgas$mc_diff <-  as.numeric(merged_domgas$domgas2019) - merged_domgas$domgas2010
-summary(merged_domgas)
-```
-
-```{r Mapping the change in dom mean gas comsumption}
-merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
-ggplot2::ggplot(msoa_domgas20102019) +
-  geom_sf(aes(fill=mc_diff))+ 
-  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
-##Error saying "Could not reallocate memory"
-```
-
-## Mapping Commercial
-### Mapping Electricty
-####2019
-```{r Loading in the MSOA electricity consumption data for industry }
-# electricity consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
-msoa_elecDatanondom <- readr::read_csv(inFile)
-head(msoa_elecDatanondom)
-```
-
-```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
-msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Difference from 2010 to 2019
-
-### Mapping Gas
-####2019
-```{r Loading in the MSOA gas consumption data for industry }
-# gas consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
-msoa_gasDatanondom <- readr::read_csv(inFile)
-head(msoa_gasDatanondom)
-```
-
-```{r Mapping the gas consumption of the MSOAs Industrial Sector}
-msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> The holes tell you where there is no non-domestic gas use
-
-####Mapping the difference in non domestic gas from 2010 to 2019
-
-here here here
-
-# Mapping the Lower Layer Super Output Area (LSOA)
-
-## Mapping Domestic
-
 ### Mapping Electricity consumption
@@
 ##### Looking at cities in more detail        
-```{r Southampton LSOA Elec}
+```{r Southampton LSOA dom Elec}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Portsmouth LSOA Elec}
+```{r Portsmouth LSOA dom Elec}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Winchester LSOA Elec}
+```{r Winchester LSOA dom Elec}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
@@
 ```
-####Difference between 2010 and 2019
+####Difference between 2010 and 2019 dom elec
+
+here here
 
 #####Cities in more detail
+
+here here here
 
@@
 ```
-### Mapping the Indices of Multiple Deprivation
-####2019
-```{r Loading in the Indices of Multiple Deprivation data}
-# Multiple deprivation data at MSOA pre downloaded
-inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
-lsoa_multidep <- readr::read_csv (inFile)
-head(lsoa_multidep)
-```
+####Difference between 2010 and 2019 dom gas
 
-```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
-head(lsoa_multidep)
-lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Indices of dep}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
+here here here
 
-# plotting the multiple scales on dep of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Indices of dep}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")
+#####Cities in more detail
 
-# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Indices of dep}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")
-
-# plotting the indices of dep 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference from 2010 to 2019
-
-### Mapping Fuel Poverty
-#### 2019
-```{r Loading in the LSOA 2019 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2019<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2019)
-```
-
-```{r Mapping the LSOA 2019 Fuel Poverty}
-lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
-  geom_sf(aes(fill=pcFP))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2019}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Fuel Pov 2019}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Fuel Pov}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-
-#### 2018
-```{r Loading in the LSOA 2018 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2018<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2018)
-```
-
-```{r Mapping the LSOA 2018 Fuel Poverty}
-lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
-  geom_sf(aes(fill=pcFP18))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs) 2018")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton 2018")
-```
-```{r Portsmouth LSOA Fuel Pov 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth 2018")
-```
-```{r Winchester LOSA Fuel Pov 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester 2018")
-```
-####Mapping the difference in proportion of fuel poverty from 2012 to 2018
-```{r Creating the dfference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Had to use 2018 as the metric for fuel poverty has changed in 2019 
-#Red indicates an increase in fuel poverty from 2012 to 2018
-fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
-fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
-merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
-names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
-summary(merged_df)
-```
-```{r Mapping the change in Fuel Poverty}
-merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
-ggplot2::ggplot(lsoa_fuelpov20122018) +
-  geom_sf(aes(fill=pc_diff))+ 
-  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-##### Looking at cities in more detail
-```{r Southampton LSOA Fuel Pov 2012 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-#Around Bargate and Freemantle increased fuel poverty
-```
-```{r Portsmouth LSOA Fuel Pov 2012 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-#Charles Dickens increased fuel poverty
-```
-```{r Winchester LSOA Fuel Pov 2012 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
-
-# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
+here here here

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Splitting it out MSOA domestic Elec and Gas

--- 2021-08-09 Solent_Mapping_v2.Rmd
@@
 
-# Mapping the Local Authority
-##Mapping Domestic Electricity Consumption
-```{r loading in Local Authority electricity consumption data}
-#inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
-#la_elecData <- readr::read_csv(inFile)
-#summary(la_elecData)
-```
-
-```{r Loading in the Boundary Data for local authorities we are intrested in}
-# geo_query <- "https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Local_Authority_Districts_December_2018_Boundaries_UK_BGC/MapServer/0/query?where=lad18nm%20IN%20(%27Southampton%27,%27Portsmouth%27,%27Winchester%27,%27Eastleigh%27,%27Isle%20of%20Wight%27,%27Fareham%27,%27Gosport%27,%27Test%20Valley%27,%27East%20Hampshire%27,%27Havant%27,%27New%20Forest%27,%27Hart%27,%27Basingstoke%20and%20Deane%27)&outFields=lad18cd,lad18nm,long,lat&outSR=4326&f=geojson"
-# #This only includes the ones we are interested in i.e the Solent
-# message("Loading LA geometry from ONS Open Geography API") #Specifying the location message
-# la_sf_data <- sf::st_read(geo_query)
-
-# The above is very clever but it takes time
-# Load from file
-#la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
-#la_sf_data <- sf::st_read(la_shpFile)
-#]head(la_sf_data)
-```
-
-```{r Mapping the local authority electricty consumption}
-#la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
-#la_merged_sf <- merge(la_sf_data, la_elecData)#Merge the local Authority boundaries and the consumption data
-#ggplot2::ggplot(la_merged_sf) +
- # geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")
-
-```
-## Mapping Transport
-### Freight
-```{r Loading the  Freight Transport consumption data for the Local Autority}
-#inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
-#la_Transport <- readr::read_csv(inFile)
-#summary(la_Transport)
-#head(la_Transport)
-```
-
-```{r Mapping the local authority energy consumption (Freight)}
-
-#la_Transport$lad18cd <- la_Transport$Code # Creating a variable with the local authority code in the same name of the consumption data
-#la_merged_Transp <- merge(la_sf_data, la_Transport)# Merge the local Authority boundaries and the Transport data
-#ggplot2::ggplot(la_merged_Transp) +
- # geom_sf(aes(fill = Freight)) +
-  #scale_fill_gradient(name = "Freight: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red")
-```
-
-### Personal
-Note: this data is not per household/person so it will correlate (to some extent) with population size.
-
-```{r Mapping the local authority energy consumption (Personal)}
-# re-use the merged dataset
-#ggplot2::ggplot(la_merged_Transp) +
- # geom_sf(aes(fill = Personal)) +
-  #scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
-```
-## Mapping Fuel Poverty 
-### 2019
-
-```{r Loading in the 2019 Local Authority Fuel Poverty Data}
-#inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
-#la_fuelpov_2019<-readr::read_csv(inFile)
-#head(la_fuelpov_2019)
-```
-```{r Mapping Local Authority Fuel Poverty 2019}
-#la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
-#la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
-#la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-#ggplot2::ggplot(la_merged_Fuelpov2019) +
- # geom_sf(aes(fill = pcFP)) +
-  #scale_fill_gradient(name = "Proportion of households fuel poor (%) 2019", low="green",high="red")
-```
-###2018
-```{r Loading in the 2018 Local Authority Fuel Poverty Data}
-#inFile<-paste0(dataFolder, "Fuel Poverty/2018 LA_Fuel_Poverty.csv")
-#la_fuelpov_2018<-readr::read_csv(inFile)
-#head(la_fuelpov_2018)
-```
-```{r Mapping Local Authority Fuel Poverty 2018}
-#la_fuelpov_2018$lad18cd <- la_fuelpov_2018$`Area Code` # Creating a variable with the local authority code in the same name 
-#la_merged_Fuelpov2018 <- merge(la_sf_data, la_fuelpov_2018)# Merge the local Authority boundaries and the Fuel Poverty data
-#la_merged_Fuelpov2018$pcFP <- as.numeric(la_merged_Fuelpov2018$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-#ggplot2::ggplot(la_merged_Fuelpov2019) +
- # geom_sf(aes(fill = pcFP)) +
-  #scale_fill_gradient(name = "Proportion of households fuel poor (%) 2018", low="green",high="red")
-```
-
-### Difference in proportion Fuel Poverty 2012 to 2018
-
-```{r Creating the difference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Red indicates an increase in fuel poverty from 2012 to 2018
-#2018 has to be used as the metric for measuring fuel poverty changed in 2019
-#fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
-#fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
-#fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
-#fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
-#merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
-#names(merged_dfla)
-#merged_dfla$pc_diff <-as.numeric(merged_dfla$pc2018la)- merged_dfla$pc2012la
-#summary(merged_dfla)
-```
-
-```{r Mapping the difference in fuel poverty from 2012 to 2018}
-##BROKEN
-#merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
-#la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
-#ggplot2::ggplot(la_Fuelpov20182012dif) +
- # geom_sf(aes(fill = pc_diff)) +
-  #scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
-#labs(caption="Solent (all LA)")
-```
-
 # Mapping the Middle Layer Super Output Areas (MSOA)
@@
 ```
-
-## Mapping Commercial
-### Mapping Electricty
-####2019
-```{r Loading in the MSOA electricity consumption data for industry }
-# electricity consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
-msoa_elecDatanondom <- readr::read_csv(inFile)
-head(msoa_elecDatanondom)
-```
-
-```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
-msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Difference from 2010 to 2019
-
-### Mapping Gas
-####2019
-```{r Loading in the MSOA gas consumption data for industry }
-# gas consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
-msoa_gasDatanondom <- readr::read_csv(inFile)
-head(msoa_gasDatanondom)
-```
-
-```{r Mapping the gas consumption of the MSOAs Industrial Sector}
-msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> The holes tell you where there is no non-domestic gas use
-
-####Mapping the difference in non domestic gas from 2010 to 2019
-
-here here here
-
-# Mapping the Lower Layer Super Output Area (LSOA)
-
-## Mapping Domestic
-
-### Mapping Electricity consumption
-####2019
-```{r Loading in the LSOA electricty consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
-lsoa_elecData <- readr::read_csv(inFile)
-lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_elecData)
-```
-
-```{r Loading in boundary data for the LSOA}
-#The LSOA boundaries for the Solent have been pre-downloaded
-inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
-message ("Loading LSOA boundaries from file")
-lsoa_sf_data <- sf::read_sf(inf)
-head(lsoa_sf_data)
-table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
-```
-
-```{r Mapping the electricty consumption of the LSOAs}
-lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-
-##### Looking at cities in more detail        
-```{r Southampton LSOA Elec}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
-
-# plotting the electricity consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Elec}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the electricity consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Elec}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")
-
-# plotting the electricity consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference between 2010 and 2019
-
-#####Cities in more detail
-
-### Mapping Gas
-####2019
-```{r Loading in the LSOA gas consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
-lsoa_gasData <- readr::read_csv(inFile)
-lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_gasData)
-```
-
-```{r Mapping the gas consumption of the LSOAs}
-lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-> Aha - this one shows where there is no gas :-)
-
-#####Cities in More detail
-```{r Southampton LSOA Gas}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
-
-# plotting the gas consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Gas}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
-
-# plotting the gas consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Gas}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
-
-# plotting the gas consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-### Mapping the Indices of Multiple Deprivation
-####2019
-```{r Loading in the Indices of Multiple Deprivation data}
-# Multiple deprivation data at MSOA pre downloaded
-inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
-lsoa_multidep <- readr::read_csv (inFile)
-head(lsoa_multidep)
-```
-
-```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
-head(lsoa_multidep)
-lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Indices of dep}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
-
-# plotting the multiple scales on dep of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Indices of dep}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Indices of dep}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")
-
-# plotting the indices of dep 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference from 2010 to 2019
-
-### Mapping Fuel Poverty
-#### 2019
-```{r Loading in the LSOA 2019 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2019<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2019)
-```
-
-```{r Mapping the LSOA 2019 Fuel Poverty}
-lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
-  geom_sf(aes(fill=pcFP))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2019}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Fuel Pov 2019}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Fuel Pov}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-
-#### 2018
-```{r Loading in the LSOA 2018 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2018<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2018)
-```
-
-```{r Mapping the LSOA 2018 Fuel Poverty}
-lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
-  geom_sf(aes(fill=pcFP18))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs) 2018")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton 2018")
-```
-```{r Portsmouth LSOA Fuel Pov 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth 2018")
-```
-```{r Winchester LOSA Fuel Pov 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester 2018")
-```
-####Mapping the difference in proportion of fuel poverty from 2012 to 2018
-```{r Creating the dfference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Had to use 2018 as the metric for fuel poverty has changed in 2019 
-#Red indicates an increase in fuel poverty from 2012 to 2018
-fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
-fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
-merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
-names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
-summary(merged_df)
-```
-```{r Mapping the change in Fuel Poverty}
-merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
-ggplot2::ggplot(lsoa_fuelpov20122018) +
-  geom_sf(aes(fill=pc_diff))+ 
-  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-##### Looking at cities in more detail
-```{r Southampton LSOA Fuel Pov 2012 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-#Around Bargate and Freemantle increased fuel poverty
-```
-```{r Portsmouth LSOA Fuel Pov 2012 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-#Charles Dickens increased fuel poverty
-```
-```{r Winchester LSOA Fuel Pov 2012 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
-
-# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Splitting them out MSOA non domestic Elec and Gas

--- 2021-08-09 Solent_Mapping_v2.Rmd
@@
 
-# Mapping the Local Authority
-##Mapping Domestic Electricity Consumption
-```{r loading in Local Authority electricity consumption data}
-#inFile <-paste0(dataFolder, "energy/Subnational_electricity_consumption_statistics_2019.csv")
-#la_elecData <- readr::read_csv(inFile)
-#summary(la_elecData)
-```
-
-```{r Loading in the Boundary Data for local authorities we are intrested in}
-# geo_query <- "https://ons-inspire.esriuk.com/arcgis/rest/services/Administrative_Boundaries/Local_Authority_Districts_December_2018_Boundaries_UK_BGC/MapServer/0/query?where=lad18nm%20IN%20(%27Southampton%27,%27Portsmouth%27,%27Winchester%27,%27Eastleigh%27,%27Isle%20of%20Wight%27,%27Fareham%27,%27Gosport%27,%27Test%20Valley%27,%27East%20Hampshire%27,%27Havant%27,%27New%20Forest%27,%27Hart%27,%27Basingstoke%20and%20Deane%27)&outFields=lad18cd,lad18nm,long,lat&outSR=4326&f=geojson"
-# #This only includes the ones we are interested in i.e the Solent
-# message("Loading LA geometry from ONS Open Geography API") #Specifying the location message
-# la_sf_data <- sf::st_read(geo_query)
-
-# The above is very clever but it takes time
-# Load from file
-#la_shpFile <- paste0(dataFolder, "/boundaries/LA/la_solent.shp")
-#la_sf_data <- sf::st_read(la_shpFile)
-#]head(la_sf_data)
-```
-
-```{r Mapping the local authority electricty consumption}
-#la_elecData$lad18cd <- la_elecData$`LA Code`#Creating a variable with the local authority code in the same name of the consumption data
-#la_merged_sf <- merge(la_sf_data, la_elecData)#Merge the local Authority boundaries and the consumption data
-#ggplot2::ggplot(la_merged_sf) +
- # geom_sf(aes(fill = Total_GWh))+scale_fill_gradient(low="green",high="red")
-
-```
-## Mapping Transport
-### Freight
-```{r Loading the  Freight Transport consumption data for the Local Autority}
-#inFile <-paste0(dataFolder, "energy/Local Authority level Transport data.csv")
-#la_Transport <- readr::read_csv(inFile)
-#summary(la_Transport)
-#head(la_Transport)
-```
-
-```{r Mapping the local authority energy consumption (Freight)}
-
-#la_Transport$lad18cd <- la_Transport$Code # Creating a variable with the local authority code in the same name of the consumption data
-#la_merged_Transp <- merge(la_sf_data, la_Transport)# Merge the local Authority boundaries and the Transport data
-#ggplot2::ggplot(la_merged_Transp) +
- # geom_sf(aes(fill = Freight)) +
-  #scale_fill_gradient(name = "Freight: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red")
-```
-
-### Personal
-Note: this data is not per household/person so it will correlate (to some extent) with population size.
-
-```{r Mapping the local authority energy consumption (Personal)}
-# re-use the merged dataset
-#ggplot2::ggplot(la_merged_Transp) +
- # geom_sf(aes(fill = Personal)) +
-  #scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
-```
-## Mapping Fuel Poverty 
-### 2019
-
-```{r Loading in the 2019 Local Authority Fuel Poverty Data}
-#inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
-#la_fuelpov_2019<-readr::read_csv(inFile)
-#head(la_fuelpov_2019)
-```
-```{r Mapping Local Authority Fuel Poverty 2019}
-#la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
-#la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
-#la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-#ggplot2::ggplot(la_merged_Fuelpov2019) +
- # geom_sf(aes(fill = pcFP)) +
-  #scale_fill_gradient(name = "Proportion of households fuel poor (%) 2019", low="green",high="red")
-```
-###2018
-```{r Loading in the 2018 Local Authority Fuel Poverty Data}
-#inFile<-paste0(dataFolder, "Fuel Poverty/2018 LA_Fuel_Poverty.csv")
-#la_fuelpov_2018<-readr::read_csv(inFile)
-#head(la_fuelpov_2018)
-```
-```{r Mapping Local Authority Fuel Poverty 2018}
-#la_fuelpov_2018$lad18cd <- la_fuelpov_2018$`Area Code` # Creating a variable with the local authority code in the same name 
-#la_merged_Fuelpov2018 <- merge(la_sf_data, la_fuelpov_2018)# Merge the local Authority boundaries and the Fuel Poverty data
-#la_merged_Fuelpov2018$pcFP <- as.numeric(la_merged_Fuelpov2018$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
-#ggplot2::ggplot(la_merged_Fuelpov2019) +
- # geom_sf(aes(fill = pcFP)) +
-  #scale_fill_gradient(name = "Proportion of households fuel poor (%) 2018", low="green",high="red")
-```
-
-### Difference in proportion Fuel Poverty 2012 to 2018
-
-```{r Creating the difference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Red indicates an increase in fuel poverty from 2012 to 2018
-#2018 has to be used as the metric for measuring fuel poverty changed in 2019
-#fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
-#fp_LA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LA_Fuel_Poverty.csv"))
-#fp_LA_2012_df$pc2012la <- fp_LA_2012_df$`Proportion of households fuel poor (%) 2012`
-#fp_LA_2018_df$pc2018la <- fp_LA_2018_df$`Proportion of households fuel poor (%)`
-#merged_dfla <- merge(fp_LA_2012_df, fp_LA_2018_df, by = "LA Code", all = TRUE)
-#names(merged_dfla)
-#merged_dfla$pc_diff <-as.numeric(merged_dfla$pc2018la)- merged_dfla$pc2012la
-#summary(merged_dfla)
-```
-
-```{r Mapping the difference in fuel poverty from 2012 to 2018}
-#merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
-#la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
-#ggplot2::ggplot(la_Fuelpov20182012dif) +
- # geom_sf(aes(fill = pc_diff)) +
-  #scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
-#labs(caption="Solent (all LA)")
-```
-
 # Mapping the Middle Layer Super Output Areas (MSOA)
-## Mapping Domestic
-### Mapping the Electricity Consumption
-####2019
-```{r Loading in the MSOA electricity consumption data}
-# electricity consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_DOM_ELEC_2019.csv")
-msoa_elecData <- readr::read_csv(inFile)
-head(msoa_elecData)
-```
 

### 2021-08-09 LSOA Deprevation.Rmd
Splitting it out LSOA Deprevation

--- 2021-08-09 MSOA non domestic Elec and Gas.Rmd
@@
 
-# Mapping the Middle Layer Super Output Areas (MSOA)
-
-```{r Loading in the Boundary Data for the MSOA}
-inf <-paste0(dataFolder, "boundaries/MSOA/msoa_solent.shp")
-message("Loading Middle Layer Super Output Area (MSOA) from file")
-#When using shp files you might also need to have other supplementary files in the same folder to allow it to run https://cfss.uchicago.edu/notes/simple-features/
-msoa_sf_data <- sf::read_sf(inf) 
-head (msoa_sf_data)
-table(msoa_sf_data$LAD11NM)#how many MSOAs are in each LA
-```
-
-```{r Mapping the electrcity consumption of the MSOAs}
-msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
-msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
-ggplot2::ggplot(msoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Mapping the change from 2010 to 2019
-```{r Creating the difference in MSOA mean dom elec consumption variable}
-domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_DOM_ELEC_2010.csv"))
-domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "/energy/MSOA_DOM_ELEC_2019.csv"))
-domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
-domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
-merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE) ##BROKEN
-names(merged_domelec)
-merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
-summary(merged_domelec)
-```
-```{r Mapping the MSOA difference in mean dom elec consumption}
-merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
-msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
-ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton of domestic electricty per meter (kWh per meter",low="green",high="red")+labs(caption="Solent(all MSOAs)")
-```
-
-### Mapping the Gas
-####2019
-```{r Loading in the MSOA gas consumption data}
-# gas consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
-msoa_gasData <- readr::read_csv(inFile)
-head(msoa_gasData)
-```
-```{r Mapping the gas consumption of the MSOAs}
-msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
-ggplot2::ggplot(msoa_merged_sf_domgas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> Does this match to non-gas areas??
-
-####Mapping the change in gas consumption from 2010 to 2019
-```{r Creating the dfference in consumption variable}
-#Green indicates a decrease in gas consumption from 2010 to 2019
-#Red indicates an increase in gas consumption from 2010 to 2019
-domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
-domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
-domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`
-domgas_MSOA_2019$domgas2019 <- domgas_MSOA_2019$`Mean consumption (kWh per meter)`
-merged_domgas <- merge(domgas_MSOA_2010, domgas_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
-names(merged_domgas)
-merged_domgas$mc_diff <-  as.numeric(merged_domgas$domgas2019) - merged_domgas$domgas2010
-summary(merged_domgas)
-```
-
-```{r Mapping the change in dom mean gas comsumption}
-merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
-ggplot2::ggplot(msoa_domgas20102019) +
-  geom_sf(aes(fill=mc_diff))+ 
-  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
-##BROKEN
-```
-
-## Mapping Commercial
-### Mapping Electricty
-####2019
-```{r Loading in the MSOA electricity consumption data for industry }
-# electricity consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
-msoa_elecDatanondom <- readr::read_csv(inFile)
-head(msoa_elecDatanondom)
-```
-
-```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
-msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Difference from 2010 to 2019
-```{r Creating the mean electricty consumption from the industrial sector MOSA}
-##BROKEN
-NONDOMELEC_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
-NONDOMELEC_MSOA_2019<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
-NONDOMELEC_MSOA_2010$nondomelec2010 <-NONDOMELEC_MSOA_2010$' Mean consumption (kWh per meter)'                                       
-NONDOMELEC_MSOA_2019$nondomeelec2019<-NONDOMELEC_MSOA_2019$' Mean consumption (kWh per meter) '
-merged_nondomelec <-merge(NONDOMELEC_MSOA_2010, NONDOMELEC_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
-names(merged_nondomelec)
-merged_nondomelec$nondomelec_diff<-merged_nondomelec$nondomeelec2019 - merged_nondomelec$nondomeelec2010
-summary(merged_nondomelec)
-```
-```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
-merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
-msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
-ggplot2::ggplot(msoa_nondom20102019) +
-  geom_sf(aes(fill=nondom_diff))+ 
-  scale_fill_continuous(name="Change in  mean electricty consumption for the industrial sector", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
-```
-
-### Mapping Gas
-####2019
-```{r Loading in the MSOA gas consumption data for industry }
-# gas consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
-msoa_gasDatanondom <- readr::read_csv(inFile)
-head(msoa_gasDatanondom)
-```
-
-```{r Mapping the gas consumption of the MSOAs Industrial Sector}
-msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> The holes tell you where there is no non-domestic gas use
-
-####Mapping the difference in non domestic gas from 2010 to 2019 
-```{r Creating the difference in non domestic gas consumption in the MSOA}
-nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NonDom_Gas_2010.csv"))
-nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/MSOA_NonDom_Gas_2019.csv"))
-nondomgas_msoa_2010$nondomgas2010<-nondomgas_msoa_2010$' Mean consumption (kWh per meter)'
-nondomgas_msoa_2019$nondomgas2019<-nondomgas_msoa_2019$' Mean consumption (kWh per meter)'
-merged_nondomgas20102019<-merge(nondomgas_msoa_2010, nondomgas_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
-names(merged_nondomgas20102019)
-merged_nondomgas20102019$nondomgas_diff<-merged_nondomgas20102019$nondomgas2019 - merged_nondomgas20102019$nondomgas2010 ##BROKEN
-summary(merged_nondomgas20102019)
-```
-
-```{r Mapping the change in non domestic gas usage in the MSOA}
-merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
-ggplot2::ggplot(msoa_nondomgas20102019) +
-  geom_sf(aes(fill=pc_diff))+ 
-  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
-```
-
 # Mapping the Lower Layer Super Output Area (LSOA)
-
-## Mapping Domestic
-
-### Mapping Electricity consumption
-####2019
-```{r Loading in the LSOA electricty consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
-lsoa_elecData <- readr::read_csv(inFile)
-lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_elecData)
-```
 
@@
 
-```{r Mapping the electricty consumption of the LSOAs}
-lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-
-##### Looking at cities in more detail        
-```{r Southampton LSOA Elec}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
-
-# plotting the electricity consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Elec}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the electricity consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Elec}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")
-
-# plotting the electricity consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference between 2010 and 2019
-
-#####Cities in more detail
-
-### Mapping Gas
-####2019
-```{r Loading in the LSOA gas consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
-lsoa_gasData <- readr::read_csv(inFile)
-lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_gasData)
-```
-
-```{r Mapping the gas consumption of the LSOAs}
-lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-> Aha - this one shows where there is no gas :-)
-
-#####Cities in More detail
-```{r Southampton LSOA Gas}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
-
-# plotting the gas consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Gas}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
-
-# plotting the gas consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Gas}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
-
-# plotting the gas consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
 ### Mapping the Indices of Multiple Deprivation
@@
 
-### Mapping Fuel Poverty
-#### 2019
-```{r Loading in the LSOA 2019 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2019<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2019)
-```
+here
 
-```{r Mapping the LSOA 2019 Fuel Poverty}
-lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
-  geom_sf(aes(fill=pcFP))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
 #####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2019}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Fuel Pov 2019}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Fuel Pov}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-
-#### 2018
-```{r Loading in the LSOA 2018 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2018<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2018)
-```
-
-```{r Mapping the LSOA 2018 Fuel Poverty}
-lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
-  geom_sf(aes(fill=pcFP18))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs) 2018")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton 2018")
-```
-```{r Portsmouth LSOA Fuel Pov 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth 2018")
-```
-```{r Winchester LOSA Fuel Pov 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester 2018")
-```
-####Mapping the difference in proportion of fuel poverty from 2012 to 2018
-```{r Creating the dfference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Had to use 2018 as the metric for fuel poverty has changed in 2019 
-#Red indicates an increase in fuel poverty from 2012 to 2018
-fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
-fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
-merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
-names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
-summary(merged_df)
-```
-```{r Mapping the change in Fuel Poverty}
-merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
-ggplot2::ggplot(lsoa_fuelpov20122018) +
-  geom_sf(aes(fill=pc_diff))+ 
-  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-##### Looking at cities in more detail
-```{r Southampton LSOA Fuel Pov 2012 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-#Around Bargate and Freemantle increased fuel poverty
-```
-```{r Portsmouth LSOA Fuel Pov 2012 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-#Charles Dickens increased fuel poverty
-```
-```{r Winchester LSOA Fuel Pov 2012 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
-
-# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```

### 2021-08-09 LSOA Fuel poverty.Rmd
Splitting it out LSOA Fuel Poverty

--- 2021-08-09 MSOA non domestic Elec and Gas.Rmd
@@
 ```
-
-```{r Mapping the electricty consumption of the LSOAs}
-lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-
-##### Looking at cities in more detail        
-```{r Southampton LSOA Elec}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
-
-# plotting the electricity consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Elec}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the electricity consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Elec}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")
-
-# plotting the electricity consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference between 2010 and 2019
-
-#####Cities in more detail
-
-### Mapping Gas
-####2019
-```{r Loading in the LSOA gas consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
-lsoa_gasData <- readr::read_csv(inFile)
-lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_gasData)
-```
-
-```{r Mapping the gas consumption of the LSOAs}
-lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-> Aha - this one shows where there is no gas :-)
-
-#####Cities in More detail
-```{r Southampton LSOA Gas}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
-
-# plotting the gas consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Gas}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
-
-# plotting the gas consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Gas}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
-
-# plotting the gas consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-### Mapping the Indices of Multiple Deprivation
-####2019
-```{r Loading in the Indices of Multiple Deprivation data}
-# Multiple deprivation data at MSOA pre downloaded
-inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
-lsoa_multidep <- readr::read_csv (inFile)
-head(lsoa_multidep)
-```
-
-```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
-head(lsoa_multidep)
-lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Indices of dep}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
-
-# plotting the multiple scales on dep of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Indices of dep}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Indices of dep}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")
-
-# plotting the indices of dep 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference from 2010 to 2019
 

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Changing title

@@
 ---
-title: "Solent region: Test Maps"
+title: "MSOA domestic Electricty and Gas maps"
 author: "Meghan Kinglsey-Walsh"

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Fixed all errors and knitted

@@
 domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
-merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE) ##BROKEN
+merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
 names(merged_domelec)
@@
 ```{r Mapping the change in dom mean gas comsumption}
-merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
+merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
 msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
@@
   labs(caption ="Solent (all MSOAs)")
-##BROKEN
 ```

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Checking the files has everything it needs to run

@@
 ---
-title: "Solent region: Test Maps"
+title: "MSOA Industrial Electricty and Gas maps"
 author: "Meghan Kinglsey-Walsh"
@@
 
-```{r Mapping the electrcity consumption of the MSOAs}
-msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
-msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
-ggplot2::ggplot(msoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-####Mapping the change from 2010 to 2019
-```{r Creating the difference in MSOA mean dom elec consumption variable}
-domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_DOM_ELEC_2010.csv"))
-domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "/energy/MSOA_DOM_ELEC_2019.csv"))
-domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
-domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
-merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE) ##BROKEN
-names(merged_domelec)
-merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
-summary(merged_domelec)
-```
-```{r Mapping the MSOA difference in mean dom elec consumption}
-merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
-msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
-ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton of domestic electricty per meter (kWh per meter",low="green",high="red")+labs(caption="Solent(all MSOAs)")
-```
-
-### Mapping the Gas
-####2019
-```{r Loading in the MSOA gas consumption data}
-# gas consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
-msoa_gasData <- readr::read_csv(inFile)
-head(msoa_gasData)
-```
-```{r Mapping the gas consumption of the MSOAs}
-msoa_gasData$MSOA11CD <- msoa_gasData$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_domgas <-merge(msoa_sf_data, msoa_gasData)
-ggplot2::ggplot(msoa_merged_sf_domgas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all MSOAs)")
-#mapping it
-```
-> Does this match to non-gas areas??
-
-####Mapping the change in gas consumption from 2010 to 2019
-```{r Creating the dfference in consumption variable}
-#Green indicates a decrease in gas consumption from 2010 to 2019
-#Red indicates an increase in gas consumption from 2010 to 2019
-domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
-domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
-domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`
-domgas_MSOA_2019$domgas2019 <- domgas_MSOA_2019$`Mean consumption (kWh per meter)`
-merged_domgas <- merge(domgas_MSOA_2010, domgas_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
-names(merged_domgas)
-merged_domgas$mc_diff <-  as.numeric(merged_domgas$domgas2019) - merged_domgas$domgas2010
-summary(merged_domgas)
-```
-
-```{r Mapping the change in dom mean gas comsumption}
-merged_domgas$MSOA11CD <- merged_domgas$"MSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
-ggplot2::ggplot(msoa_domgas20102019) +
-  geom_sf(aes(fill=mc_diff))+ 
-  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
-##BROKEN
-```
-
 ## Mapping Commercial
@@
 ```
-
 ### Mapping Gas
@@
 ```
-
-# Mapping the Lower Layer Super Output Area (LSOA)
-
-## Mapping Domestic
-
-### Mapping Electricity consumption
-####2019
-```{r Loading in the LSOA electricty consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
-lsoa_elecData <- readr::read_csv(inFile)
-lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_elecData)
-```
-
-```{r Loading in boundary data for the LSOA}
-#The LSOA boundaries for the Solent have been pre-downloaded
-inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
-message ("Loading LSOA boundaries from file")
-lsoa_sf_data <- sf::read_sf(inf)
-head(lsoa_sf_data)
-table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
-```
-
-```{r Mapping the electricty consumption of the LSOAs}
-lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-
-##### Looking at cities in more detail        
-```{r Southampton LSOA Elec}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
-
-# plotting the electricity consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Elec}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the electricity consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Elec}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")
-
-# plotting the electricity consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference between 2010 and 2019
-
-#####Cities in more detail
-
-### Mapping Gas
-####2019
-```{r Loading in the LSOA gas consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
-lsoa_gasData <- readr::read_csv(inFile)
-lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_gasData)
-```
-
-```{r Mapping the gas consumption of the LSOAs}
-lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-> Aha - this one shows where there is no gas :-)
-
-#####Cities in More detail
-```{r Southampton LSOA Gas}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
-
-# plotting the gas consumption of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Gas}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
-
-# plotting the gas consumption of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Gas}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
-
-# plotting the gas consumption of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
-  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-### Mapping the Indices of Multiple Deprivation
-####2019
-```{r Loading in the Indices of Multiple Deprivation data}
-# Multiple deprivation data at MSOA pre downloaded
-inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
-lsoa_multidep <- readr::read_csv (inFile)
-head(lsoa_multidep)
-```
-
-```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
-head(lsoa_multidep)
-lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Indices of dep}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
-
-# plotting the multiple scales on dep of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Indices of dep}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")
-
-# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Indices of dep}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")
-
-# plotting the indices of dep 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
-  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-####Difference from 2010 to 2019
-
-### Mapping Fuel Poverty
-#### 2019
-```{r Loading in the LSOA 2019 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2019<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2019)
-```
-
-```{r Mapping the LSOA 2019 Fuel Poverty}
-lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
-  geom_sf(aes(fill=pcFP))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2019}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-```
-```{r Portsmouth LSOA Fuel Pov 2019}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-```
-```{r Winchester LSOA Fuel Pov}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```
-
-#### 2018
-```{r Loading in the LSOA 2018 Fuel Poverty data}
-inFile<-paste0(dataFolder, "Fuel Poverty/2018 LSOA_Fuel_Poverty.csv")
-lsoa_fuelpov_2018<-readr::read_csv (inFile)
-head(lsoa_fuelpov_2018)
-```
-
-```{r Mapping the LSOA 2018 Fuel Poverty}
-lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
-# as above - why does it load as a char?
-lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
-ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
-  geom_sf(aes(fill=pcFP18))+ 
-  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs) 2018")
-```
-#####Looking at the cities in more detail
-```{r Southampton LSOA Fuel Pov 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")
-
-# plotting the fuel poverty 2019 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton 2018")
-```
-```{r Portsmouth LSOA Fuel Pov 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth 2018")
-```
-```{r Winchester LOSA Fuel Pov 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
-
-# plotting the fuel poverty 2019 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pcFP18)) +
-  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester 2018")
-```
-####Mapping the difference in proportion of fuel poverty from 2012 to 2018
-```{r Creating the dfference in proportion variable}
-#Green indicates a smaller increase in fuel poverty from 2012 to 2018
-#Had to use 2018 as the metric for fuel poverty has changed in 2019 
-#Red indicates an increase in fuel poverty from 2012 to 2018
-fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
-fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
-merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
-names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
-summary(merged_df)
-```
-```{r Mapping the change in Fuel Poverty}
-merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
-ggplot2::ggplot(lsoa_fuelpov20122018) +
-  geom_sf(aes(fill=pc_diff))+ 
-  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
-```
-##### Looking at cities in more detail
-```{r Southampton LSOA Fuel Pov 2012 2018}
-#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")
-
-# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Southampton")
-#Around Bargate and Freemantle increased fuel poverty
-```
-```{r Portsmouth LSOA Fuel Pov 2012 2018}
-#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")
-
-# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
-#Charles Dickens increased fuel poverty
-```
-```{r Winchester LSOA Fuel Pov 2012 2018}
-#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
-
-# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
-ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
-  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
-  labs(caption = "Winchester")
-```

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Pushing again

@@
 ```
+##END

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Changing graph title to make map bigger

@@
 msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
-ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton of domestic electricty per meter (kWh per meter",low="green",high="red")+labs(caption="Solent(all MSOAs)")
+ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
 ```

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Changing elec variable name

@@
 ##BROKEN
-NONDOMELEC_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
-NONDOMELEC_MSOA_2019<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
-NONDOMELEC_MSOA_2010$nondomelec2010 <-NONDOMELEC_MSOA_2010$' Mean consumption (kWh per meter)'                                       
-NONDOMELEC_MSOA_2019$nondomeelec2019<-NONDOMELEC_MSOA_2019$' Mean consumption (kWh per meter) '
-merged_nondomelec <-merge(NONDOMELEC_MSOA_2010, NONDOMELEC_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
-names(merged_nondomelec)
-merged_nondomelec$nondomelec_diff<-merged_nondomelec$nondomeelec2019 - merged_nondomelec$nondomeelec2010
-summary(merged_nondomelec)
+ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
+ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
+ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
+ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
+merged_nondomelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_ndelec)
+merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010
+summary(merged_ndelec)
 ```

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Fixed part of the Electricty error

@@
 ```{r Creating the mean electricty consumption from the industrial sector MOSA}
+ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv"))
+ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv"))
+ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
+ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
+merged_ndelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_ndelec)
+merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010
+summary(merged_ndelec)
+```
+
+```{r Creating the mean electricty consumption from the industrial sector MOSA}
 ##BROKEN
-ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
-ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
+ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv"))
+ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv"))
 ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Changing file paths

@@
 # electricity consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_DOM_ELEC_2019.csv")
+inFile <-paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv")
 msoa_elecData <- readr::read_csv(inFile)
@@
 ```{r Creating the difference in MSOA mean dom elec consumption variable}
-domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_DOM_ELEC_2010.csv"))
-domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "/energy/MSOA_DOM_ELEC_2019.csv"))
+domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"))
+domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
 domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
@@
 # gas consumption data at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_GAS_2019.csv")
+inFile <-paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2019.csv")
 msoa_gasData <- readr::read_csv(inFile)
@@
 #Red indicates an increase in gas consumption from 2010 to 2019
-domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2010.csv"))
-domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "/energy/MSOA_GAS_2019.csv"))
+domgas_MSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2010.csv"))
+domgas_MSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/MSOA Dom Gas csv/MSOA_GAS_2019.csv"))
 domgas_MSOA_2010$domgas2010 <- domgas_MSOA_2010$`Mean consumption (kWh per meter)`

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Changing path names

--- 2021-08-09 MSOA non domestic Elec and Gas.Rmd
@@
 # electricity consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NONDOM_2019.csv")
+inFile <-paste0(dataFolder, "energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv")
 msoa_elecDatanondom <- readr::read_csv(inFile)
@@
 ```{r Creating the mean electricty consumption from the industrial sector MOSA}
-##BROKEN
-ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
-ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
+ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
+ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
+ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
+ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
+merged_ndelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_ndelec)
+merged_ndelec$ndelec_diff<-(as.numeric(merged_ndelec$ndelec2019))-(as.numeric(merged_ndelec$ndelec2010))
+summary(merged_ndelec)
+```
+
+```{r Creating the mean electricty consumption from the industrial sector MOSA}
+ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
+ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
 ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
@@
 names(merged_ndelec)
-merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010
+merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010 ##BROKEN
 summary(merged_ndelec)
@@
 # gas consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
+inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
 msoa_gasDatanondom <- readr::read_csv(inFile)
@@
 ```{r Creating the difference in non domestic gas consumption in the MSOA}
-nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NonDom_Gas_2010.csv"))
-nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/MSOA_NonDom_Gas_2019.csv"))
+nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
+nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
 nondomgas_msoa_2010$nondomgas2010<-nondomgas_msoa_2010$' Mean consumption (kWh per meter)'

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Changed so the first column of 2010 electricty data is skipped

@@
 ```{r Creating the difference in MSOA mean dom elec consumption variable}
-domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"))
+domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"),skip = 1)
 domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))

### 2021-08-09 LSOA domestic Elec and Gas.Rmd
Changing files paths and title

@@
 ---
-title: "Solent region: Test Maps"
+title: "LSOA domestic Electricty and Gas maps"
 author: "Meghan Kinglsey-Walsh"
@@
 #Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
+inFile <-paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv")
 lsoa_elecData <- readr::read_csv(inFile)
@@
 #Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
+inFile <-paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv")
 lsoa_gasData <- readr::read_csv(inFile)

### 2021-08-09 LSOA Deprevation.Rmd
changing title

@@
 ---
-title: "Solent region: Test Maps"
+title: "LSOA Deprevation maps"
 author: "Meghan Kinglsey-Walsh"
@@
 ```
+
 #####Looking at the cities in more detail

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Solved some of the errors

--- 2021-08-09 MSOA non domestic Elec and Gas.Rmd
@@
 ```{r Creating the mean electricty consumption from the industrial sector MOSA}
-##BROKEN
-ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
-ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
+ndelec_msoa_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
+ndelec_msoa_2019<-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
+ndelec_msoa_2010$ndelec2010<-ndelec_msoa_2010$'Mean consumption (kWh per meter)'                                       
+ndelec_msoa_2019$ndelec2019<-ndelec_msoa_2019$'Mean consumption (kWh per meter)'
+merged_ndelec<-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_ndelec)
+merged_ndelec$ndelec_diff<-(as.numeric(merged_ndelec$ndelec2019))-(as.numeric(merged_ndelec$ndelec2010))
+summary(merged_ndelec)
+```
+
+```{r Creating the mean electricty consumption from the industrial sector MOSA}
+ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
+ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
 ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
@@
 names(merged_ndelec)
-merged_ndelec$ndelec_diff<-merged_ndelec$ndelec2019 - merged_ndelec$ndelec2010
+merged_ndelec$ndelec_diff<-as.numeric(merged_ndelec$ndelec2019) - as.numeric(merged_ndelec$ndelec2010) ##BROKEN
 summary(merged_ndelec)
@@
 ```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
-merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
-msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
-ggplot2::ggplot(msoa_nondom20102019) +
-  geom_sf(aes(fill=nondom_diff))+ 
+merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
+msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
+ggplot2::ggplot(msoa_nd20102019) +
+  geom_sf(aes(fill=" Mean consumption (kWh per meter)"))+ 
   scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
@@
 # gas consumption data for industry at MSOA level (pre downloaded)
-inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
-msoa_gasDatanondom <- readr::read_csv(inFile)
-head(msoa_gasDatanondom)
+inFile <-paste0(dataFolder, "energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv")
+msoa_ndgas <- readr::read_csv(inFile)
+head(msoa_ndgas)
 ```
@@
 ```{r Mapping the gas consumption of the MSOAs Industrial Sector}
-msoa_gasDatanondom$MSOA11CD <- msoa_gasDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
-msoa_merged_sf_nondom_gas <-merge(msoa_sf_data, msoa_gasDatanondom)
-ggplot2::ggplot(msoa_merged_sf_nondom_gas) + 
+msoa_ndgas$MSOA11CD <- msoa_ndgas$'Middle Layer Super Output Area (MSOA) Code' 
+msoa_merged_ndgas <-merge(msoa_sf_data, msoa_ndgas)
+ggplot2::ggplot(msoa_merged_ndgas) + 
   geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
@@
 ```{r Creating the difference in non domestic gas consumption in the MSOA}
-nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NonDom_Gas_2010.csv"))
-nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/MSOA_NonDom_Gas_2019.csv"))
-nondomgas_msoa_2010$nondomgas2010<-nondomgas_msoa_2010$' Mean consumption (kWh per meter)'
-nondomgas_msoa_2019$nondomgas2019<-nondomgas_msoa_2019$' Mean consumption (kWh per meter)'
-merged_nondomgas20102019<-merge(nondomgas_msoa_2010, nondomgas_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
-names(merged_nondomgas20102019)
-merged_nondomgas20102019$nondomgas_diff<-merged_nondomgas20102019$nondomgas2019 - merged_nondomgas20102019$nondomgas2010 ##BROKEN
+msoa_2010_ndgas<-readr::read_csv(paste0(dataFolder,"/energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2010.csv"))
+msoa_2019_ndgas<-readr::read_csv(paste0(dataFolder,"energy/gas/MSOA NonDom Gas csv/MSOA_NonDom_Gas_2019.csv"))
+msoa_2010_ndgas$ndgas2010<-msoa_2010_ndgas$'Mean consumption (kWh per meter)'
+msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'
+
+merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_ndgas20102019)
+merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$nondomgas2019 - merged_nd20102019$nondomgas2010 ##BROKEN
 summary(merged_nondomgas20102019)
@@
   labs(caption ="Solent (all MSOAs)")
+##BROKEN
 ```

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Fixing some of the errors

@@
 
-```{r Creating the mean electricty consumption from the industrial sector MOSA}
-ndelec_msoa_2010 <-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2010.csv"))
-ndelec_msoa_2019 <-readr::read_csv(paste0(dataFolder,"/energy/electricity/MSOA NonDom Elec csv/MSOA_NONDOM_2019.csv"))
-ndelec_msoa_2010$ndelec2010 <-ndelec_msoa_2010$' Mean consumption (kWh per meter)'                                       
-ndelec_msoa_2019$ndelec2019 <-ndelec_msoa_2019$' Mean consumption (kWh per meter) '
-merged_nondomelec <-merge(ndelec_msoa_2010, ndelec_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
-names(merged_ndelec)
-merged_ndelec$ndelec_diff<-as.numeric(merged_ndelec$ndelec2019) - as.numeric(merged_ndelec$ndelec2010) ##BROKEN
-summary(merged_ndelec)
-```
 ```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Highlighting Broken sections

@@
   scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
+  labs(caption ="Solent (all MSOAs)")#BROKEN
 ```

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Fixed one error!

--- 2021-08-09 MSOA non domestic Elec and Gas.Rmd
@@
 msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
-ggplot2::ggplot(msoa_nd20102019) +
-  geom_sf(aes(fill=" Mean consumption (kWh per meter)"))+ 
-  scale_fill_continuous(name="Change in mean electricty consumption for the industrial sector", low="green",high="red")+
-  labs(caption ="Solent (all MSOAs)")
+ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")
+```
+```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
+merged_ndelec$MSOA11CD<-merged_ndelec$"Middle Layer Super Output Area (MSOA) Code"
+msoa_nd20102019<-merge(msoa_sf_data, merged_ndelec) #merging these
+ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff/ndelec2010))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")##Why does this look like this?
+Increased efficiency?
+Businesses closing down?
 ```
@@
 msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'
-
 merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
@@
 ggplot2::ggplot(msoa_nondomgas20102019) +
-  geom_sf(aes(fill=pc_diff))+ 
+  geom_sf(aes(fill=ndgas_diff))+ 
   scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+

### 2021-08-09 MSOA non domestic Elec and Gas.Rmd
Adding in cities in more detail

@@
 ```
+#####Cities in more detail
+```{r Southampton MSOA difference in non dom Elec}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Southampton")
+# plotting the electricity consumption of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
+  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Portsmouth LSOA difference in dom Elec}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Portsmouth")
+# plotting the electricity consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
+  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester LSOA difference in dom Elec}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(msoa_nd20102019, LAD11NM == "Winchester")
+# plotting the electricity consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = ndelec_diff/ndelec2010)) +
+  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```
 ### Mapping Gas

### 2021-08-10 LSOA domestic Elec and Gas.Rmd
Filling in the gaps for cities in more detail

@@
 mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
-
 # plotting the electricity consumption of Southampton in more detail
@@
 mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
-
 # plotting the electricity consumption of Portsmouth in more detail
@@
 ####Difference between 2010 and 2019 dom elec
+```{r Creating the difference in LSOA mean dom elec consumption variable}
+domelec_LSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
+domelec_LSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
+domelec_LSOA_2010$de2010<-domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter).x'
+domelec_LSOA_2019$de2019<-domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter).y'
+merged_de<-merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_de)
+merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010)##BROKEN
+summary(merged_de)
+```
 
-here here
+```{r Mapping the LSOA difference in mean dom elec consumption}
+merged_de$LSOA11CD<-merged_de$"Middle Layer Super Output Area (MSOA) Code"
+lsoa_de20102019<-merge(lsoa_sf_data, merged_de)
+ggplot2::ggplot(lsoa_de20102019)+geom_sf(aes(fill="de_diff")+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)"),low="green",high="red")+labs(caption="Solent(all LSOAs)")
+##BROKEN
+```
 
 #####Cities in more detail
-
-here here here
+```{r Southampton LSOA difference in dom Elec}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(merged_de, LAD11NM == "Southampton")
+# plotting the electricity consumption of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `de_diff`)) +
+  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Portsmouth LSOA difference in dom Elec}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(merged_de, LAD11NM == "Portsmouth")
+# plotting the electricity consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `de-diff`)) +
+  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester LSOA difference in dom Elec}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
+# plotting the electricity consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `de_diff`)) +
+  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```
 
@@
 ####Difference between 2010 and 2019 dom gas 
+```{r Creating the dfference in LSOA dom gas consumption variable}
+#Green indicates a decrease in gas consumption from 2010 to 2019
+#Red indicates an increase in gas consumption from 2010 to 2019
+dgas_LSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2010.csv"))
+dgas_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv"))
+dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$`Mean consumption (kWh per meter)`
+dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$`Mean consumption (kWh per meter)`
+merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
+names(merged_dgas)
+merged_dgas$dg_diff<-as.numeric(merged_dgas$dgas2019) - merged_dgas$dgas2010
+summary(merged_dgas)
+```
 
-here here here
+```{r Mapping the change in LSOA dom mean gas comsumption}
+merged_dgas$LSOA11CD <- merged_dgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
+ggplot2::ggplot(merged_dgas) +
+  geom_sf(aes(fill=dg_diff))+ 
+  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
+  labs(caption ="Solent (all MSOAs)") ##BROKEN
+```
 
 #####Cities in more detail
+```{r Southampton LSOA Gas}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
 
-here here here
+# plotting the gas consumption of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Portsmouth LSOA Gas}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
+
+# plotting the gas consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester LSOA Gas}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
+
+# plotting the gas consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```

### 2021-08-10 LSOA Deprevation.Rmd
Adding the difference in IMD score map

@@
 ```
-####Difference from 2010 to 2019
-
-here
-
+####Difference from 2015 to 2019
+```{r Creating the dfference in IMD score variable}
+imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2015.csv"))
+imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
+imd_lsoa_2015$imd2015 <- imd_lsoa_2015$`Index of Multiple Deprivation (IMD) Score`
+imd_lsoa_2015$imd2019 <- imd_lsoa_2019$`IMDScore`
+merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by = "lsoa11cd", all = TRUE)
+names(merged_imd)
+merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
+summary(merged_imd)
+```
+```{r Mapping the change in IMD Score}
+merged_imd$lsoa11cd <- merged_imd$"lsoa11cd" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
+names(lsoa_imd20152019)##BROKEN
+##ggplot2::ggplot(lsoa_imd20152019) +
+ ## geom_sf(aes(fill=mc_diff))+ 
+  ##scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
+  ##labs(caption ="Solent (all MSOAs)")
+```
 #####Looking at the cities in more detail
+```{r Southampton LSOA Gas}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(merged_imd, LAD11NM == "Southampton")
+# plotting the gas consumption of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `imd_diff`)) +
+  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Portsmouth LSOA Gas}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(merged_imd, LAD11NM == "Portsmouth")
+# plotting the gas consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `imd_diff`)) +
+  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester LSOA Gas}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(merged_imd, LAD11NM == "Winchester")
+# plotting the gas consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `imd_diff`)) +
+  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```

### 2021-08-10 LSOA Fuel poverty.Rmd
Changing title

@@
 # Mapping the Lower Layer Super Output Area (LSOA)
-
 ```{r Loading in boundary data for the LSOA}
@@
 mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
-
 # plotting the fuel poverty 2019 of Winchester in more detail

### 2021-08-17 mappingSolentWindTurbineAcceptance.Rmd
examining Michael Harper's wind turbine acceptance model outputs at LSOA level

---
title: "Southampton: Mapping Solent Wind Turbine Acceptance"
author: "Ben Anderson"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # set this to FALSE if you don't want the code in the final output

# Libraries ----
# useful R libraries
library(ggplot2)
library(data.table)

# GIS libraries
library(leaflet)
library(raster)
library(sf)
library(spData)
library(spDataLarge)

# Paramaters ----

dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/" # default for Meghan
user <- Sys.info()[[7]] # who are we logged in as?
if(user == "ben"){
  dataFolder <- path.expand("~/University of Southampton/HCC Energy Landscape Mapping project - Documents/General/data/")
}

# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
message("User: ", user)
message("dataFolder: ", dataFolder)

# Functions ----

selectSoton <- function(dt){
  # function we can re-use
  # assumes a data.table
  # assumes LA name = la_name (may need to make new var first)
  # returns just the rows that have Local Authority == Southampton
  select_dt <- dt[la_name %like% "Southampton"]
  return(select_dt)
}

selectSolent <- function(dt){
  # function we can re-use
  # assumes a data.table
  # assumes LA name = la_name (may need to make new var first)
  # returns just the rows that have Local Authority in Solent area
  select_dt <- dt[la_name == "Southampton" | 
                   la_name == "Portsmouth" |
                   la_name == "Winchester" |
                   la_name == "Eastleigh" |
                   la_name == "Isle of Wight" |
                   la_name == "Fareham" |
                   la_name == "Gosport" |
                   la_name == "Test Valley" |
                   la_name == "East Hampshire" |
                   la_name == "Havant" |
                   la_name == "New Forest" |
                   la_name == "Hart" |
                   la_name == "Basingstoke and Deane"]
  return(select_dt)
}
```

# Intro

Mapping wind turbine acceptance model data output.

Based on:

 * [Michael Harper's PhD](https://github.com/dataknut/energyMapping) project code
 * re-using Tom Rushby's [open geography and leaflet](https://dataknut.github.io/mapping-with-r/ONS-open-geography.html) example.

# Load LSOA boundaries and lookup

We need these for all maps.

```{r loadShapefile}
#The LSOA boundaries for the Solent have been pre-downloaded
inf<-paste0(dataFolder, "boundaries/LSOA/lsoa_solent.shp")
message ("Loading LSOA boundaries from file")
lsoa_sf_data <- sf::read_sf(inf)
table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
```

```{r loadLookup}
# pre-prepped names of LSOAs etc
lsoa_lookup <- data.table::fread(paste0(dataFolder, "lookups/lsoa_lookup_solent.csv"))
```

Build a simple map just to check (Figure \@ref(fig:simpleLSOAMap).

```{r simpleLSOAMap, fig.cap = "LSOA check map (shows MSOA and ward names when clicked"}

lsoa_sf_data <- merge(lsoa_sf_data, lsoa_lookup)

st_coord_sys <- sf::st_crs(lsoa_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

# transform the coord system if required
if(st_coord_sys$epsg != 4326){
 lsoa_sf_trans <- st_transform(lsoa_sf_data, "+proj=longlat +datum=WGS84")
}

leaflet(lsoa_sf_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("LSOA ", LSOA11CD,
                      "<br> MSOA: " ,MSOA11NM,
                      "<br> Ward: ", WD20NM,
                      "<br> RUC11: ", RUC11,
                      "<br> OAC: ", `Group Name`)
                      ), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

# Mapping Wind Turbine Acceptance (LSOAs)

This data is the output of a model described in https://doi.org/10.1016/j.enpol.2019.01.002. A further paper used the model to compare the West Midlands and Solent regions: https://doi.org/10.1093/ijlct/ctz006. The latter noted:

"From a resource perspective, the Solent area is highly suitable with many hilly regions and its coastal location offering high wind speeds. However, the opportunity for development is limited by National Parks and Areas of Outstanding Natural Beauty (AONB), and the sites that are located outside of these regions are largely unsuitable for development due to the demographic composition."

The model was based on a a range of physical factors as well as known constraints and a model of local social acceptability. The acceptance indices were originally estimated at 100m squares and have been aggregated to LSOAs (min, max and mean).

Figure \@ref(fig:loadTurbineModelData) maps the acceptance probabilities for the Solent region at LSOA level.

```{r loadTurbineModelData, fig.cap="Modelled wind turbin planning acceptance probabilities (LSOAs, Solent region)"}
inFile <- paste0(dataFolder, "harperWindTurbineScores/lsoa_turbine_scores.csv")
lsoa_turbineAcceptance <- data.table::fread(inFile)

# merge to the transformed sf
wt_sf_trans <- merge(lsoa_sf_trans, 
                     lsoa_turbineAcceptance[, .(LSOA11CD, min, mean, max)]) # keep just the columns we want for clarity

#h/t @tom_rushby - see also https://rstudio.github.io/leaflet/colors.html

qpal <- colorNumeric("Greens", wt_sf_trans$mean, n = 9)

l_map <- leaflet(wt_sf_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(mean),
              fillOpacity = 0.5, weight = 1.5, 
              popup = ~(paste0("LSOA ", LSOA11CD,
                      "<br> MSOA: " ,MSOA11NM,
                      "<br> Ward: ", WD20NM,
                      "<br> RUC11: ", RUC11,
                      "<br> OAC: ", `Group Name`,
                      "<br> Mean acceptance probability: ", round(mean*100), "%")), # popups clicked - format using html
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

l_map
```

As noted above, modelled wind turbine acceptance levels are low in most of the Solent region - generally due to physical/landscape constraints such as presence of two National Parks, AONBs etc. There are some interesting anomalies - some built up (urban) areas have relatively high acceptance probabilities (up to `r round(100*max(wt_sf_trans$mean))` % ).

```{r topTurbineLSOAs}
setkey(lsoa_turbineAcceptance, LSOA11CD)
lsoa_turbineAcceptance <- lsoa_turbineAcceptance[lsoa_lookup]
lsoa_turbineAcceptance[, la_name := LA11NM]
solent_lsoa_turbineAcceptance <- selectSolent(lsoa_turbineAcceptance)
t <- solent_lsoa_turbineAcceptance[, .(LSOA11CD, LSOA11NM, WD20NM,RUC11, `Group Name` , 
                                       min, mean, max)][order(-mean)]
library(kableExtra)
h <- head(t, 10)
kableExtra::kable(h) %>% kable_styling()
```

# Comparison with Domestic Electricity consumption (LSOAs)

Just for fun. As we saw, wind turbine acceptance levels are low - mostly due to physical constraints

```{r Loading data}
# load elec data for LSOA level comparisons
inFile <-paste0(dataFolder, "energy/electricity/LSOA Dom elec csv/LSOA_ELEC_2019.csv")
elec_dt <- data.table::fread(inFile)
elec_dt[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]

# merge to the transformed sf
wt_sf_trans <- merge(wt_sf_trans, 
                     elec_dt[, .(LSOA11CD, total_kWh = `Total domestic electricity consumption (kWh)`)]) # keep just the columns we want for clarity

p <- ggplot2::ggplot(wt_sf_trans, aes(x = total_kWh, y = 100*mean, colour = RUC11)) +
  geom_point() +
  labs(x = "Total domestic electricity used 2019 (kWh)",
       y = "Modelled probability of turbine acceptance (%)")

p + geom_smooth()
```

As we would probably expect, those areas with highest turbine acceptance probabilities tend to have lowest total domestic electricity use.

For even more fun, here's the plot split by OAC Group name

```{r oacPlot}
p + facet_wrap(vars(`Group Name`)) +
  theme(legend.position="bottom")
```

# The end

```{r environment}
R.Version()

```

### 2021-08-17 MSOA domestic Elec and Gas.Rmd
added leaflet example for pretty plots

@@
 ```
-##END
+
+Use leaflet version to place geo tile underlay
+
+First check co-ord system so matches leaflet
+
+```{r checkLeaflet}
+# https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
+library(leaflet)
+
+st_coord_sys <- st_crs(msoa_domgas20102019) # check coord system
+st_coord_sys$epsg # current coord system ? Leaflet wants EPSG: 4326
+
+# transform the coord system if required
+if(st_coord_sys$epsg != 4326){
+  map_df_trans <- st_transform(msoa_domgas20102019, "+proj=longlat +datum=WGS84")
+}
+```
+
+Plot the leaflet map
+
+```{r mapDiffLeaflet, fig.cap="Change in mean domestic gas kWh/meter"}
+
+#h/t @tom_rushby - see also https://rstudio.github.io/leaflet/colors.html
+
+qpal <- colorNumeric("Reds", map_df_trans$mc_diff, n = 9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%  # Add default OpenStreetMap map tiles
+  addPolygons(color = ~qpal(mc_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD), # popups clicked
+              highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
+
+## END

### 2021-08-17 mappingSolentWindTurbineAcceptance.Rmd
fixed title

@@
 ---
-title: "Southampton: Mapping Solent Wind Turbine Acceptance"
+title: "Solent: Mapping Solent Wind Turbine Acceptance"
 author: "Ben Anderson"

### 2021-08-18 LSOA Fuel poverty.Rmd
Titles Changed

@@
 ---
-title: "Solent region: Test Maps"
+title: "LOSA Fuel Poverty maps"
 author: "Meghan Kinglsey-Walsh"

### 2021-08-18 MSOA domestic Elec and Gas.Rmd
Titles Changed

--- 2021-08-09 MSOA domestic Elec and Gas.Rmd
@@
 ---
-title: "MSOA domestic Electricty and Gas maps"
+title: "MSOA domestic Electricity and Gas maps"
 author: "Meghan Kinglsey-Walsh"

### 2021-08-18 LSOA domestic Elec and Gas.Rmd
Fixing error on line 118

@@
 ```{r Creating the difference in LSOA mean dom elec consumption variable}
-domelec_LSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
-domelec_LSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
-domelec_LSOA_2010$de2010<-domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter).x'
-domelec_LSOA_2019$de2019<-domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter).y'
-merged_de<-merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+domelec_LSOA_2010 <- readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
+domelec_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
+domelec_LSOA_2010$de2010 <- domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter)'
+domelec_LSOA_2019$de2019 <- domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter)'
+merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Lower Layer Super Output Area (LSOA) Code", all=TRUE)
 names(merged_de)
-merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010)##BROKEN
+merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) ##Fixed
 summary(merged_de)
@@
 lsoa_de20102019<-merge(lsoa_sf_data, merged_de)
-ggplot2::ggplot(lsoa_de20102019)+geom_sf(aes(fill="de_diff")+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)"),low="green",high="red")+labs(caption="Solent(all LSOAs)")
+ggplot2::ggplot(lsoa_de20102019)+geom_sf(aes(fill=de_diff)+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)"),low="green",high="red")+labs(caption="Solent(all LSOAs)")
 ##BROKEN

### 2021-08-18 LSOA domestic Elec and Gas.Rmd
Fixing error drawing LSOA diff in mean dom elect consumption map

--- 2021-08-10 LSOA domestic Elec and Gas.Rmd
@@
 ```{r Creating the difference in LSOA mean dom elec consumption variable}
-domelec_LSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
-domelec_LSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
-domelec_LSOA_2010$de2010<-domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter).x'
-domelec_LSOA_2019$de2019<-domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter).y'
-merged_de<-merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+domelec_LSOA_2010 <- readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
+domelec_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
+domelec_LSOA_2010$de2010 <- domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter)'
+domelec_LSOA_2019$de2019 <- domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter)'
+# create unambiguos lsoa code for matching to each other and the sf geometry
+domelec_LSOA_2010$LSOA11CD <- domelec_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
+domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
+
+merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="LSOA11CD", all=TRUE)
 names(merged_de)
-merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010)##BROKEN
+merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) ##Fixed
 summary(merged_de)
@@
 ```{r Mapping the LSOA difference in mean dom elec consumption}
-merged_de$LSOA11CD<-merged_de$"Middle Layer Super Output Area (MSOA) Code"
-lsoa_de20102019<-merge(lsoa_sf_data, merged_de)
-ggplot2::ggplot(lsoa_de20102019)+geom_sf(aes(fill="de_diff")+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)"),low="green",high="red")+labs(caption="Solent(all LSOAs)")
-##BROKEN
+# merge to sf geometry on LSOA11CD
+lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
+ggplot2::ggplot(lsoa_sf_de20102019, aes(fill=de_diff))+
+                  geom_sf() +
+                  scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red") +
+  labs(caption="Solent(all LSOAs)")
 ```

### 2021-08-18 mappingSolentWindTurbineAcceptance.Rmd
amended text to explain what model is actually showing h/t @dr-harper

@@
 
- * [Michael Harper's PhD](https://github.com/dataknut/energyMapping) project code
+ * [Michael Harper's PhD](https://mikeyharper.uk/wind-turbinesuccess/) project code and models
  * re-using Tom Rushby's [open geography and leaflet](https://dataknut.github.io/mapping-with-r/ONS-open-geography.html) example.
@@
 
-The model was based on a a range of physical factors as well as known constraints and a model of local social acceptability.
+The model was based on a range of physical factors, modelled wind resource potential, known constraints and local socio-demographics (from Census 2011 data).
+'Acceptance' refers to the *likelihood of planning acceptance* based on Harper et al's model which was developed using a database of planning outcomes for wind turbines from across the UK.
+
 The acceptance indices were originally estimated at 100m squares and have been aggregated to LSOAs (min, max and mean).
+Note that the model outputs used here *do not* take account of the current local built form - so they do not indicate feasibility, merely the probability of a successful planning application assuming there is land available on which to build turbines.
 
@@
 As noted above, modelled wind turbine acceptance levels are low in most of the Solent region - generally due to physical/landscape constraints such as presence of two National Parks, AONBs etc.
-There are some interesting anomalies - some built up (urban) areas have relatively high acceptance probabilities (up to `r round(100*max(wt_sf_trans$mean))` % ).
+There are some interesting outliers - some built up (urban) areas have relatively high acceptance probabilities (up to `r round(100*max(wt_sf_trans$mean))` % ).
+Remembering that the model does not take account of available land (see above), these are most likely due to the socio-demographic factors which tended to increase the probability of acceptance in certain areas (e.g.
+[areas with higher mean age and higher level of qualification have lower acceptance rates](https://mikeyharper.uk/wind-turbinesuccess/)).
 

### 2021-08-19 LSOA domestic Elec and Gas.Rmd
Adding Histogram of the difference in energy consumption

@@
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(merged_de, LAD11NM == "Southampton")
+mapData <- dplyr::filter(merged_de, LSOA11CD == "Southampton")
 # plotting the electricity consumption of Southampton in more detail

### 2021-08-19 LSOA domestic Elec and Gas.Rmd
Fixing Typo errors

--- 2021-08-18 LSOA domestic Elec and Gas.Rmd
@@
   labs(caption="Solent(all LSOAs)")
+
+lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
+t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
+                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
+                         de2010, de2019, de_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
+  geom_histogram()
 ```
@@
   labs(caption = "Southampton")
+#BROKEN
 ```

### 2021-08-19 MSOA non domestic Elec and Gas.Rmd
Fixing Typo errors

@@
 names(merged_ndgas20102019)
-merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$nondomgas2019 - merged_nd20102019$nondomgas2010 ##BROKEN
-summary(merged_nondomgas20102019)
+merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$ndgas2019 - merged_ndgas20102019$ndgas2010 ##BROKEN
+summary(merged_ndgas20102019)
 ```
@@
 ```{r Mapping the change in non domestic gas usage in the MSOA}
-merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
-ggplot2::ggplot(msoa_nondomgas20102019) +
+merged_ndgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
+msoa_ndgas20102019 <- merge(msoa_sf_data, merged_ndgas20102019) #merging these
+ggplot2::ggplot(msoa_ndgas20102019) +
   geom_sf(aes(fill=ndgas_diff))+ 

### 2021-08-21 LSOA domestic Elec and Gas.Rmd
Changing some typos in the cities in more detail section

@@
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(merged_de, LAD11NM == "Portsmouth")
+mapData <- dplyr::filter(merged_de, LSOA11CD == "Portsmouth")
 # plotting the electricity consumption of Portsmouth in more detail
@@
   labs(caption ="Solent (all MSOAs)") ##BROKEN
+##Need to change the varibale names to reflect what is actually there
 ```

### 2021-08-24 LSOA domestic Elec and Gas.Rmd
Trying to fix the error in mapping the difference in electricty consumpton map

@@
 domelec_LSOA_2019$de2019 <- domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter)'
-# create unambiguos lsoa code for matching to each other and the sf geometry
+# create unambiguous lsoa code for matching to each other and the sf geometry
 domelec_LSOA_2010$LSOA11CD <- domelec_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
@@
 
-merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="LSOA11CD", all=TRUE)
+merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Lower Layer Super Output Area (LSOA) Code", all=TRUE)
 names(merged_de)
-merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) ##Fixed
+merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) 
 summary(merged_de)
@@
 # merge to sf geometry on LSOA11CD
+merged_de$LSOA11CD <- merged_de$"Lower Layer Super Output Area (LSOA) Code"
 lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
-ggplot2::ggplot(lsoa_sf_de20102019, aes(fill=de_diff))+
-                  geom_sf() +
-                  scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red") +
+ggplot2::ggplot(lsoa_sf_de20102019) + geom_sf(aes(fill=de_diff))+
+                  scale_fill_continuous(name="Change in Mean consumpton (kWh per meter)",low="green",high="red") +
   labs(caption="Solent(all LSOAs)")
@@
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(merged_de, LSOA11CD == "Southampton")
+mapData <- dplyr::filter(lsoa_sf_de20102019, LSOA11NM == "Southampton")
 # plotting the electricity consumption of Southampton in more detail
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `de_diff`)) +
-  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
+  geom_sf(aes(fill= de_diff)) +
+  scale_fill_continuous(name = "Change in Mean consumpton (kWh per meter)", low = "green", high = "red") +
   labs(caption = "Southampton")

### 2021-08-24 LSOA domestic Elec and Gas.Rmd
Fixed errors in LSOA dom elec and gas

@@
 lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
-ggplot2::ggplot(lsoa_sf_de20102019) + geom_sf(aes(fill=de_diff))+
+ggplot2::ggplot(lsoa_sf_de20102019) +
+  geom_sf(aes(fill=de_diff))+
   scale_fill_continuous(name="Change in Mean consumpton (kWh per meter)",low="green",high="red") +
@@
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_sf_de20102019, LSOA11NM == "Southampton")
+mapData <- dplyr::filter(lsoa_sf_de20102019, LAD11NM == "Southampton")
 # plotting the electricity consumption of Southampton in more detail
@@
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(merged_de, LSOA11CD == "Portsmouth")
+mapData <- dplyr::filter(lsoa_sf_de20102019, LAD11NM == "Portsmouth")
 # plotting the electricity consumption of Portsmouth in more detail
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `de-diff`)) +
+  geom_sf(aes(fill = de_diff)) +
   scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
@@
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
+mapData <- dplyr::filter(lsoa_sf_de20102019, LAD11NM == "Winchester")
 # plotting the electricity consumption of Winchester in more detail
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `de_diff`)) +
+  geom_sf(aes(fill = de_diff)) +
   scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
@@
 dgas_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv"))
-dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$`Mean consumption (kWh per meter)`
-dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$`Mean consumption (kWh per meter)`
-merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all = TRUE)
+
+dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$'Mean consumption (kWh per meter)'
+dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$'Mean consumption (kWh per meter)'
+merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Lower Layer Super Output Area (LSOA) Code", all = TRUE)
 names(merged_dgas)
@@
 ```{r Mapping the change in LSOA dom mean gas comsumption}
-merged_dgas$LSOA11CD <- merged_dgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
+merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
 lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
-ggplot2::ggplot(merged_dgas) +
-  geom_sf(aes(fill=dg_diff))+ 
+ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
                   scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
@@
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")
+mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Southampton")
 
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  geom_sf(aes(fill = dg_diff)) +
   scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
@@
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")
+mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Portsmouth")
 
@@
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")
+mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Winchester")
 

### 2021-08-24 LSOA Deprevation.Rmd
Trying to solve the issues with mapping the difference in IMD Score map

--- 2021-08-09 LSOA Deprevation.Rmd
@@
 lsoa_multidep <- readr::read_csv (inFile)
+lsoa_multidep$LSOA11CD <- lsoa_multidep$'lsoa11cd'
 head(lsoa_multidep)
@@
 ```{r Mapping the Indices of deprivation for the LSOA}
-lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
-head(lsoa_multidep)
-lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
-ggplot2::ggplot(lsoa_multidep_merged_sf) +
-  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
-  scale_fill_continuous(name="IMD Score", low="green",high="red")+
-  labs(caption ="Solent (all LSOAs)")
+lsoa_multidep_merged_sf<- merge(lsoa_sf_data, lsoa_multidep)
+ggplot2::ggplot(lsoa_multidep_merged_sf)+
+  geom_sf(aes(fill=IMDScore))+
+  scale_fill_continuous(name="IMD Score", low="green", high="red")+
+  labs(caption="Solent (all LSOAs)")
 ```
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `IMDScore`)) +
+  geom_sf(aes(fill = IMDScore)) +
   scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
@@
 ```
-####Difference from 2010 to 2019
+####Difference from 2015 to 2019
+```{r Creating the dfference in IMD score variable}
+imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2015.csv"))
+imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
 
-here
+imd_lsoa_2015$imd2015 <- imd_lsoa_2015$'Index of Multiple Deprivation (IMD) Score'
+imd_lsoa_2019$imd2019 <- imd_lsoa_2019$'Index of Multiple Deprivation (IMD) Score'
 
+merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by ='lsoa11cd', all = TRUE)
+names(merged_imd)
+merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
+summary(merged_imd)
+```
+```{r Mapping the change in IMD Score}
+merged_imd$lsoa11cd <- merged_imd$"lsoa11cd" #creating a variable with the LSOA code in the same name as in sf_data
+lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
+names(lsoa_imd20152019)##BROKEN
+##ggplot2::ggplot(lsoa_imd20152019) +
+ ## geom_sf(aes(fill=mc_diff))+ 
+  ##scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
+  ##labs(caption ="Solent (all MSOAs)")
+```
 #####Looking at the cities in more detail
+```{r Southampton LSOA Gas}
+#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
+mapData <- dplyr::filter(merged_imd, LAD11NM == "Southampton")
+# plotting the gas consumption of Southampton in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `imd_diff`)) +
+  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
+  labs(caption = "Southampton")
+```
+```{r Portsmouth LSOA Gas}
+#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
+mapData <- dplyr::filter(merged_imd, LAD11NM == "Portsmouth")
+# plotting the gas consumption of Portsmouth in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `imd_diff`)) +
+  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
+  labs(caption = "Portsmouth")
+```
+```{r Winchester LSOA Gas}
+#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
+mapData <- dplyr::filter(merged_imd, LAD11NM == "Winchester")
+# plotting the gas consumption of Winchester in more detail
+ggplot2::ggplot(mapData) + 
+  geom_sf(aes(fill = `imd_diff`)) +
+  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
+  labs(caption = "Winchester")
+```

### 2021-08-24 LSOA domestic Elec and Gas.Rmd
Knitting Code that works, just left with MSOA non dom and LSOA Deprevation to fix

@@
 #####Cities in more detail
-```{r Southampton LSOA Gas}
+```{r Southampton change in LSOA Gas}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
-```{r Portsmouth LSOA Gas}
+```{r Portsmouth Change in LSOA Gas}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
@@
 ```
-```{r Winchester LSOA Gas}
+```{r Winchester Chnage in LSOA Gas}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail

### 2021-08-24 LSOA Deprevation.Rmd
Knitting Code that works, just left with MSOA non dom and LSOA Deprevation to fix
Tried fixing the difference in depreviation map

@@
 ### Mapping the Indices of Multiple Deprivation
+####2015
+```{r Loading in the Indices of Multiple Deprevation data 2015}
+inFile <-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2015.csv")
+lsoa_multidep2015 <- readr::read_csv (inFile)
+lsoa_multidep2015$LSOA11CD <- lsoa_multidep2015$'lsoa11cd'
+head(lsoa_multidep2015)
+names(lsoa_multidep2015)
+```
+
 ####2019
-```{r Loading in the Indices of Multiple Deprivation data}
+```{r Loading in the Indices of Multiple Deprivation data 2019}
 # Multiple deprivation data at MSOA pre downloaded
@@
 head(lsoa_multidep)
+names(lsoa_multidep)
 ```
@@
 imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
+imd_lsoa_2015$imd2015 <- imd_lsoa_2015$'Index of Multiple Deprivation (IMD) Score'
+imd_lsoa_2019$imd2019 <- imd_lsoa_2019$'IMDScore'
 
-imd_lsoa_2015$imd2015 <- imd_lsoa_2015$'Index of Multiple Deprivation (IMD) Score'
-imd_lsoa_2019$imd2019 <- imd_lsoa_2019$'Index of Multiple Deprivation (IMD) Score'
+imd_lsoa_2015$LSOA11CD <-imd_lsoa_2015$lsoa11cd
+imd_lsoa_2019$LSOA11CD <-imd_lsoa_2019$lsoa11cd
 
-merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by ='lsoa11cd', all = TRUE)
+merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by =lsoa11cd, all = TRUE)
 names(merged_imd)

### 2021-08-24 MSOA non domestic Elec and Gas.Rmd
Tried fixing the difference in depreviation map

@@
 ggplot2::ggplot(msoa_nd20102019)+geom_sf(aes(fill=ndelec_diff))+scale_fill_continuous(name="Change in electricty:Mean kWh per meter",low="green",high="red")+labs(caption ="Solent (all MSOAs)")
+
+msoa_nd20102019$pc_diff <-100*(msoa_nd20102019$ndelec_diff/msoa_nd20102019$ndelec2010)
+t_diff <- dplyr::select(as.data.frame(msoa_nd20102019),MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code', ndelec2010, ndelec2019,ndelec_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```
@@
 msoa_2019_ndgas$ndgas2019<-msoa_2019_ndgas$'Mean consumption (kWh per meter)'
-merged_ndgas20102019<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
-names(merged_ndgas20102019)
-merged_ndgas20102019$ndgas_diff<-merged_ndgas20102019$ndgas2019 - merged_ndgas20102019$ndgas2010 ##BROKEN
-summary(merged_ndgas20102019)
+
+msoa_2010_ndgas$MSOA11CD <-msoa_2010_ndgas$'Middle Layer Super Output Area (MSOA) Code'
+msoa_2019_ndgas$MSOA11CD <-msoa_2019_ndgas$'Middle Layer Super Output Area (MSOA) Code'
+
+merged_ndgas<-merge(msoa_2010_ndgas, msoa_2019_ndgas, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
+names(merged_ndgas)
+merged_ndgas$ndgas_diff<-merged_ndgas$ndgas2019 - merged_ndgas$ndgas2010 
+summary(merged_ndgas)
 ```
@@
 ```{r Mapping the change in non domestic gas usage in the MSOA}
-merged_ndgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
-msoa_ndgas20102019 <- merge(msoa_sf_data, merged_ndgas20102019) #merging these
+merged_ndgas$MSOA11CD <- merged_ndgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
+
+msoa_ndgas20102019 <- merge(msoa_sf_data, merged_ndgas) #merging these
 ggplot2::ggplot(msoa_ndgas20102019) +
@@
   labs(caption ="Solent (all MSOAs)")
-##BROKEN
+
+msoa_ndgas20102019$pc_diff <-100*(msoa_ndgas20102019$ndgas_diff/msoa_ndgas20102019$ndgas2010)
+t_diff <- dplyr::select(as.data.frame(msoa_ndgas20102019), MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code', ndgas2010, ndgas2019, ndgas_diff, pc_diff) 
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff))+
+  geom_histogram()
+
 ```

### 2021-08-26 LSOA Deprevation.Rmd
Adding in notes on how the overlay map works

@@
 ```{r Creating the dfference in IMD score variable}
-imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2015.csv"))
+imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/File_5_ID_2015_Scores_for_the_Indices_of_Deprivation.csv")) # see https://www.gov.uk/government/statistics/english-indices-of-deprivation-2015 - this file has the actual indices in it, the other files (I don't know which you are using) have the ranks
 imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
@@
 
-imd_lsoa_2015$LSOA11CD <-imd_lsoa_2015$lsoa11cd
+#use names(imd_lsoa_2015) to see what the column (variable) names are!
+imd_lsoa_2015$LSOA11CD <-imd_lsoa_2015$`LSOA code (2011)` # <- this does!
 imd_lsoa_2019$LSOA11CD <-imd_lsoa_2019$lsoa11cd
 
-merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by =lsoa11cd, all = TRUE)
+merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, 
+                    by = "LSOA11CD", # you have to use the LSOA11CD variable you just created! 'lsoa11cd' doesn't exist in these two datasets...
+                    all = TRUE)
 names(merged_imd)
@@
 ```{r Mapping the change in IMD Score}
-merged_imd$lsoa11cd <- merged_imd$"lsoa11cd" #creating a variable with the LSOA code in the same name as in sf_data
+merged_imd$lsoa11cd <- merged_imd$LSOA11CD #creating a variable with the LSOA code in the same name as in sf_data - check what you created above!
 lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
-names(lsoa_imd20152019)##BROKEN
-##ggplot2::ggplot(lsoa_imd20152019) +
- ## geom_sf(aes(fill=mc_diff))+ 
-  ##scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
-  ##labs(caption ="Solent (all MSOAs)")
+names(lsoa_imd20152019)## fixed
+ggplot2::ggplot(lsoa_imd20152019) +
+ geom_sf(aes(fill=imd_diff))+ 
+ scale_fill_continuous(name="Change in IMD score", low="green",high="red")+
+ labs(caption ="Solent (all LSOAs)")
 ```
 #####Looking at the cities in more detail
-```{r Southampton LSOA Gas}
+```{r Southampton LSOA IMD}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
-mapData <- dplyr::filter(merged_imd, LAD11NM == "Southampton")
+mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Southampton") # check names of variables! Use the data file with the geometry in it
 # plotting the gas consumption of Southampton in more detail
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `imd_diff`)) +
+  geom_sf(aes(fill = imd_diff)) +
   scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
@@
 ```
-```{r Portsmouth LSOA Gas}
+```{r Portsmouth LSOA IMD}
 #Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
-mapData <- dplyr::filter(merged_imd, LAD11NM == "Portsmouth")
+mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Portsmouth")
 # plotting the gas consumption of Portsmouth in more detail
@@
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
-mapData <- dplyr::filter(merged_imd, LAD11NM == "Winchester")
+mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Winchester")
 # plotting the gas consumption of Winchester in more detail

### 2021-08-26 MSOA domestic Elec and Gas.Rmd
Adding in notes on how the overlay map works

@@
 st_coord_sys <- st_crs(msoa_domgas20102019) # check coord system
-st_coord_sys$epsg # current coord system ? Leaflet wants EPSG: 4326
+st_coord_sys$epsg # current coord system 27700 Leaflet wants EPSG: 4326 so we need to transform
 
@@
 
-qpal <- colorNumeric("Reds", map_df_trans$mc_diff, n = 9)
+qpal <- colorNumeric("Reds", map_df_trans$mc_diff, n = 9)#This is setting the colour that wil used later?
 
@@
               fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD), # popups clicked
+
+              ##label =~(popup_text),
+             ##labelOptions -labelOptions(
+               ##style = list("font-weight"= "normal", padding ="2px 2px"),
+               ##direction ="auto"),
+
                highlight = highlightOptions(

### 2021-08-26 MSOA domestic Elec and Gas.Rmd
Adding in Overlay maps to all the MSOA dom maps

@@
 ```
+####Map with Overlay
+```{r Check leaflet for dom elec consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(msoa_merged_sf)
+st_coord_sys$epsg
+#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform
+
+#Transforming the coord system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(msoa_merged_sf, "+proj=longlat +datum=WGS84")
+  }
+```
+```{r Plotting leaflet dom elec consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n = 9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%  # Add default OpenStreetMap map tiles
+  addPolygons(color = ~qpal(`Mean consumption (kWh per meter)`),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),
+
+              ##label =~(popup_text),
+             ##labelOptions -labelOptions(
+               ##style = list("font-weight"= "normal", padding ="2px 2px"),
+               ##direction ="auto"),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
+
 ####Mapping the change from 2010 to 2019
@@
 ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
+```
+####Map with Overlay
+```{r Check leaflet for Change in dom elec consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(msoa_domelec20102019)
+st_coord_sys$epsg
+#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform
+
+#Transforming the coord system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(msoa_domelec20102019, "+proj=longlat +datum=WGS84")
+  }
+```
+```{r Plotting leaflet for change in dom elec consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$domelec_diff, n = 9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%  # Add default OpenStreetMap map tiles
+  addPolygons(color = ~qpal(domelec_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),
+
+              ##label =~(popup_text),
+             ##labelOptions -labelOptions(
+               ##style = list("font-weight"= "normal", padding ="2px 2px"),
+               ##direction ="auto"),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
 ```
@@
 > Does this match to non-gas areas??
+
+####Map with Overlay
+```{r Check leaflet for dom gas consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(msoa_merged_sf_domgas)
+st_coord_sys$epsg
+#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform
+
+#Transforming the coord system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(msoa_merged_sf_domgas, "+proj=longlat +datum=WGS84")
+  }
+```
+```{r Plotting leaflet dom gas consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n = 9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%  # Add default OpenStreetMap map tiles
+  addPolygons(color = ~qpal(`Mean consumption (kWh per meter)`),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),
+
+              ##label =~(popup_text),
+             ##labelOptions -labelOptions(
+               ##style = list("font-weight"= "normal", padding ="2px 2px"),
+               ##direction ="auto"),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
 
@@
 
-```{r checkLeaflet}
+```{r checkLeaflet for change in dom gas consumption}
 # https://dataknut.github.io/mapping-with-r/ONS-open-geography.html
@@
 
-```{r mapDiffLeaflet, fig.cap="Change in mean domestic gas kWh/meter"}
+```{r Plotting leaflet chnage in dom gas consumption map}
 

### 2021-08-26 MSOA domestic Elec and Gas.Rmd
Adding in Histograms

@@
 ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
+
+#Histogram
+msoa_domelec20102019$pc_diff <- 100* (msoa_domelec20102019$domelec_diff/msoa_domelec20102019$domelec2010)
+t_diff <-dplyr::select(as.data.frame(msoa_domelec20102019), MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code',domelec2010, domelec2019, domelec_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```
@@
   labs(caption ="Solent (all MSOAs)")
+
+#Histogram
+msoa_domgas20102019$pc_diff <- 100* (msoa_domgas20102019$mc_diff/msoa_domgas20102019$domgas2010)
+t_diff <- dplyr::select(as.data.frame(msoa_domgas20102019), MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code',domgas2010, domgas2019, mc_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
+
 ```

### 2021-08-26 MSOA non domestic Elec and Gas.Rmd
Adding Overlay maps to MSOA non dom maps

@@
 ```
+####Map Overlay
+```{r Check leaflet for non dom elec consumption}
+library (leaflet)
+
+st_coord_sys <- st_crs(msoa_merged_sf_nondom)
+st_coord_sys$epsg
+#current coordinate system 27700 Leaflet needs EPSG: 4326
+
+#Transforming the coor system
+if(st_coord_sys$epsg !=4326) {
+  map_df_trans <- st_transform(msoa_merged_sf_nondom, "+proj=longlat +datum=WGS84")
+}
+
+```
+```{r Plotting leaflet non dom elec consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>% 
+  addPolygons(color= ~qpal(`Mean consumption (kWh per meter)`), 
+              fillOpacity = 0.6, weight = 1.5, popup= ~(MSOA11CD),
+
+                highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
 ####Difference from 2010 to 2019
@@
 ```
+####Map with Overlay
+```{r Check leaflet for change in non dom elec consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(msoa_nd20102019)
+st_coord_sys$epsg
+#Current coor system 27700 Leaflet wants EPSG: 4326 so we need to transform
+
+#Tranforming the coord system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(msoa_nd20102019, "+proj=longlat +datum=WGS84")
+}
+```
+```{r Plotting leaflet change in non dom elec consumtpion map}
+qpal <- colorNumeric("Reds", map_df_trans$ndelec_diff, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%
+  addPolygons(color = ~qpal(ndelec_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD), 
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
+
 ```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
@@
 ```
+####Map with Overlay
+```{r Check leaflet for Change in non dom gas consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(msoa_ndgas20102019)
+st_coord_sys$epsg
+
+#Transporting the coord system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(msoa_ndgas20102019, "+proj=longlat +datum=WGS84")
+}
+```
+```{r Plotting leaflet change in non dom gas consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$ndgas_diff, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%
+  addPolygons(color=~qpal(ndgas_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```

### 2021-08-26 LSOA Deprevation.Rmd
Adding the layover maps and histograms for the analysis of the results

@@
  labs(caption ="Solent (all LSOAs)")
+
+#Histogram
+lsoa_imd20152019$pc_diff <-100* (lsoa_imd20152019$imd_diff/lsoa_imd20152019$imd2015)
+t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```

### 2021-08-26 LSOA Fuel poverty.Rmd
Adding the layover maps and histograms for the analysis of the results

@@
 fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
-fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
-fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
+fp_LSOA_2012_df$fp2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
+fp_LSOA_2018_df$fp2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
 merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
 names(merged_df)
-merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
+merged_df$fp_diff <-  as.numeric(merged_df$fp2018) - merged_df$fp2012
 summary(merged_df)
@@
 ggplot2::ggplot(lsoa_fuelpov20122018) +
-  geom_sf(aes(fill=pc_diff))+ 
+  geom_sf(aes(fill=fp_diff))+ 
   scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
   labs(caption ="Solent (all LSOAs)")
+
+#Histogram 
+lsoa_fuelpov20122018$pc_diff <-100* (lsoa_fuelpov20122018$fp_diff/lsoa_fuelpov20122018$fp2012)
+t_diff <-dplyr::select(as.data.frame(lsoa_fuelpov20122018),LSOA11CD, 'LSOA Code', fp2012, fp2018, fp_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```

### 2021-08-26 LSOA domestic Elec and Gas.Rmd
Adding the layover maps and histograms for the analysis of the results

@@
 ```
+####Map with Overlay
+```{r Check leaflet for dom electricity consumption}
+library(leaflet)
 
+st_coord_sys <- st_crs(lsoa_merged_sf)
+st_coord_sys$epsg
+
+#Trasforming the coord systen
+if(st_coord_sys$epsg !=4326){
+map_df_trans <- st_transform(lsoa_merged_sf, "+proj=longlat +datum=WGS84")
+}
+```
+```{r Plotting leaflet dom electricity consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$`Mean domestic electricity consumption \n(kWh per meter)`, n=9)
+
+leaflet(map_df_trans) %>%
+addTiles() %>%  # Add default OpenStreetMap map tiles
+  addPolygons(color = ~qpal(`Mean domestic electricity consumption \n(kWh per meter)`),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
 ##### Looking at cities in more detail        
@@
 ```
+####Map with Overlay 
+```{r Check leaflet for Change in dom elec consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(lsoa_sf_de20102019)
+st_coord_sys$epsg
+
+#Transforming the coord system
+if(st_coord_sys$epsg !=4326) {
+  map_df_trans <- st_transform(lsoa_sf_de20102019, "+proj=longlat +datum=WGS84")
+}
+
+```
+```{r Plotting leaflet for change in dom elec consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$de_diff, n=9)
+
+leaflet(map_df_trans) %>% 
+  addTiles() %>%  # Add default OpenStreetMap map tiles
+  addPolygons(color = ~qpal(de_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD ),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
 
@@
 > Aha - this one shows where there is no gas :-)
+
+###Map with Overlay
+```{r Check leaflet for dom gas consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(lsoa_merged_sf_gas)
+st_coord_sys$epsg
+
+#Transforming the coord system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(lsoa_merged_sf_gas, "+proj=longlat +datum=WGS84")
+}
+```
+```{r Plotting leaflet dom gas consumption}
+qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%
+  addPolygons(color= ~qpal(`Mean consumption (kWh per meter)`), 
+              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
+
+              highlight=highlightOptions(
+                weight=5,
+                color="#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
 
@@
 ```
+####Map with overlay 
+```{r Check leaflet for change i dom gas consumption}
+library(leaflet)
 
+st_coord_sys <- st_crs(lsoa_dgas20102019)
+st_coord_sys$epsg
+
+#Transforming the coor system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(lsoa_dgas20102019, "+proj=longlat +datum=WGS84")
+}
+
+```
+```{r Plotting leaflet for change in dom gas consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$dg_diff, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%
+  addPolygons(color = ~qpal(dg_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
 #####Cities in more detail

### 2021-08-26 MSOA-domestic-Elec-and-Gas.Rmd
Adding the layover maps and histograms to be used in the analysis

--- 2021-08-26 MSOA domestic Elec and Gas.Rmd
@@
 ```
+
 ####Map with Overlay
@@
               fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD),
-
-              ##label =~(popup_text),
-             ##labelOptions -labelOptions(
-               ##style = list("font-weight"= "normal", padding ="2px 2px"),
-               ##direction ="auto"),
 

### 2021-08-29 LSOA Fuel poverty.Rmd
Using the maps for the mapping discussion section

@@
   labs(caption ="Solent (all LSOAs)")
+head(lsoa_fuelpov_2019_merged)
+names(lsoa_fuelpov_2019_merged)
 ```
@@
 ```
+### Over 65 annd Fuel Poverty
+```{r Loading in the Census age data}
+inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
+census_age<-readr::read_csv (inFile)
+census_age$'Local Authority Code'<- census_age$'geography code'
+head(census_age)
+names(census_age)
+```
+```{r Mapping the fuel poverty in over 65s}
+#census_age$"LSOA11CD" <- census_age$"geography code"
+Census_age_fp <- merge(lsoa_fuelpov_2019_merged, census_age)
+names(Census_age_fp)
+ggplot(Census_age_fp, aes(x='Proportion Over 65', y=pcFP))
+
+```

### 2021-08-29 MSOA non domestic Elec and Gas.Rmd
using the maps for the mapping discussion section

@@
 #mapping it
+mean(msoa_merged_sf_nondom$`Mean consumption (kWh per meter)`)
 ```

### 2021-09-02 LSOA Fuel poverty.Rmd
Graphing relationship betwene older age and fuel poverty

@@
 census_age<-readr::read_csv (inFile)
-census_age$'Local Authority Code'<- census_age$'geography code'
+census_age$'LSOA11CD'<- census_age$'geography code'
 head(census_age)
@@
 names(Census_age_fp)
-ggplot(Census_age_fp, aes(x='Proportion Over 65', y=pcFP))
+ggplot(Census_age_fp, aes(x=as.numeric('Proportion Over 65'), y=pcFP)) +
+  geom_point()
 

### 2021-09-02 LSOA Fuel poverty.Rmd
Trying to fix error with over 65s and fuel poverty graph

--- 2021-08-29 LSOA Fuel poverty.Rmd
@@
 #census_age$"LSOA11CD" <- census_age$"geography code"
-Census_age_fp <- merge(lsoa_fuelpov_2019_merged, census_age)
+Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
 names(Census_age_fp)
-ggplot(Census_age_fp, aes(x='Proportion Over 65', y=pcFP))
+census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
+ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +
+  geom_point()
 

### 2021-09-02 LSOA Fuel poverty.Rmd
fixed for now

--- 2021-08-29 LSOA Fuel poverty.Rmd
@@
 ```
-```{r Mapping the fuel poverty in over 65s}
+
+```{r Plotting the fuel poverty in over 65s}
 #census_age$"LSOA11CD" <- census_age$"geography code"
-Census_age_fp <- merge(lsoa_fuelpov_2019_merged, census_age)
+Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
 names(Census_age_fp)
-ggplot(Census_age_fp, aes(x='Proportion Over 65', y=pcFP))
+
+# select the variables we want for clarity
+df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")
+
+df$propFP <- as.numeric(substring(df$`Proportion Over 65`, 
+                                  1, 
+                                  nchar(df$`Proportion Over 65`)-1)
+                        )
+
+head(df)
+# select the places we want
+
+ggplot2::ggplot(df, aes(x=`Proportion of households fuel poor (%)`, 
+               y=propFP)) +
+  geom_point()
 

### 2021-09-02 LSOA Fuel poverty.Rmd

@@
 head(df)
-# select the places we want
+# select the places we want here
 
-ggplot2::ggplot(df, aes(x=`Proportion of households fuel poor (%)`, 
-               y=propFP)) +
+census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
+ggplot(Census_age_fp, aes(x=oldpop, y=`Proportion of households fuel poor (%)`)) +
   geom_point()

### 2021-09-02 LSOA Fuel poverty.Rmd
Trying to resolve issue with age fuel poverty graph

--- 2021-09-02 LSOA Fuel poverty.Rmd
@@
 census_age<-readr::read_csv (inFile)
+census_age$oldpop <- census_age$'Over 65s'/census_age$'Age: All usual residents; measures: Value'
 census_age$'LSOA11CD'<- census_age$'geography code'
@@
 names(Census_age_fp)
-census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
 ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +

### 2021-09-02 LSOA Fuel poverty.Rmd
big plot of all LSOAs

@@
 census_age<-readr::read_csv (inFile)
-census_age$oldpop <- census_age$'Over 65s'/census_age$'Age: All usual residents; measures: Value'
 census_age$'LSOA11CD'<- census_age$'geography code'
@@
 ```
-```{r Mapping the fuel poverty in over 65s}
+```{r Plotting the fuel poverty in over 65s}
 #census_age$"LSOA11CD" <- census_age$"geography code"
@@
 names(Census_age_fp)
-ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +
+# select the variables we want for clarity
+df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")
+df$propFP <- as.numeric(substring(df$`Proportion Over 65`, 
+                                  1, 
+                                  nchar(df$`Proportion Over 65`)-1)
+                        )
+head(df)
+# select the places we want here
+ggplot(df, aes(x=propFP, y=`Proportion of households fuel poor (%)`)) +
   geom_point()
-
+census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
+ggplot(Census_age_fp, aes(x=oldpop, y=`Proportion of households fuel poor (%)`)) +
+  geom_point()
 ```

### 2021-09-02 LSOA Fuel poverty.Rmd

--- 2021-09-02 LSOA Fuel poverty.Rmd
@@
 names(Census_age_fp)
-ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +
+# select the variables we want for clarity
+df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")
+df$propFP <- as.numeric(substring(df$`Proportion Over 65`, 
+                                  1, 
+                                  nchar(df$`Proportion Over 65`)-1)
+                        )
+head(df)
+# select the places we want here
+ggplot(df, aes(x=propFP, y=`Proportion of households fuel poor (%)`)) +
   geom_point()
 
+census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
+ggplot(Census_age_fp, aes(x=oldpop, y=`Proportion of households fuel poor (%)`)) +
+  geom_point()
 ```

### 2021-09-02 LSOA Fuel poverty.Rmd
Fixing

--- 2021-09-02 LSOA Fuel poverty.Rmd
@@
 names(Census_age_fp)
-ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +
+# select the variables we want for clarity
+df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")
+
+head(df)
+# select the places we want here
+ggplot(df, aes(x='Proportion Over 65', y=`Proportion of households fuel poor (%)`)) +
   geom_point()
 
+census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
+ggplot(Census_age_fp, aes(x=oldpop, y=(`Proportion of households fuel poor (%)`/100)) +
+  geom_point()
 ```

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
Plotting Change in dom elec against IMD

@@
 ```
+####Plotting the change in dom elec consumption against the deprevation score
+```{r Loading in the Deprevation score data}
+inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
+LSOAdep<-readr::read_csv(inFile)
+LSOAdep$'LSOA11CD' <- LSOAdep$'lsoa11cd'
+head(LSOAdep)
+names(LSOAdep)
+```
+```{r plotting change in elec usage against dep}
+LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
+names(LSOAdepelec)
+df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
+)
+
+head(df)
+Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
+                           `Local Authority Name.x` == "East Hampshire"|
+                           `Local Authority Name.x` == "Eastleigh"|
+                           `Local Authority Name.x` == "Fareham"|
+                           `Local Authority Name.x` == "Gosport"|
+                           `Local Authority Name.x` == "Hart"|
+                           `Local Authority Name.x` == "Havant"|
+                           `Local Authority Name.x` == "New Forest"|
+                           `Local Authority Name.x` == "Portsmouth"|
+                           `Local Authority Name.x` == "Rushmoor"|
+                           `Local Authority Name.x` == "Southampton"|
+                           `Local Authority Name.x` == "Test Valley"|
+                           `Local Authority Name.x` == "Winchester"|
+                           `Local Authority Name.x` == "Isle of Wight"
+                           )
+
+ggplot(Solent,aes(x =as.factor(IMD_Decile)), y =(de_diff/de2010), colour =as.factor(IMD_Decile), group =IMD_Decile) +  geom_boxplot()
+
+nrow(Solent)
+```
+
 ####Map with Overlay 

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
fixed % change plots and added an example by facet_wrap

@@
                            )
+head(Solent)
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(de_diff/de2010), 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "% change")
+```
 
-ggplot(Solent,aes(x =as.factor(IMD_Decile)), y =(de_diff/de2010), colour =as.factor(IMD_Decile), group =IMD_Decile) +  geom_boxplot()
+```{r addFacetsToElecDiff}
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(de_diff/de2010), 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "% change") +
+  facet_wrap(`Local Authority Name.x` ~ .)
 

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
fixed % change plots and added an example by facet_wrap

--- 2021-09-02 LSOA domestic Elec and Gas.Rmd
@@
                            )
+head(Solent)
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(de_diff/de2010), 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "% change")
 
-ggplot(Solent,aes(x =as.factor(IMD_Decile)), y =(de_diff/de2010), colour =as.factor(IMD_Decile), group =IMD_Decile) +  geom_boxplot()
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(de_diff/de2010), 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "% change") +
+  facet_wrap(`Local Authority Name.x` ~ .)
 

### 2021-09-02 LSOA domestic Elec and Gas.Rmd

--- 2021-09-02 LSOA domestic Elec and Gas.Rmd
@@
 
+Try adding facets for each Local Authority
 ```{r addFacetsToElecDiff}

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
added IMD score checks

--- 2021-09-02 LSOA domestic Elec and Gas.Rmd
@@
 ```
-####Plotting the change in dom elec consumption against the deprevation score
-```{r Loading in the Deprevation score data}
+#### Plotting the change in dom elec consumption against the deprivation score
+
+Loading deprivation data and double checking what the IMD Decile means
+
+```{r Loading in the Deprivation score data}
 inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
@@
 names(LSOAdep)
+
+# check IMD decile is higher with higher deprivation
+library(data.table)
+dt <- as.data.table(Solent)
+dt[, .(nLSOAs = .N,
+       meanIMDScore = mean(IMDScore)),
+   keyby = .(IMD_Decile)]
+
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y = IMDScore, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "IMD Score")
 ```
+
+NB: IMD Decile 10 has _LOWER_ IMD score!
+
 ```{r plotting change in elec usage against dep}
@@
 ```
+
+Try adding facets for each Local Authority
 

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
added IMD score checks

@@
 
-# check IMD decile is higher with higher deprivation
-library(data.table)
-dt <- as.data.table(Solent)
-dt[, .(nLSOAs = .N,
-       meanIMDScore = mean(IMDScore)),
-   keyby = .(IMD_Decile)]
-
+# check IMD decile is higher or lower with higher deprivation
 ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
@@
 
-NB: IMD Decile 10 has _LOWER_ IMD score!
+NB: IMD Decile 10 has _LOWER_ mean IMD score!
 

### 2021-09-02 LSOA Fuel poverty.Rmd
Fuel poverty and age relationship

@@
 ```
-### Over 65 annd Fuel Poverty
 ```{r Loading in the Census age data}
@@
 census_age$'LSOA11CD'<- census_age$'geography code'
-head(census_age)
+census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
+#head(census_age) lots of variables
 names(census_age)
+message("Original Proportion Over 65:")
+summary(census_age$`Proportion Over 65`)
+message("New prop_65m:")
+summary(census_age$prop_65m)
 ```
-```{r Plotting the fuel poverty in over 65s}
+
+## 2012 Fuel poverty & Census 2011 data
+
+```{r Plotting the 2012 fuel poverty vs 2011 percent over 65s}
 #census_age$"LSOA11CD" <- census_age$"geography code"
-Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
-names(Census_age_fp)
+fp_LSOA_2012_df$LSOA11CD <- fp_LSOA_2012_df$`LSOA Code`
+Census_age_2012fp <- merge(fp_LSOA_2012_df, census_age, by = "LSOA11CD")
 # select the variables we want for clarity
-df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")
+df_2012 <- dplyr::select(Census_age_2012fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
+head(df_2012)
+# table(df$`LA Name`)
+df_2012$la_name <- df_2012$`LA Name` # make a new variable with an easier name
+df_2012$pcFuelPoor <- df_2012$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
+# select the places we want here
+getSolent <- function(df){
+  # assumes we are filtering on la_name
+  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
+                           la_name == "East Hampshire"|
+                           la_name == "Eastleigh"|
+                           la_name == "Fareham"|
+                           la_name == "Gosport"|
+                           la_name == "Hart"|
+                           la_name == "Havant"|
+                           la_name == "New Forest"|
+                           la_name == "Portsmouth"|
+                           la_name == "Rushmoor"|
+                           la_name == "Southampton"|
+                           la_name == "Test Valley"|
+                           la_name == "Winchester"|
+                           la_name == "Isle of Wight"
+                           )
+  return(res)
+}
+Solent_2012 <- getSolent(df_2012) # use our function to get just Solent LAs
+nrow(Solent_2012)
+ggplot(Solent_2012, aes(x= 100 * prop_65m, 
+                   y= pcFuelPoor, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  geom_smooth() + # adds a smoothed best fit line
+  theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "% households in fuel poverty, 2012") +
+  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
+message("Correlation coeficient across al LSOAs (2012)")
+cor(Solent_2012$prop_65m, Solent_2012$pcFuelPoor)
+```
 
-head(df)
+## 2019 Fuel poverty & Census 2011 data
+
+```{r Plotting the 2019 fuel poverty vs 2011 percent over 65s}
+#census_age$"LSOA11CD" <- census_age$"geography code"
+Census_age_2019fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
+names(Census_age_2019fp)
+# select the variables we want for clarity
+df_2019 <- dplyr::select(Census_age_2019fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
+head(df_2019)
+# table(df$`LA Name`)
+df_2019$la_name <- df_2019$`LA Name` # make a new variable with an easier name
+df_2019$pcFuelPoor <- df_2019$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
 # select the places we want here
-ggplot(df, aes(x='Proportion Over 65', y=`Proportion of households fuel poor (%)`)) +
-  geom_point()
-
-census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
-ggplot(Census_age_fp, aes(x=oldpop, y=(`Proportion of households fuel poor (%)`/100)) +
-  geom_point()
+Solent_2019 <- getSolent(df_2019) # use our function to get just Solent LAs
+nrow(Solent_2019)
+ggplot(Solent_2019, aes(x= 100 * prop_65m, 
+                   y= pcFuelPoor, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  geom_smooth() + # adds a smoothed best fit line
+  theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "% households in fuel poverty, 2019") +
+  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
+message("Correlation coeficient across al LSOAs (2019)")
+cor(Solent_2019$prop_65m, Solent_2019$pcFuelPoor)
 ```

### 2021-09-02 LSOA domestic Elec and Gas.Rmd

--- 2021-09-02 LSOA domestic Elec and Gas.Rmd
@@
 
-# check IMD decile is higher with higher deprivation
-library(data.table)
-dt <- as.data.table(Solent)
-dt[, .(nLSOAs = .N,
-       meanIMDScore = mean(IMDScore)),
-   keyby = .(IMD_Decile)]
-
 ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
@@
 
-NB: IMD Decile 10 has _LOWER_ IMD score!
+NB: IMD Decile 10 has _LOWER_ mean IMD score! Which is what it says in the Excel workbok...
 

### 2021-09-02 LSOA Fuel poverty.Rmd

--- 2021-09-02 LSOA Fuel poverty.Rmd
@@
 head(df)
+table(df$`LA Name`)
+Solent <- dplyr::filter(df, `LA Name` == "Basingstoke and Deane"|
+                           `LA Name` == "East Hampshire"|
+                           `LA Name` == "Eastleigh"|
+                           `LA Name` == "Fareham"|
+                           `LA Name` == "Gosport"|
+                           `LA Name` == "Hart"|
+                           `LA Name` == "Havant"|
+                           `LA Name` == "New Forest"|
+                           `LA Name` == "Portsmouth"|
+                           `LA Name` == "Rushmoor"|
+                           `LA Name` == "Southampton"|
+                           `LA Name` == "Test Valley"|
+                           `LA Name` == "Winchester"|
+                           `LA Name` == "Isle of Wight"
+                           )
+
 # select the places we want here
-ggplot(df, aes(x='Proportion Over 65', y=`Proportion of households fuel poor (%)`)) +
+ggplot(Solent, aes(x=`Proportion Over 65`, y=`Proportion of households fuel poor (%)`)) +
   geom_point()
+nrow(Solent)
+table(Solent$`LA Name`)
 
-census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
-ggplot(Census_age_fp, aes(x=oldpop, y=(`Proportion of households fuel poor (%)`/100)) +
-  geom_point()
 ```

### 2021-09-03 LSOA Fuel poverty.Rmd
Graphing the chnage in gas usage against deprevation score

@@
 ```
-### Over 65 annd Fuel Poverty
+### Over 65 and Fuel Poverty
 ```{r Loading in the Census age data}

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Graph finished
Graphing the chnage in gas usage against deprevation score

@@
 ```
-
 ####Map with Overlay 
@@
 ##Need to change the varibale names to reflect what is actually there
+
+lsoa_dgas20102019$pc_diff <- 100*(lsoa_dgas20102019$dg_diff/lsoa_dgas20102019$dgas2010)
+t_diff <-  dplyr::select(as.data.frame(lsoa_dgas20102019), 
+                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Code`,
+                         dgas2010, dgas2019, dg_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
+  geom_histogram()
+
 ```
+####Plotting the change in gas usage against the deprevation 
+```{r plotting change in gas usage against dep}
+LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
+names(LSOAdepgas)
+df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile
+)
+
+head(df)
+Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
+                           `Local Authority Name.x` == "East Hampshire"|
+                           `Local Authority Name.x` == "Eastleigh"|
+                           `Local Authority Name.x` == "Fareham"|
+                           `Local Authority Name.x` == "Gosport"|
+                           `Local Authority Name.x` == "Hart"|
+                           `Local Authority Name.x` == "Havant"|
+                           `Local Authority Name.x` == "New Forest"|
+                           `Local Authority Name.x` == "Portsmouth"|
+                           `Local Authority Name.x` == "Rushmoor"|
+                           `Local Authority Name.x` == "Southampton"|
+                           `Local Authority Name.x` == "Test Valley"|
+                           `Local Authority Name.x` == "Winchester"|
+                           `Local Authority Name.x` == "Isle of Wight"
+                           )
+head(Solent)
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(dg_diff/dgas2010), 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "% change")
+```
+
+Try adding facets for each Local Authority
+
+```{r addFacetsToElecDiff}
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(dg_diff/dgas2010), 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "% change") +
+  facet_wrap(`Local Authority Name.x` ~ .)
+
+nrow(Solent)
+```
+
 ####Map with overlay 

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Excluding outlayer

@@
   labs(x = "IMD Decile",
-       y = "% change")
+       y = "% change Electricity")
 ```
@@
   labs(x = "IMD Decile",
-       y = "% change") +
+       y = "% change Electricty") +
   facet_wrap(`Local Authority Name.x` ~ .)
@@
   labs(x = "IMD Decile",
-       y = "% change")
+       y = "% change Gas")
 ```
@@
 # or without colour but using facets for Local Authorities
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+Solentex <- filter(Solent,100*(dg_diff/dgas2010)<50)
+ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                    y =100*(dg_diff/dgas2010), 

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Adding plot of gas consumption against deprevation

@@
 names(LSOAdepgas)
-df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile
+df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile, dgas2019
 )
@@
 
-```{r addFacetsToElecDiff}
+```{r addFacetsTogasDiff}
 # or without colour but using facets for Local Authorities
@@
 ```
+#####Plotting the gas usage against deprevation
+```{r Boxplot of the gas consumption and deprevation}
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =dgas2019, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "Gas Consumption")
 
+```
+```{r addFacetsTogasconsumption}
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =dgas2019, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Gas Consumption") +
+  facet_wrap(`Local Authority Name.x` ~ .)
+
+nrow(Solent)
+```
 ####Map with overlay 

### 2021-09-03 LSOA Fuel poverty.Rmd
Adding Fuel poverty against deprevation graphs

--- 2021-09-02 LSOA Fuel poverty.Rmd
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = pc_diff)) +
+  geom_sf(aes(fill = fp_diff)) +
   scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
@@
 ```
+### Linking age and Fuel Poverty
 ```{r Loading in the Census age data}
@@
 census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
-#head(census_age) lots of variables
+head(census_age)
 names(census_age)
@@
 
-## 2012 Fuel poverty & Census 2011 data
-
-```{r Plotting the 2012 fuel poverty vs 2011 percent over 65s}
+## 2012 Fuel Poverty & Census 2011 Data
+```{r Plotting the fuel poverty in over 65s}
 #census_age$"LSOA11CD" <- census_age$"geography code"
@@
 cor(Solent_2012$prop_65m, Solent_2012$pcFuelPoor)
+
 ```
-
-## 2019 Fuel poverty & Census 2011 data
-
+##2019 Fuel Poverty & Census 2011 data
 ```{r Plotting the 2019 fuel poverty vs 2011 percent over 65s}
@@
 ```
+
+####Plotting Fuel Poverty Against Deprevation
+```{r plotting Change in Fuel Pov against dep}
+LSOAfuelpovdep <- merge(lsoa_fuelpov20122018, LSOAdep, by= "LSOA11CD")
+names(LSOAfuelpovdep)
+df <- dplyr::select(LSOAfuelpovdep, LSOA11CD, "LA Name.x", fp_diff, IMDScore, fp2012, IMD_Decile, fp2018
+)
+
+head(df)
+Solent <- dplyr::filter(df, `LA Name.x` == "Basingstoke and Deane"|
+                           `LA Name.x` == "East Hampshire"|
+                           `LA Name.x` == "Eastleigh"|
+                           `LA Name.x` == "Fareham"|
+                           `LA Name.x` == "Gosport"|
+                           `LA Name.x` == "Hart"|
+                           `LA Name.x` == "Havant"|
+                           `LA Name.x` == "New Forest"|
+                           `LA Name.x` == "Portsmouth"|
+                           `LA Name.x` == "Rushmoor"|
+                           `LA Name.x` == "Southampton"|
+                           `LA Name.x` == "Test Valley"|
+                           `LA Name.x` == "Winchester"|
+                           `LA Name.x` == "Isle of Wight"
+                           )
+head(Solent)
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(fp_diff/fp2012), 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "% Change in Fuel Poverty")
+```
+Try adding facets for each Local Authority
+
+```{r addFacetsToFuelpovdep}
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(fp_diff/fp2012), 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "% change Fuel Poverty") +
+  facet_wrap(`LA Name.x` ~ .)
+
+nrow(Solent)
+```

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Adding Fuel poverty against deprevation graphs

@@
 names(LSOAdepelec)
-df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
+df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile, de2019
 )
@@
 ```
+####Plotting the relationship between Electricty consumption and deprevation
+```{r plotting electricty consumption against deprevation}
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =de2019, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "Electricity Consumption")
+```
+```{r addFacetsToElecconsumption}
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =de2019, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Electricty Consumption") +
+  facet_wrap(`Local Authority Name.x` ~ .)
+
+nrow(Solent)
+```
+
 ####Map with Overlay 
@@
 ####Map with overlay 
-```{r Check leaflet for change i dom gas consumption}
+```{r Check leaflet for change in dom gas consumption}
 library(leaflet)

### 2021-09-03 R/functions.R
amended getSoton to not include Rushmoor

@@ -6,6 +6,7 @@
 getSolent <- function(df){
   # function to return the rows that match on Local Authority name
   # assumes we're matching on la_name
+  # this aligns with the .shp boundary file we pre-created
   solent <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
                             la_name == "East Hampshire"|
                             la_name == "Eastleigh"|
@@ -15,7 +16,7 @@ getSolent <- function(df){
                             la_name == "Havant"|
                             la_name == "New Forest"|
                             la_name == "Portsmouth"|
-                            la_name == "Rushmoor"| # northern Hampshire - not always considered part of Solent
+                            #la_name == "Rushmoor"| # northern Hampshire - not always considered part of Solent
                             la_name == "Southampton"|
                             la_name == "Test Valley"|
                             la_name == "Winchester"|

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
restructured headings and order so the headings work in html; load boundaries & deprivation data at the start; re-use loaded data where we can; re-order of plots slightly; reduce all dataframes so we just merge in the variables we want; more informative captions

--- 2021-09-03 LSOA domestic Elec and Gas.Rmd
@@
 
-# useful R libraries
+# useful R libraries ----
+library(dplyr)
 library(ggplot2)
+library(leaflet)
 library(readr)
-library(dplyr)
 
-# GIS libraries
+# GIS libraries ----
 library(raster)
 library(sf)
-library(spData)
-library(spDataLarge)
+#library(spData) # not needed
+#library(spDataLarge)
+
+# local functions ----
+source(here::here("R", "functions.R"))
 
@@
 
-# Mapping the Lower Layer Super Output Area (LSOA)
-## Mapping Domestic
-### Mapping Electricity consumption
-####2019
-```{r Loading in the LSOA electricty consumption data}
-#Electricty consumption data LSOA pre downloaded
-inFile <-paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv")
-lsoa_elecData <- readr::read_csv(inFile)
-lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_elecData)
-```
+# Background data
+
+Load & check boundary data for Solent area. The table shows which LAs we expect to plot.
 
@@
 message ("Loading LSOA boundaries from file")
-lsoa_sf_data <- sf::read_sf(inf)
-head(lsoa_sf_data)
-table(lsoa_sf_data$LAD11NM)#How many LSOAs are there in each LA
+lsoa_sf <- sf::read_sf(inf)
+head(lsoa_sf)
+table(lsoa_sf$LAD11NM) # How many LSOAs are there in each LA?
 ```
 
-```{r Mapping the electricty consumption of the LSOAs}
-lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
-ggplot2::ggplot(lsoa_merged_sf) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
-  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Solent (all LSOAs)")
-#Mapping it
-```
-####Map with Overlay
-```{r Check leaflet for dom electricity consumption}
-library(leaflet)
-
-st_coord_sys <- st_crs(lsoa_merged_sf)
+```{r transform boundary data for use in leaflet}
+st_coord_sys <- st_crs(lsoa_sf)
 st_coord_sys$epsg
@@
 if(st_coord_sys$epsg !=4326){
-map_df_trans <- st_transform(lsoa_merged_sf, "+proj=longlat +datum=WGS84")
+  lsoa_sf_leaflet <- st_transform(lsoa_sf, "+proj=longlat +datum=WGS84")
 }
 ```
+
+Loading deprivation data and double checking what the IMD Decile means - NB this is all LSOAs not just Solent
+
+```{r Loading in the Deprivation score data}
+inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
+LSOAdep<-readr::read_csv(inFile)
+LSOAdep$'LSOA11CD' <- LSOAdep$'lsoa11cd'
+head(LSOAdep)
+#names(LSOAdep)
+
+ggplot(LSOAdep, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y = IMDScore, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "IMD Score",
+       caption = "All LSOAs")
+
+LSOAdep$la_name <- LSOAdep$LADnm
+solent_dep <- getSolent(LSOAdep)
+ggplot(solent_dep, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y = IMDScore, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  facet_wrap(. ~ la_name)
+  labs(x = "IMD Decile",
+       y = "IMD Score",
+       caption = "Solent LSOAs split by Local Authority")
+```
+
+> NB: IMD Decile 10 has _LOWER_ mean IMD score (less deprived)! Which is what it says in the Excel workbook...
+
+> So remember: IMD Decile 1 = 10% _most_ deprived; IMD Decile 10 = 10% _least_ deprived
+
+# Domestic Electricity consumption
+
+## 2019
+
+Load LSOA elec data - NB this is all LSOAs not just Solent
+
+```{r Loading in the LSOA electricty consumption data}
+#Electricty consumption data LSOA pre downloaded
+inFile <-paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv")
+domelec_LSOA_2019 <- readr::read_csv(inFile)
+domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
+head(domelec_LSOA_2019)
+domelec_LSOA_2019$mean_de2019 <- domelec_LSOA_2019$`Mean domestic electricity consumption 
+(kWh per meter)`
+```
+
+### Base map
+
+```{r Mapping the electricty consumption of the LSOAs}
+# just add the variables we want
+df <- dplyr::select(domelec_LSOA_2019, LSOA11CD, mean_de2019)
+
+lsoa_merged_sf <- merge(lsoa_sf, df) #merging the LSOA boundaries and energy data
+ggplot2::ggplot(lsoa_merged_sf) + 
+  geom_sf(aes(fill = mean_de2019)) +
+  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
+  labs(caption = "Electricity (2019, all Solent LSOAs)")
+#Mapping it
+```
+
+### Map with Overlay (leaflet)
+
 ```{r Plotting leaflet dom electricity consumption map}
-qpal <- colorNumeric("Reds", map_df_trans$`Mean domestic electricity consumption \n(kWh per meter)`, n=9)
+# make a new df for use in the map (prevents confusion)
+map_df <- merge(lsoa_sf_leaflet, df, by = "LSOA11CD")
 
-leaflet(map_df_trans) %>%
+qpal <- colorNumeric("Reds", df$mean_de2019, n=9)
+
+leaflet(map_df) %>%
 addTiles() %>%  # Add default OpenStreetMap map tiles
-  addPolygons(color = ~qpal(`Mean domestic electricity consumption \n(kWh per meter)`),
+  addPolygons(color = ~qpal(mean_de2019),
               fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
@@
 ```
-##### Looking at cities in more detail        
+### Looking at cities in more detail
+
 ```{r Southampton LSOA dom Elec}
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
+  geom_sf(aes(fill = mean_de2019)) +
   scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
@@
 ```
+
 ```{r Portsmouth LSOA dom Elec}
@@
 ```
+
 ```{r Winchester LSOA dom Elec}
@@
 ```
-####Difference between 2010 and 2019 dom elec
-```{r Creating the difference in LSOA mean dom elec consumption variable}
-domelec_LSOA_2010 <- readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
-domelec_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv"))
-domelec_LSOA_2010$de2010 <- domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter)'
-domelec_LSOA_2019$de2019 <- domelec_LSOA_2019$'Mean domestic electricity consumption \n(kWh per meter)'
-# create unambiguous lsoa code for matching to each other and the sf geometry
-domelec_LSOA_2010$LSOA11CD <- domelec_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
-domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
 
-merged_de <- merge(domelec_LSOA_2010, domelec_LSOA_2019, by="Lower Layer Super Output Area (LSOA) Code", all=TRUE)
-names(merged_de)
-merged_de$de_diff<-as.numeric(merged_de$de2019)-as.numeric(merged_de$de2010) 
-summary(merged_de)
-```
+### Plotting the relationship between Electricty consumption and deprivation
 
-```{r Mapping the LSOA difference in mean dom elec consumption}
-# merge to sf geometry on LSOA11CD
-merged_de$LSOA11CD <- merged_de$"Lower Layer Super Output Area (LSOA) Code"
-lsoa_sf_de20102019<-merge(lsoa_sf_data, merged_de)
-ggplot2::ggplot(lsoa_sf_de20102019) +
-  geom_sf(aes(fill=de_diff))+
-  scale_fill_continuous(name="Change in Mean consumpton (kWh per meter)",low="green",high="red") +
-  labs(caption="Solent(all LSOAs)")
+To see if higher electricity use is associated with higher deprivation
 
-lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
-t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
-                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
-                         de2010, de2019, de_diff, pc_diff)
-head(arrange(t_diff, pc_diff))
-head(arrange(t_diff, -pc_diff))
-ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
-  geom_histogram()
-```
-#### Plotting the change in dom elec consumption against the deprivation score
+```{r plotting electricty consumption against deprevation}
+domelec_LSOA_2019$la_name <-domelec_LSOA_2019$`Local Authority Name`
 
-Loading deprivation data and double checking what the IMD Decile means
+solent_elec <- getSolent(domelec_LSOA_2019)
 
-```{r Loading in the Deprivation score data}
-inFile<-paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv")
-LSOAdep<-readr::read_csv(inFile)
-LSOAdep$'LSOA11CD' <- LSOAdep$'lsoa11cd'
-head(LSOAdep)
-names(LSOAdep)
+df <- merge(solent_dep, solent_elec, by = "LSOA11CD")
 
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
-                   y = IMDScore, 
+ggplot(df, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y = mean_de2019, 
                    group = IMD_Decile,
@@
   labs(x = "IMD Decile",
-       y = "IMD Score")
+       y = "Electricity use (mean kWh per meter)",
+       caption = "Solent LSOAs, 2019")
 ```
 
-NB: IMD Decile 10 has _LOWER_ mean IMD score! Which is what it says in the Excel workbok...
+With facets by LA
 
-```{r plotting change in elec usage against dep}
-LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
-names(LSOAdepelec)
-df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
-)
-
-head(df)
-Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
-                           `Local Authority Name.x` == "East Hampshire"|
-                           `Local Authority Name.x` == "Eastleigh"|
-                           `Local Authority Name.x` == "Fareham"|
-                           `Local Authority Name.x` == "Gosport"|
-                           `Local Authority Name.x` == "Hart"|
-                           `Local Authority Name.x` == "Havant"|
-                           `Local Authority Name.x` == "New Forest"|
-                           `Local Authority Name.x` == "Portsmouth"|
-                           `Local Authority Name.x` == "Rushmoor"|
-                           `Local Authority Name.x` == "Southampton"|
-                           `Local Authority Name.x` == "Test Valley"|
-                           `Local Authority Name.x` == "Winchester"|
-                           `Local Authority Name.x` == "Isle of Wight"
-                           )
-head(Solent)
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
-                   y =100*(de_diff/de2010), 
-                   group = IMD_Decile,
-                   colour = IMD_Decile)) +  
-  geom_boxplot() +
-  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
-  labs(x = "IMD Decile",
-       y = "% change Electricity")
-```
-
-Try adding facets for each Local Authority
-
-```{r addFacetsToElecDiff}
+```{r addFacetsToElecconsumption}
 # or without colour but using facets for Local Authorities
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
-                   y =100*(de_diff/de2010), 
+ggplot(df, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de2019, 
                    group = IMD_Decile)) +
@@
   labs(x = "IMD Decile",
-       y = "% change Electricty") +
-  facet_wrap(`Local Authority Name.x` ~ .)
-
-nrow(Solent)
-```
-####Map with Overlay 
-```{r Check leaflet for Change in dom elec consumption}
-library(leaflet)
-
-st_coord_sys <- st_crs(lsoa_sf_de20102019)
-st_coord_sys$epsg
-
-#Transforming the coord system
-if(st_coord_sys$epsg !=4326) {
-  map_df_trans <- st_transform(lsoa_sf_de20102019, "+proj=longlat +datum=WGS84")
-}
+       y = "Electricity use (mean kWh per meter)",
+       caption = "Solent LSOAs, 2019") +
+  facet_wrap(la_name.x ~ .)
 
 ```
+
+### Difference between 2010 and 2019 dom elec
+
+```{r Creating the difference in LSOA mean dom elec consumption variable}
+domelec_LSOA_2010 <- readr::read_csv(paste0(dataFolder,"energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2010.csv"))
+domelec_LSOA_2010$mean_de2010 <- domelec_LSOA_2010$'Mean domestic electricity consumption \n(kWh per meter)'
+
+# create unambiguous lsoa code for matching to each other and the sf geometry
+domelec_LSOA_2010$LSOA11CD <- domelec_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
+# just the vars we want
+df <- dplyr::select(domelec_LSOA_2010, LSOA11CD, mean_de2010)
+# reuse the 2019 data we already analysed
+merged_de <- merge(df, domelec_LSOA_2019, by="LSOA11CD", all=TRUE)
+#names(merged_de)
+
+merged_de$mean_de_diff <- as.numeric(merged_de$mean_de2019)-as.numeric(merged_de$mean_de2010) 
+merged_de$mean_de_diff_pc <- 100*(merged_de$mean_de_diff/merged_de$mean_de2010)
+summary(merged_de$mean_de_diff)
+summary(merged_de$mean_de_diff_pc)
+```
+
+#### Basic map
+
+```{r Mapping the LSOA difference in mean dom elec consumption}
+# merge to sf geometry on LSOA11CD
+lsoa_sf_de20102019<-merge(lsoa_sf, merged_de, by = "LSOA11CD")
+ggplot2::ggplot(lsoa_sf_de20102019) +
+  geom_sf(aes(fill=mean_de_diff))+
+  scale_fill_continuous(name="Change in Mean consumpton (kWh per meter)",low="green",high="red") +
+  labs(caption="Solent (all LSOAs)")
+
+t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
+                         LSOA11CD,
+                         mean_de2010, mean_de2019, mean_de_diff, mean_de_diff_pc)
+head(arrange(t_diff, mean_de_diff_pc))
+head(arrange(t_diff, -mean_de_diff_pc))
+ggplot2::ggplot(t_diff, aes(x = mean_de_diff_pc)) +
+  geom_histogram()
+```
+
+#### Change map with Overlay (leaflet)
+
 ```{r Plotting leaflet for change in dom elec consumption map}
-qpal <- colorNumeric("Reds", map_df_trans$de_diff, n=9)
+# merge just the variables we want to the leaflet sf
+df <- dplyr::select(merged_de, LSOA11CD, mean_de2010, mean_de2019, mean_de_diff, mean_de_diff_pc)
+lsoa_sf_leaflet <- merge(lsoa_sf_leaflet, df) # add on to the 
+#names(lsoa_sf_leaflet)
 
-leaflet(map_df_trans) %>% 
+qpal <- colorNumeric("Reds", lsoa_sf_leaflet$mean_de_diff, n=9)
+
+# we already checked & transformed the boundaries for leaflet so re-use
+leaflet(lsoa_sf_leaflet) %>% 
   addTiles() %>%  # Add default OpenStreetMap map tiles
-  addPolygons(color = ~qpal(de_diff),
+  addPolygons(color = ~qpal(mean_de_diff),
               fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD ),
@@
 
-#####Cities in more detail
+#### Cities in more detail
+
 ```{r Southampton LSOA difference in dom Elec}
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill= de_diff)) +
+  geom_sf(aes(fill= mean_de_diff)) +
   scale_fill_continuous(name = "Change in Mean consumpton (kWh per meter)", low = "green", high = "red") +
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = de_diff)) +
+  geom_sf(aes(fill = mean_de_diff)) +
   scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
@@
 
-### Mapping Gas
-####2019
+#### Plotting the change in dom elec consumption against the deprivation score
+
+```{r plotting change in elec usage against dep}
+df <- dplyr::select(merged_de, LSOA11CD, mean_de_diff, mean_de2010, mean_de2019, mean_de_diff_pc)
+LSOAdepelec <- merge(df, LSOAdep, by= "LSOA11CD")
+#names(LSOAdepelec)
+
+Solent <- getSolent(LSOAdepelec)
+head(Solent)
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y = mean_de_diff_pc, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "% change in mean kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs")
+```
+
+Try adding facets for each Local Authority
+
+```{r addFacetsToElecDiff}
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de_diff_pc, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "% change in mean kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+nrow(Solent)
+```
+
+# Mapping Gas
+
+## 2019
+
 ```{r Loading in the LSOA gas consumption data}
@@
 inFile <-paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv")
-lsoa_gasData <- readr::read_csv(inFile)
-lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
-head(lsoa_gasData)
+domgas_LSOA_2019 <- readr::read_csv(inFile)
+domgas_LSOA_2019$LSOA11CD <- domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
+
+domgas_LSOA_2019$mean_dg2019 <- domgas_LSOA_2019$`Mean consumption (kWh per meter)`
+
+head(domgas_LSOA_2019)
 ```
 
+### Basic map
+
 ```{r Mapping the gas consumption of the LSOAs}
-lsoa_merged_sf_gas <- merge(lsoa_sf_data, lsoa_gasData) #merging the boundaries and energy data
+df <- dplyr::select(domgas_LSOA_2019, LSOA11CD, mean_dg2019)
+lsoa_merged_sf_gas <- merge(lsoa_sf, df) #merging the boundaries and energy data
 ggplot2::ggplot(lsoa_merged_sf_gas) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  geom_sf(aes(fill = mean_dg2019)) +
   scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
@@
 
-###Map with Overlay
-```{r Check leaflet for dom gas consumption}
-library(leaflet)
+### Map with Overlay
 
-st_coord_sys <- st_crs(lsoa_merged_sf_gas)
-st_coord_sys$epsg
+```{r Plotting leaflet dom gas consumption}
+# re-use the df from previous chunk
+lsoa_sf_leaflet <- merge(lsoa_sf_leaflet, df, by = "LSOA11CD")
+qpal <- colorNumeric("Reds", lsoa_sf_leaflet$mean_dg2019, n=9)
 
-#Transforming the coord system
-if(st_coord_sys$epsg !=4326){
-  map_df_trans <- st_transform(lsoa_merged_sf_gas, "+proj=longlat +datum=WGS84")
-}
-```
-```{r Plotting leaflet dom gas consumption}
-qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n=9)
-
-leaflet(map_df_trans) %>%
+leaflet(lsoa_sf_leaflet) %>%
   addTiles() %>%
-  addPolygons(color= ~qpal(`Mean consumption (kWh per meter)`), 
+  addPolygons(color= ~qpal(mean_dg2019), 
               fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
@@
 
-#####Cities in More detail
+### Cities in More detail
+
 ```{r Southampton LSOA Gas}
@@
 ggplot2::ggplot(mapData) + 
-  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
+  geom_sf(aes(fill = mean_dg2019)) +
   scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
@@
 ```
+
 ```{r Winchester LSOA Gas}
@@
 ```
-####Difference between 2010 and 2019 dom gas 
+
+### Plotting  gas usage against deprivation
+
+```{r Boxplot of the gas consumption and deprevation}
+domgas_LSOA_2019$la_name <-domgas_LSOA_2019$`Local Authority Name`
+
+solent_gas <- getSolent(domgas_LSOA_2019)
+
+df <- merge(solent_dep, solent_gas, by = "LSOA11CD")
+
+ggplot(df, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y = mean_dg2019, 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "Gas Consumption")
+
+```
+
+Much more of a correlation with low deprivation (higher deciles)
+
+```{r addFacetsTogasconsumption}
+# or without colour but using facets for Local Authorities
+ggplot(df, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_dg2019, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Gas Consumption") +
+  facet_wrap(la_name.y ~ .)
+
+nrow(Solent)
+```
+
+### Difference between 2010 and 2019 dom gas
+
 ```{r Creating the dfference in LSOA dom gas consumption variable}
-#Green indicates a decrease in gas consumption from 2010 to 2019
-#Red indicates an increase in gas consumption from 2010 to 2019
-dgas_LSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2010.csv"))
-dgas_LSOA_2019 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv"))
 
-dgas_LSOA_2010$dgas2010 <- dgas_LSOA_2010$'Mean consumption (kWh per meter)'
-dgas_LSOA_2019$dgas2019 <- dgas_LSOA_2019$'Mean consumption (kWh per meter)'
-merged_dgas <- merge(dgas_LSOA_2010, dgas_LSOA_2019, by = "Lower Layer Super Output Area (LSOA) Code", all = TRUE)
-names(merged_dgas)
-merged_dgas$dg_diff<-as.numeric(merged_dgas$dgas2019) - merged_dgas$dgas2010
+domgas_LSOA_2010 <- readr::read_csv(paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2010.csv"))
+domgas_LSOA_2010$mean_dg2010 <- domgas_LSOA_2010$'Mean consumption (kWh per meter)'
+domgas_LSOA_2010$LSOA11CD <- domgas_LSOA_2010$`Lower Layer Super Output Area (LSOA) Code`
+
+df <- dplyr::select(domgas_LSOA_2010, LSOA11CD, mean_dg2010) # just the vars we need
+
+merged_dgas <- merge(domgas_LSOA_2019, df, by = "LSOA11CD", all = TRUE)
+
+#names(merged_dgas)
+merged_dgas$dg_diff<-as.numeric(merged_dgas$mean_dg2019) - merged_dgas$mean_dg2010
 summary(merged_dgas)
@@
 
+#### Plotting the change in gas usage against the deprivation
+
+```{r plotting change in gas usage against dep}
+LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
+#names(LSOAdepgas)
+df <- dplyr::select(LSOAdepgas, LSOA11CD, la_name.x, mean_dg2019, IMDScore, mean_dg2010, IMD_Decile,dg_diff
+)
+
+head(df)
+df$la_name <- df$la_name.x
+Solent <- getSolent(df)
+head(Solent)
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(dg_diff/mean_dg2010), 
+                   group = IMD_Decile,
+                   colour = IMD_Decile)) +  
+  geom_boxplot() +
+  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
+  labs(x = "IMD Decile",
+       y = "% change",
+       caption = "Mean gas kWh 2010-2019, all Solent LSOas")
+```
+
+Try adding facets for each Local Authority and remove the outlier
+
+```{r addFacetsTogasDiff}
+# or without colour but using facets for Local Authorities
+Solentex <- filter(Solent,100*(dg_diff/mean_dg2010)<50)
+ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =100*(dg_diff/mean_dg2010), 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "% change",
+       caption = "Mean gas kWh 2010-2019, all Solent LSOas") +
+  facet_wrap(la_name ~ .)
+
+nrow(Solent)
+```
+
+#### Basic change map
+
 ```{r Mapping the change in LSOA dom mean gas comsumption}
-merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
-lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
+#Green indicates a decrease in gas consumption from 2010 to 2019
+#Red indicates an increase in gas consumption from 2010 to 2019
+
+df <- dplyr::select(merged_dgas, LSOA11CD, mean_dg2010, mean_dg2019, dg_diff)
+lsoa_dgas20102019 <- merge(lsoa_sf, df, by = "LSOA11CD") #merging these
 ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
@@
 
-lsoa_dgas20102019$pc_diff <- 100*(lsoa_dgas20102019$dg_diff/lsoa_dgas20102019$dgas2010)
+lsoa_dgas20102019$pc_diff <- 100*(lsoa_dgas20102019$dg_diff/lsoa_dgas20102019$mean_dg2010)
 t_diff <-  dplyr::select(as.data.frame(lsoa_dgas20102019), 
-                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Code`,
-                         dgas2010, dgas2019, dg_diff, pc_diff)
+                         LSOA11CD, LSOA11NM,
+                         mean_dg2010, mean_dg2019, dg_diff, pc_diff)
 head(arrange(t_diff, pc_diff))
@@
 ```
-####Plotting the change in gas usage against the deprevation 
-```{r plotting change in gas usage against dep}
-LSOAdepgas <- merge(merged_dgas, LSOAdep, by= "LSOA11CD")
-names(LSOAdepgas)
-df <- dplyr::select(LSOAdepgas, LSOA11CD, "Local Authority Name.x", dg_diff, IMDScore, dgas2010, IMD_Decile
-)
 
-head(df)
-Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
-                           `Local Authority Name.x` == "East Hampshire"|
-                           `Local Authority Name.x` == "Eastleigh"|
-                           `Local Authority Name.x` == "Fareham"|
-                           `Local Authority Name.x` == "Gosport"|
-                           `Local Authority Name.x` == "Hart"|
-                           `Local Authority Name.x` == "Havant"|
-                           `Local Authority Name.x` == "New Forest"|
-                           `Local Authority Name.x` == "Portsmouth"|
-                           `Local Authority Name.x` == "Rushmoor"|
-                           `Local Authority Name.x` == "Southampton"|
-                           `Local Authority Name.x` == "Test Valley"|
-                           `Local Authority Name.x` == "Winchester"|
-                           `Local Authority Name.x` == "Isle of Wight"
-                           )
-head(Solent)
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
-                   y =100*(dg_diff/dgas2010), 
-                   group = IMD_Decile,
-                   colour = IMD_Decile)) +  
-  geom_boxplot() +
-  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
-  labs(x = "IMD Decile",
-       y = "% change Gas")
-```
+#### Change map with overlay
 
-Try adding facets for each Local Authority
+Using leaflet
 
-```{r addFacetsToElecDiff}
-# or without colour but using facets for Local Authorities
-Solentex <- filter(Solent,100*(dg_diff/dgas2010)<50)
-ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
-                   y =100*(dg_diff/dgas2010), 
-                   group = IMD_Decile)) +
-  geom_boxplot() +
-  labs(x = "IMD Decile",
-       y = "% change") +
-  facet_wrap(`Local Authority Name.x` ~ .)
+```{r Plotting leaflet for change in dom gas consumption map}
 
-nrow(Solent)
-```
+lsoa_sf_leaflet <- merge(lsoa_sf_leaflet, t_diff, by = "LSOA11CD")
 
-####Map with overlay 
-```{r Check leaflet for change i dom gas consumption}
-library(leaflet)
+qpal <- colorNumeric("Reds", lsoa_sf_leaflet$dg_diff, n=9)
 
-st_coord_sys <- st_crs(lsoa_dgas20102019)
-st_coord_sys$epsg
-
-#Transforming the coor system
-if(st_coord_sys$epsg !=4326){
-  map_df_trans <- st_transform(lsoa_dgas20102019, "+proj=longlat +datum=WGS84")
-}
-
-```
-```{r Plotting leaflet for change in dom gas consumption map}
-qpal <- colorNumeric("Reds", map_df_trans$dg_diff, n=9)
-
-leaflet(map_df_trans) %>%
+leaflet(lsoa_sf_leaflet) %>%
   addTiles() %>%
@@
 ```
-#####Cities in more detail
+
+#### Cities in more detail
+
 ```{r Southampton change in LSOA Gas}
@@
   scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Southampton")
+  labs(caption = "2010-2019, Southampton LSOAs")
 ```
@@
   scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Portsmouth")
+  labs(caption = "2010-2019, Portsmouth LSOAs")
 ```
+
 ```{r Winchester Chnage in LSOA Gas}
@@
   scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
-  labs(caption = "Winchester")
+  labs(caption = "2010-2019, Winchester LSOAs")
 ```

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Making the overlay map a bit clearer

@@
   addPolygons(color = ~qpal(mean_de_diff),
-              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD ),
+              fillOpacity = 0.6, weight = 1.6, popup = ~(LSOA11CD ),
 
                highlight = highlightOptions(
-                weight = 5,
+                weight = 6,
                 color = "#666",
-                fillOpacity = 0.7,
+                fillOpacity = 0.8,
                 bringToFront = TRUE))

### 2021-09-06 LSOA domestic Elec and Gas.Rmd
comparing absolute change with % change

--- 2021-09-03 LSOA domestic Elec and Gas.Rmd
@@
 ```
+Plot kWh change as a contrast to % change (which seems constant-ish across IMD)
+
+```{r plotkWhchange}
+# as a contrast to % change
+
+ggplot(Solent, aes(x = mean_de2010, # forces a box plot at each value 
+                   y =mean_de_diff,
+                   colour = la_name)) +
+  geom_point() +
+  geom_smooth() +
+  labs(x = "Domestic mean kWh 2010",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs")
+
+# or without colour but using facets for Local Authorities
+ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+nrow(Solent)
+```
+So there is a slightly downward trend - those in lower deprivation deciles are reducing slightly more.
 

### 2021-09-06 LSOA Deprevation.Rmd
Tweaking bits

@@
 ```
+####Map with overlay 
+```{r Check leaflet for change i dom gas consumption}
+library(leaflet)
 
+st_coord_sys <- st_crs(lsoa_multidep_merged_sf)
+st_coord_sys$epsg
+
+#Transforming the coor system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(lsoa_multidep_merged_sf, "+proj=longlat +datum=WGS84")
+}
+
+```
+```{r Plotting leaflet for change in dom gas consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$IMDScore, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%
+  addPolygons(color = ~qpal(IMDScore),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
+```{r Southampton LSOA Indices of dep}
 #####Looking at the cities in more detail
-```{r Southampton LSOA Indices of dep}
 #Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
@@
 ```
+####Map with overlay 
+```{r Check leaflet for change i dom gas consumption}
+library(leaflet)
+
+st_coord_sys <- st_crs(lsoa_imd20152019)
+st_coord_sys$epsg
+
+#Transforming the coor system
+if(st_coord_sys$epsg !=4326){
+  map_df_trans <- st_transform(lsoa_imd20152019, "+proj=longlat +datum=WGS84")
+}
+
+```
+```{r Plotting leaflet for change in dom gas consumption map}
+qpal <- colorNumeric("Reds", map_df_trans$imd_diff, n=9)
+
+leaflet(map_df_trans) %>%
+  addTiles() %>%
+  addPolygons(color = ~qpal(imd_diff),
+              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),
+
+               highlight = highlightOptions(
+                weight = 5,
+                color = "#666",
+                fillOpacity = 0.7,
+                bringToFront = TRUE))
+
+```
+
 #####Looking at the cities in more detail
@@
   labs(caption = "Southampton")
+#Histogram
+mapData$imd_diff <-100* (mapData$imd_diff/mapData$imd2015)
+t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```
@@
   labs(caption = "Portsmouth")
+#Histogram
+mapData$imd_diff <-100* (mapData$imd_diff/mapData$imd2015)
+t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```
@@
   labs(caption = "Winchester")
+#Histogram
+mapData$imd_diff <-100* (mapData$imd_diff/mapData$imd2015)
+t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
+head(arrange(t_diff, pc_diff))
+head(arrange(t_diff, -pc_diff))
+ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
+  geom_histogram()
 ```
+####Plotting the relationship between deprevation and Fuel Poverty

### 2021-09-06 LSOA domestic Elec and Gas.Rmd
added scale free plots & plotted mean kWh change for gas

--- 2021-09-03 LSOA domestic Elec and Gas.Rmd
@@
 
-Solent <- getSolent(LSOAdepelec)
-head(Solent)
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+solent_elec <- getSolent(LSOAdepelec)
+head(solent_elec)
+ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                    y = mean_de_diff_pc, 
@@
 # or without colour but using facets for Local Authorities
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                    y =mean_de_diff_pc, 
@@
 
-nrow(Solent)
+nrow(solent_elec)
 ```
+Plot kWh change as a contrast to % change (which seems constant-ish across IMD)
+
+```{r plotEleckWhchange}
+# as a contrast to % change
+
+ggplot(solent_elec, aes(x = mean_de2010, # forces a box plot at each value 
+                   y =mean_de_diff,
+                   colour = la_name)) +
+  geom_point() +
+  theme(legend.position="none") +
+  geom_smooth() +
+  labs(x = "Domestic mean kWh 2010",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs")
+
+# or without colour but using facets for Local Authorities
+# first with fixed scales
+ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+# now with 'free' scales
+ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =mean_de_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Electricity 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ . , scales = "free")
+
+nrow(solent_elec)
+```
+So there is a slightly downward trend - those in lower deprivation deciles are reducing slightly more.
 
@@
 
-nrow(Solent)
 ```
@@
 #names(LSOAdepgas)
-df <- dplyr::select(LSOAdepgas, LSOA11CD, la_name.x, mean_dg2019, IMDScore, mean_dg2010, IMD_Decile,dg_diff
+LSOAdepgas$MSOA_name <- LSOAdepgas$`MSOA Name`
+df <- dplyr::select(LSOAdepgas, la_name.x,MSOA_name, LSOA11CD,  IMD_Decile, mean_dg2019, IMDScore, mean_dg2010,mean_dg2019, dg_diff 
 )
@@
 df$la_name <- df$la_name.x
-Solent <- getSolent(df)
-head(Solent)
-ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+solent_gas <- getSolent(df)
+head(solent_gas)
+ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                    y =100*(dg_diff/mean_dg2010), 
@@
 
-Try adding facets for each Local Authority and remove the outlier
+Try adding facets for each Local Authority and remove the outlier where % change > 50
 
 ```{r addFacetsTogasDiff}
+message("Dropping:")
+filter(solent_gas,100*(dg_diff/mean_dg2010)>50)
+
 # or without colour but using facets for Local Authorities
-Solentex <- filter(Solent,100*(dg_diff/mean_dg2010)<50)
-ggplot(Solentex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+solent_gasex <- filter(solent_gas,100*(dg_diff/mean_dg2010)<50)
+ggplot(solent_gasex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                    y =100*(dg_diff/mean_dg2010), 
@@
        y = "% change",
-       caption = "Mean gas kWh 2010-2019, all Solent LSOas") +
+       caption = "Mean gas kWh 2010-2019, all Solent LSOAs with outlier removed") +
   facet_wrap(la_name ~ .)
 
-nrow(Solent)
+nrow(solent_gasex)
+```
+
+As for electricity, plot the mean kWh difference. Keep the outlier.
+
+```{r plotGaskWhchange}
+# as a contrast to % change
+
+ggplot(solent_gas, aes(x = mean_dg2010, # forces a box plot at each value 
+                   y =dg_diff,
+                   colour = la_name)) +
+  geom_point() +
+  theme(legend.position="none") +
+  geom_smooth() +
+  labs(x = "Domestic mean kWh 2010",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Gas 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =dg_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Gas 2010-2019, all Solent LSOAs")
+
+# or without colour but using facets for Local Authorities
+# first with fixed scales
+ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =dg_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Gas 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ .)
+
+# now with 'free' scales to see pattern in each LA
+ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
+                   y =dg_diff, 
+                   group = IMD_Decile)) +
+  geom_boxplot() +
+  labs(x = "IMD Decile",
+       y = "Change in mean domestic kWh per meter",
+       caption = "Gas 2010-2019, all Solent LSOAs") +
+  facet_wrap(la_name ~ ., scales = "free")
+
+nrow(solent_gas)
 ```
@@
 
-```{r Winchester Chnage in LSOA Gas}
+```{r Winchester change in LSOA Gas}
 #Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail

### 2021-09-06 LSOA domestic Elec and Gas.Rmd
fixed free to be just y axis

@@
   facet_wrap(la_name ~ .)
+```
 
+Figure \@ref(fig:freeScaleElecIMD)
+
+```{r freeScaleElecIMD, fig.cap = "freeScaleElecIMD"}
 # now with 'free' scales
@@
        caption = "Electricity 2010-2019, all Solent LSOAs") +
-  facet_wrap(la_name ~ . , scales = "free")
+  facet_wrap(la_name ~ . , scales = "free_y")
 
@@
   facet_wrap(la_name ~ .)
+```
 
+Figure \@ref(fig:freeScaleGasIMD)
+
+```{r freeScaleGasIMD, fig.cap = "freeScaleGasIMD"}
 # now with 'free' scales to see pattern in each LA
@@
        caption = "Gas 2010-2019, all Solent LSOAs") +
-  facet_wrap(la_name ~ ., scales = "free")
+  facet_wrap(la_name ~ ., scales = "free_y")
 

### 2021-09-13 mappingParishes.Rmd
added mapping parishes example (Framlingham in Suffolk)

---
title: "Mapping parishe emissions: Framlingham as an example"
author: "Ben Anderson"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # set this to FALSE if you don't want the code in the final output

# Libraries ----
# useful R libraries
library(ggplot2)
library(dplyr)
library(data.table)

# GIS libraries
library(leaflet)
library(raster)
library(sf)

# Paramaters ----

dataFolder<-"/Users/megha/Desktop/1. Uni/Masters/Project/Mapping Code/data/" # default for Meghan
user <- Sys.info()[[7]] # who are we logged in as?
if(user == "ben"){
  dataFolder <- path.expand("~/Dropbox/data/")
}

# this will not print anything out when knitted due to the include=FALSE setting in the chunk header
message("User: ", user)
message("dataFolder: ", dataFolder)

# Functions ----

selectSoton <- function(dt){
  # function we can re-use
  # assumes a data.table
  # assumes LA name = la_name (may need to make new var first)
  # returns just the rows that have Local Authority == Southampton
  select_dt <- dt[la_name %like% "Southampton"]
  return(select_dt)
}

selectSolent <- function(dt){
  # function we can re-use
  # assumes a data.table
  # assumes LA name = la_name (may need to make new var first)
  # returns just the rows that have Local Authority in Solent area
  select_dt <- dt[la_name == "Southampton" | 
                   la_name == "Portsmouth" |
                   la_name == "Winchester" |
                   la_name == "Eastleigh" |
                   la_name == "Isle of Wight" |
                   la_name == "Fareham" |
                   la_name == "Gosport" |
                   la_name == "Test Valley" |
                   la_name == "East Hampshire" |
                   la_name == "Havant" |
                   la_name == "New Forest" |
                   la_name == "Hart" |
                   la_name == "Basingstoke and Deane"]
  return(select_dt)
}

selectParish <- function(dt, parish = parish){
   # as above but selects a parish based on name
  select_dt <- dt[parncp19nm == get(parish)]
}

# Data ----
f <- "lookups/Lower_Layer_Super_Output_Area_(2011)_to_Ward_(2020)_to_LAD_(2020)_Lookup_in_England_and_Wales_V2.csv.gz"
#lsoa_lut <- data.table::fread(paste0(dataFolder, f))
lsoa_lookup <- data.table::fread(paste0(dataFolder, "lookups/lsoa_lookup.csv.gz")) # reduced version

parish_lookup <- data.table::fread(paste0(dataFolder, "lookups/Parish_to_Ward_to_Local_Authority_District__December_2020__Lookup_in_England_and_Wales.csv.gz"))

# 
```

# Intro

Focus on Framlingham (for now, intended to be gneric)

# Mapping parishes

Example: Framlingham

```{r loadParishShapefile}
#The LSOA boundaries for the Solent have been pre-downloaded
inf<-paste0(dataFolder, "EW_parishes/Parishes_and_Non_Civil_Parished_Areas_(April_2019)_EW_BGC/Parishes_and_Non_Civil_Parished_Areas_(April_2019)_EW_BGC.shp")
message ("Loading parish boundaries from file")
parish_sf_data <- sf::read_sf(inf)
names(parish_sf_data)
```

Build a simple map just to check (Figure \@ref(fig:simpleParishMap).

```{r simpleParishMap, fig.cap = "LSOA check map (shows MSOA and ward names when clicked"}

st_coord_sys <- sf::st_crs(parish_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

# transform the coord system if required
if(st_coord_sys$epsg != 4326){
 parish_sf_trans <- st_transform(parish_sf_data, "+proj=longlat +datum=WGS84")
}

fram <- dplyr::filter(parish_sf_trans, parncp19nm == "Framlingham")

leaflet(fram) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("Name ", parncp19nm,
                      "<br> LA: " ,lad19nm)
                      ), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

Build a simple map from LSOAs based on the Framlingham electoral ward just to check (Figure \@ref(fig:simpleLSOAMap).

```{r loadLSOAShapefile}
inf<-paste0(dataFolder, "/UK_census2011/Lower_Layer_Super_Output_Areas_(December_2011)_Boundaries_Generalised_Clipped_(BGC)_EW_V3-shp/Lower_Layer_Super_Output_Areas_(December_2011)_Boundaries_Generalised_Clipped_(BGC)_EW_V3.shp")
message ("Loading LSOA boundaries from file")
lsoa_sf_data <- sf::read_sf(inf)
names(lsoa_sf_data)

# merge the LSOA look-up table
df <- merge(lsoa_sf_data, lsoa_lookup, by = "LSOA11CD")

fram_lsoa_sf_data <- dplyr::filter(df, WD20NM %like% "Framlingham")

names(fram_lsoa_sf_data)
```

```{r simpleLSOAMap, fig.cap = "LSOA check map (shows MSOA and ward names when clicked"}

st_coord_sys <- sf::st_crs(fram_lsoa_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

# transform the coord system if required
if(st_coord_sys$epsg != 4326){
 fram_lsoa_sf_trans <- st_transform(fram_lsoa_sf_data, "+proj=longlat +datum=WGS84")
}

leaflet(fram_lsoa_sf_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("LSOA Name ", LSOA11NM.x,
                      "<br> LA: " ,LA11NM)
                      ), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

dplyr::select(fram_lsoa_sf_data, "LSOA11CD","LSOA11NM.x", "MSOA11CD","MSOA11NM", "WD20NM", )
```

This map suggests that two LSOAs:

 * E01030172 Suffolk Coastal 002B
 * E01030173 Suffolk Coastal 002C

Are a close match to the Framlingham civil parish shown in the first map. This will enable us to extract residential gas & electricity use.

Commercial gas & electricity use is at MSOA level. This may exceed the parish boundaries - find E02006288 (see above) and map it.

```{r loadMSOAShapefile}

inf<-paste0(dataFolder, "/UK_census2011/Middle_Layer_Super_Output_Areas__December_2011__Boundaries-shp/Middle_Layer_Super_Output_Areas__December_2011__Boundaries.shp")
message ("Loading MSOA boundaries from file")
msoa_sf_data <- sf::read_sf(inf)
names(msoa_sf_data)

fram_msoa_sf_data <- dplyr::filter(msoa_sf_data, msoa11cd == "E02006288")

names(fram_msoa_sf_data)
```

```{r simpleMSOAMap, fig.cap = "MSOA check map (shows MSOA and ward names when clicked"}

st_coord_sys <- sf::st_crs(fram_msoa_sf_data) # check coord system
st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)

# transform the coord system if required
if(st_coord_sys$epsg != 4326){
 fram_msoa_sf_trans <- st_transform(fram_msoa_sf_data, "+proj=longlat +datum=WGS84")
}

leaflet(fram_msoa_sf_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("MSOA Name ", msoa11nm)), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

Yep, way too big.

This means we can only get residential electricity & gas at LSOA level and aggregate, all other data is at MSOA or LA level. See CREDS carbon.place for LSOA emissions estimates or CSE's impact tool for parish/LA emissions - both of these use the LSOA data for 2018/19 as part of their inputs.

# Energy use

2010 & 2019 residential gas & electricity consumption data from:

 * https://www.gov.uk/government/statistics/lower-and-middle-super-output-areas-gas-consumption
 * https://www.gov.uk/government/statistics/lower-and-middle-super-output-areas-electricity-consumption

Define Framlingham by selecting the following LSOAs:

 * E01030172 Suffolk Coastal 002B
 * E01030173 Suffolk Coastal 002C

## Gas 2010

Note the 'old' local authority label.

```{r getResidentialGas2010}
gas2010_dt <- data.table::fread(paste0(dataFolder, "beis/subnationalGas/lsoaDom/LSOA_GAS_2010.csv.gz"))
gas2010_dt[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
gas2010_dt[, total_gas_kWh := `Consumption (kWh)`]
setkey(gas2010_dt, LSOA11CD)
setkey(lsoa_lookup, LSOA11CD)
gas2010_dt <- gas2010_dt[lsoa_lookup]
fram_gas2010_dt <- gas2010_dt[LSOA11CD == "E01030172" |
                        LSOA11CD == "E01030173"]

fram_gas2010_dt[, .(`LSOA Name`, LSOA11CD, WD20NM, `Number of meters`, total_gas_kWh)]

message("Framlingham: Total number of gas meters = ", sum(fram_gas2010_dt$`Number of meters`))

message("Total residential gas kWh = ", sum(fram_gas2010_dt$total_gas_kWh))
```

Using BEIS gas emissions factors for 2010 (https://www.gov.uk/government/publications/greenhouse-gas-reporting-conversion-factors-2010) doesn't help - no gas value. Use 2015 -   0.18445 kg CO2e/kWh (it's roughly constant over time in any case)

```{r residentialGasCO2e2010}
fram_gas2010_dt[, T_co2e_gas := (total_gas_kWh * 0.18445)/1000]

fram_gas2010_dt[, .(`LSOA Name`, LSOA11CD, WD20NM, `Number of meters`, total_gas_kWh, T_co2e_gas)]

message("Total T CO2e from gas  = ", sum(fram_gas2010_dt$T_co2e_gas))
```

## Electricity 2010

  BEIS CI: 0.48531 kg CO2e/kWh - very high due to use of goal.

```{r getResidentialElec2010}
elec2010_dt <- data.table::fread(paste0(dataFolder, "beis/subnationalElec/lsoaDom/LSOA_ELEC_2010.csv.gz"))
elec2010_dt[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
elec2010_dt[, total_elec_kWh := `Total domestic electricity consumption (kWh)`]
setkey(elec2010_dt, LSOA11CD)
setkey(lsoa_lookup, LSOA11CD)
elec2010_dt <- elec2010_dt[lsoa_lookup]
fram_elec2010_dt <- elec2010_dt[LSOA11CD == "E01030172" |
                        LSOA11CD == "E01030173"]

fram_elec2010_dt[, .(LSOA11NM, LSOA11CD, WD20NM, `Total number of domestic electricity meters`, total_elec_kWh)]

message("Total number of elec meters = ", sum(fram_elec2010_dt$`Total number of domestic electricity meters`))

message("Total residential elec kWh = ", sum(fram_elec2010_dt$total_elec_kWh))
```
The difference between number of gas and electricity meters more or less shows those off-gas - but there could be two electricity meters per house - e.g. anyone using Economy-7.

```{r residentialElecCO2e2010}
fram_elec2010_dt[, T_co2e_elec := (total_elec_kWh * 0.48531)/1000]

fram_elec2010_dt[, .(LSOA11NM, LSOA11CD, WD20NM, `Total number of domestic electricity meters`, total_elec_kWh, T_co2e_elec)]

s2010 <- sum(fram_elec2010_dt$T_co2e_elec)
s2021 <- (sum(fram_elec2010_dt$total_elec_kWh) *   0.21233 )/1000

message("Total T CO2e from electricity  = ", s2010)

message("Total T CO2e from this much electricity in 2021 using the most recent grid CI factor would be = ", s2021)

message("That's ", 100*round(s2021/s2010,2), " % lower.")
```

## Gas 2019 (latest data, pre-covid)

```{r getResidentialGas2019}
gas_dt <- data.table::fread(paste0(dataFolder, "beis/subnationalGas/lsoaDom/LSOA_GAS_2019.csv.gz"))
gas_dt[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
gas_dt[, total_gas_kWh := `Consumption (kWh)`]
setkey(gas_dt, LSOA11CD)
setkey(lsoa_lookup, LSOA11CD)
gas_dt <- gas_dt[lsoa_lookup]
fram_gas2019_dt <- gas_dt[LSOA11CD == "E01030172" |
                        LSOA11CD == "E01030173"]

fram_gas2019_dt[, .(`LSOA Name`, LSOA11CD, WD20NM, `Number of consuming meters`, total_gas_kWh)]

message("Total number of consuming gas meters 2019 = ", sum(fram_gas2019_dt$`Number of consuming meters`))

message("Total residential gas kWh 2019 = ", sum(fram_gas2019_dt$total_gas_kWh))
```

Using BEIS gas emissions factors for 2019 (https://www.gov.uk/government/publications/greenhouse-gas-reporting-conversion-factors-2019).

  0.18385 kg CO2e/kWh +   0.02391 (WTT)

```{r residentialGasCO2e2019}
fram_gas2019_dt[, T_co2e_gas := (total_gas_kWh * (0.18385 + 0.02391))/1000]

fram_gas2019_dt[, .(`LSOA Name`, LSOA11CD, WD20NM, `Number of consuming meters`, total_gas_kWh, T_co2e_gas)]

message("Total T CO2e from gas  = ", sum(fram_gas2019_dt$T_co2e_gas))

```

## Electricity 2019 (latest data, pre-covid)

  BEIS CI:   0.2556   kg CO2e/kWh +   0.03565  + 0.02170 (WTT + T&D)

```{r getResidentialElec2019}
elec2019_dt <- data.table::fread(paste0(dataFolder, "beis/subnationalElec/lsoaDom/LSOA_ELEC_2019.csv.gz"))
elec2019_dt[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
elec2019_dt[, total_elec_kWh := `Total domestic electricity consumption (kWh)`]
setkey(elec2019_dt, LSOA11CD)
setkey(lsoa_lookup, LSOA11CD)
elec2019_dt <- elec2019_dt[lsoa_lookup]
fram_elec2019_dt <- elec2019_dt[LSOA11CD == "E01030172" |
                        LSOA11CD == "E01030173"]

fram_elec2019_dt[, .(LSOA11NM, LSOA11CD, WD20NM, `Total number of domestic electricity meters`, total_elec_kWh)]

message("Total number of elec meters = ", sum(fram_elec2019_dt$`Total number of domestic electricity meters`))

message("Total residential elec kWh = ", sum(fram_elec2019_dt$total_elec_kWh))
```
The difference between number of gas and electricity meters more or less shows those off-gas - but there could be two electricity meters per house - e.g. anyone using Economy-7.

```{r residentialElecCO2e2019}
fram_elec2019_dt[, T_co2e_elec := (total_elec_kWh * (0.2556 + 0.03565 + 0.02170))/1000]

fram_elec2019_dt[, .(LSOA11NM, LSOA11CD, WD20NM, `Total number of domestic electricity meters`, total_elec_kWh, T_co2e_elec)]

message("Total T CO2e from electricity  = ", sum(fram_elec2019_dt$T_co2e_elec))

```

## 2010 - 2019 change

### Gas 2010-2019

```{r gasChange}

# add to 2010
fram_gas2010_dt[, year := 2010]
fram_gas2019_dt[, year := 2019]

fg_2010 <- fram_gas2010_dt[,.(LSOA11CD, LSOA11NM, WD20NM, total_gas_kWh, T_co2e_gas, nMeters = `Number of meters`, year)]
fg_2019 <- fram_gas2019_dt[ ,.(LSOA11CD, LSOA11NM, WD20NM, total_gas_kWh, T_co2e_gas, nMeters = `Number of consuming meters`, year)]
fram_gas_dt <- rbind(fg_2010, fg_2019)

ggplot2::ggplot(fram_gas_dt, aes(x = year, y = total_gas_kWh/1000, colour = LSOA11NM)) +
  geom_line() +
  geom_point() +
  labs(y = "Gas MWh")

ggplot2::ggplot(fram_gas_dt, aes(x = year, y = T_co2e_gas, colour = LSOA11NM)) +
  geom_line() +
  geom_point()

fram_gas_dt

gas_diff = sum(fram_gas2019_dt$total_gas_kWh)-sum(fram_gas2010_dt$total_gas_kWh)
pc_gas_diff <- 100*(gas_diff/sum(fram_gas2019_dt$total_gas_kWh))
message("Change in total gas use = ", gas_diff/1000 , " MWh")
message("% change in total gas use = ", round(pc_gas_diff,2), " %")

gas_Tco2e_diff = sum(fram_gas2019_dt$T_co2e_gas)-sum(fram_gas2010_dt$T_co2e_gas)
pc_gas_Tco2e_diff <- 100 * (gas_Tco2e_diff/sum(fram_gas2010_dt$T_co2e_gas))
message("% change in T CO2e from gas use = ", round(pc_gas_Tco2e_diff,2), " %")
```

### Electricity 2010-2019

```{r elecChange}

# add to 2010
fram_elec2010_dt[, year := 2010]
fram_elec2019_dt[, year := 2019]

fe_2010 <- fram_elec2010_dt[,.(LSOA11CD, LSOA11NM, WD20NM, total_elec_kWh, T_co2e_elec, nMeters = `Total number of domestic electricity meters`, year)]
fe_2019 <- fram_elec2019_dt[ ,.(LSOA11CD, LSOA11NM, WD20NM, total_elec_kWh, T_co2e_elec, nMeters = `Total number of domestic electricity meters`, year)]
fram_elec_dt <- rbind(fe_2010, fe_2019)

ggplot2::ggplot(fram_elec_dt, aes(x = year, y = total_elec_kWh/1000, colour = LSOA11NM)) +
  geom_line() +
  geom_point() +
  labs(y = "Electricity MWh")

ggplot2::ggplot(fram_elec_dt, aes(x = year, y = T_co2e_elec, colour = LSOA11NM)) +
  geom_line() +
  geom_point()

fram_elec_dt

elec_diff = sum(fram_elec2019_dt$total_elec_kWh)-sum(fram_elec2010_dt$total_elec_kWh)
pc_elec_diff <- 100*(elec_diff/sum(fram_elec2010_dt$total_elec_kWh))
message("Change in total electricity use = ", elec_diff/1000 , " MWh")
message("% change in total electricity use = ", round(pc_elec_diff,2), " %")

elec_Tco2e_diff = sum(fram_elec2019_dt$T_co2e_elec)-sum(fram_elec2010_dt$T_co2e_elec)
pc_elec_Tco2e_diff <- 100 * (elec_Tco2e_diff/sum(fram_elec2010_dt$T_co2e_elec))
message("% change in T CO2e from electricity use = ", round(pc_elec_Tco2e_diff,2), " %")
```

# The end

```{r environment}
R.Version()

```

### 2021-09-13 LSOA domestic Elec and Gas.Rmd

@@
   labs(x = "IMD Decile",
-       y = "% change",
+       y = "% change in Gas consumption",
        caption = "Mean gas kWh 2010-2019, all Solent LSOAs with outlier removed") +

### 2021-09-13 mappingParishes.Rmd
amended text & comments, reduced spurious feedback

@@
 
-Build a simple map just to check (Figure \@ref(fig:simpleParishMap).
+Build a simple map just to check the size of the parish (Figure \@ref(fig:simpleParishMap).
 
@@
 st_coord_sys <- sf::st_crs(parish_sf_data) # check coord system
-st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)
+#st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)
 
@@
 
-Build a simple map from LSOAs based on the Framlingham electoral ward just to check (Figure \@ref(fig:simpleLSOAMap).
+Npw build a simple map from LSOAs based on the Framlingham electoral ward to see how well it matches the parish (Figure \@ref(fig:simpleLSOAMap).
 
@@
 st_coord_sys <- sf::st_crs(fram_lsoa_sf_data) # check coord system
-st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)
+#st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)
 
@@
 
-Commercial gas & electricity use is at MSOA level. This may exceed the parish boundaries - find E02006288 (see above) and map it.
+Commercial gas & electricity use is at MSOA level. This may exceed the parish boundaries - find E02006288 (see above) and map it - Figure \@ref(fig:simpleMSOAMap).
 
@@
 st_coord_sys <- sf::st_crs(fram_msoa_sf_data) # check coord system
-st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)
+#st_coord_sys # current coord system EPSG: 4326 (is what leaflet wants - good)
 
@@
 Yep, way too big.
+In fact this looks much like the [Framlingham electoral ward](https://www.suffolk.gov.uk/assets/council-and-democracy/how-the-council-works/SCC-Electoral-Division-Ward-Parish-map.pdf)...
 
 This means we can only get residential electricity & gas at LSOA level and aggregate, all other data is at MSOA or LA level.
-See CREDS carbon.place for LSOA emissions estimates or CSE's impact tool for parish/LA emissions - both of these use the LSOA data for 2018/19 as part of their inputs.
+See CREDS [carbon.place](https://www.carbon.place/) for LSOA emissions estimates or CSE's impact tool for parish/LA emissions - both of these use the LSOA data for 2018/19 as part of their inputs.
 

### 2021-09-13 mappingParishes.Rmd
fixed typos & added n meters changes

@@
 
-Npw build a simple map from LSOAs based on the Framlingham electoral ward to see how well it matches the parish (Figure \@ref(fig:simpleLSOAMap).
+Now build a simple map from LSOAs based on the Framlingham electoral ward to see how well it matches the parish (Figure \@ref(fig:simpleLSOAMap).
 
@@
 
+gas_meters_diff = sum(fram_gas2019_dt$`Number of consuming meters`)-sum(fram_gas2010_dt$`Number of meters`)
+gas_meters_diff_pc <- 100*(gas_meters_diff/sum(fram_gas2010_dt$`Number of meters`))
+message("Change in number of meters = ", gas_meters_diff , " (", round(gas_meters_diff_pc)," %)")
+
 gas_diff = sum(fram_gas2019_dt$total_gas_kWh)-sum(fram_gas2010_dt$total_gas_kWh)
@@
 
+elec_meters_diff = sum(fram_elec2019_dt$`Total number of domestic electricity meters`)-sum(fram_elec2010_dt$`Total number of domestic electricity meters`)
+elec_meters_diff_pc <- 100*(elec_meters_diff/sum(fram_elec2010_dt$`Total number of domestic electricity meters`))
+message("Change in number of meters = ", elec_meters_diff , " (", round(elec_meters_diff_pc)," %) - should probably be about the same as number of gas meters until new builds with electricity only are more common")
+
 elec_diff = sum(fram_elec2019_dt$total_elec_kWh)-sum(fram_elec2010_dt$total_elec_kWh)

### 2021-09-14 mappingParishes.Rmd
added annual change plots

@@
   addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("LSOA Name ", LSOA11NM.x,
+                      "<br> LSOA code:: " ,LSOA11CD,
                       "<br> LA: " ,LA11NM)
@@
 
+```{r getAllGasFiles}
+# slightly more complex - need to load all files & select LSOAs
+getGasFiles <- function(files){
+  dt <- data.table::data.table()
+  for(f in files){
+    d <- data.table::fread(f)
+    message("Loading ", f)
+    names(d)
+    s <- strsplit(f, "_")
+    suffix <- strsplit(s[[1]][3], ".", fixed = TRUE)
+    year <- suffix[[1]][1]
+    d[, year := year]
+    # if these variable names vary by year have to set here
+    d[, total_gas_kWh := `Consumption (kWh)`]
+
+    dt <- rbind(dt,d, fill=TRUE) # prevents breakage when new var name introduced in 2016
+  }
+
+  return(dt)
+}
+
+files <- list.files(paste0(dataFolder, "beis/subnationalGas/lsoaDom"), 
+                    pattern = ".gz", full.names = TRUE)
+
+gas_allYears <- getGasFiles(files)
+
+gas_allYears[, total_nMeters := ifelse(is.na(`Number of meters`), # must be after 2014
+                                       `Number of consuming meters`, # so this is true
+                                       `Number of meters`)] # pre 2015
+
+gas_allYears[, .(nMeters = mean(`Number of meters`),
+             nConsumingMeters = mean(`Number of consuming meters`),
+             nAllMeters = mean(total_nMeters)), 
+             keyby = .(year)]
+
+names(gas_allYears)
+gas_allYears[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
+
+```
+
+```{r plotGasOverTime}
+
+fram_gas_allYears <- gas_allYears[LSOA11CD == "E01030172" |
+                        LSOA11CD == "E01030173"]
+
+ggplot2::ggplot(fram_gas_allYears, aes(x = year, y = total_nMeters, 
+                                        group = LSOA11CD,
+                                        colour = LSOA11CD)) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Total number of gas meters")
+
+ggplot2::ggplot(fram_gas_allYears, aes(x = year, y = total_gas_kWh/1000, 
+                                        group = LSOA11CD,
+                                        colour = LSOA11CD)) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Total residential gas (MWh)")
+
+ggplot2::ggplot(fram_gas_allYears, aes(x = year, y = total_gas_kWh/total_nMeters, 
+                                        group = LSOA11CD,
+                                        colour = LSOA11CD)) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Mean residential gas kWh per meter",
+       caption = "This is an indicator of increasing energy efficiency over time")
+```
+
 ### Electricity 2010-2019
@@
 
+```{r getAllElecFiles}
+# slightly more complex - need to load all files & select LSOAs
+getElecFiles <- function(files){
+  dt <- data.table::data.table()
+  for(f in files){
+    d <- data.table::fread(f)
+    message("Loading ", f)
+    names(d)
+    s <- strsplit(f, "_")
+    suffix <- strsplit(s[[1]][3], ".", fixed = TRUE)
+    year <- suffix[[1]][1]
+    d[, year := year]
+    # if these variable names vary by year have to set here
+    d[, total_elec_kWh := `Total domestic electricity consumption (kWh)`]
+    d[, total_nMeters := `Total number of domestic electricity meters`]
+    dt <- rbind(dt,d)
+  }
+
+  return(dt)
+}
+
+files <- list.files(paste0(dataFolder, "beis/subnationalElec/lsoaDom"), 
+                    pattern = ".gz", full.names = TRUE)
+
+elec_allYears <- getElecFiles(files)
+names(elec_allYears)
+elec_allYears[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
+elec_allYears[, LSOA11NM := `Lower Layer Super Output Area (LSOA) Name`]
+
+```
+
+```{r plotElecOverTime}
+
+fram_elec_allYears <- elec_allYears[LSOA11CD == "E01030172" |
+                        LSOA11CD == "E01030173"]
+
+ggplot2::ggplot(fram_elec_allYears, aes(x = year, y = total_nMeters, 
+                                        group = LSOA11CD,
+                                        colour = LSOA11CD)) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Total number of electricity meters")
+
+ggplot2::ggplot(fram_elec_allYears, aes(x = year, y = total_elec_kWh/1000, 
+                                        group = LSOA11CD,
+                                        colour = LSOA11CD)) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Total residential electricity (MWh)")
+
+ggplot2::ggplot(fram_elec_allYears, aes(x = year, y = total_elec_kWh/total_nMeters, 
+                                        group = LSOA11CD,
+                                        colour = LSOA11CD)) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Mean residential kWh per meter",
+       caption = "This is an indicator of increasing energy efficiency over time")
+```
+
 # The end

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
Error with age again elec consumption

@@
 
+```
+
+### Plotting over 65s against dom elec consumption 
+```{r Loading in the Census age data}
+inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
+census_age<-readr::read_csv (inFile)
+census_age$'LSOA11CD'<- census_age$'geography code'
+census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
+head(census_age)
+names(census_age)
+message("Original Proportion Over 65:")
+summary(census_age$`Proportion Over 65`)
+message("New prop_65m:")
+summary(census_age$prop_65m)
+```
+```{r Plotting elec consumption in the over 65s}
+#BROKEN
+#domelec_LSOA_2019$LSOA11CD <-domelec_LSOA_2019$`Local Authority Name`
+#census_age_2019elec <- merge(domelec_LSOA_2019, census_age, by= "LSOA11CD")
+#head(census_age_2019elec)
+#Select varibale we want
+#aggec_2019 <- dplyr::select(census_age_2019elec, LSOA11CD, "Local Authority Name", "Proportion Over 65", mean_de2019, prop_65m )
+#head(aggec_2019)
+
+domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Name`
+Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
+# select the variables we want for clarity
+
+de_age <- dplyr::select(Census_age_elec2019, LSOA11CD, "Local Authority Name",mean_de2019, "Proportion Over 65", prop_65m)
+head(de_age)
+# table(df$`LA Name`)
+
+de_age$la_name <- de_age$`Local Authority Name` # make a new variable with an easier name
+# select the places we want here
+getSolent <- function(df){
+  # assumes we are filtering on la_name
+  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
+                           la_name == "East Hampshire"|
+                           la_name == "Eastleigh"|
+                           la_name == "Fareham"|
+                           la_name == "Gosport"|
+                           la_name == "Hart"|
+                           la_name == "Havant"|
+                           la_name == "New Forest"|
+                           la_name == "Portsmouth"|
+                           la_name == "Rushmoor"|
+                           la_name == "Southampton"|
+                           la_name == "Test Valley"|
+                           la_name == "Winchester"|
+                           la_name == "Isle of Wight"
+                           )
+return(res)
+}
+Solent_2019 <- getSolent(de_age) # use our function to get just Solent LAs
+nrow(Solent_2019)
+ggplot(Solent_2019, aes(x= 100 * prop_65m, 
+                   y= mean_de2019, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  geom_smooth() + # adds a smoothed best fit line
+  theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "Domestic Electricity COnsumption") +
+  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
+message("Correlation coeficient across all LSOAs (2019)")
+cor(Solent_2019$prop_65m, Solent_2012$mean_de2019)
 ```
@@
 ```
+### Plotting gas usage against proportion of over 65s
+```{r Loading in the Census age data}
+inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
+census_age<-readr::read_csv (inFile)
+census_age$'LSOA11CD'<- census_age$'geography code'
+census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
+head(census_age)
+names(census_age)
+message("Original Proportion Over 65:")
+summary(census_age$`Proportion Over 65`)
+message("New prop_65m:")
+summary(census_age$prop_65m)
+```
+
+```{r Graphing over 65s against gas consumption}
+#census_age$"LSOA11CD" <- census_age$"geography code"
+domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code` <- domgas_LSOA_2019$`LSOA Code`
+
+Census_age_2012fp <- merge(domgas_LSOA_2019, census_age, by = "Lower Layer Super Output Area (LSOA) Code")
+# select the variables we want for clarity
+df_2012 <- dplyr::select(Census_age_2012fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
+head(df_2012)
+# table(df$`LA Name`)
+df_2012$la_name <- df_2012$`LA Name` # make a new variable with an easier name
+df_2012$pcFuelPoor <- df_2012$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
+# select the places we want here
+getSolent <- function(df){
+  # assumes we are filtering on la_name
+  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
+                           la_name == "East Hampshire"|
+                           la_name == "Eastleigh"|
+                           la_name == "Fareham"|
+                           la_name == "Gosport"|
+                           la_name == "Hart"|
+                           la_name == "Havant"|
+                           la_name == "New Forest"|
+                           la_name == "Portsmouth"|
+                           la_name == "Rushmoor"|
+                           la_name == "Southampton"|
+                           la_name == "Test Valley"|
+                           la_name == "Winchester"|
+                           la_name == "Isle of Wight"
+                           )
+return(res)
+}
+Solent_2012 <- getSolent(df_2012) # use our function to get just Solent LAs
+nrow(Solent_2012)
+ggplot(Solent_2012, aes(x= 100 * prop_65m, 
+                   y= pcFuelPoor, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  geom_smooth() + # adds a smoothed best fit line
+  theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "% households in fuel poverty, 2012") +
+  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
+message("Correlation coeficient across al LSOAs (2012)")
+cor(Solent_2012$prop_65m, Solent_2012$pcFuelPoor)
+```
 

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
Fixing elec over 65s graph

--- 2021-09-13 LSOA domestic Elec and Gas.Rmd
@@
 
+```
+
+### Plotting over 65s against dom elec consumption 
+```{r Loading in the Census age data}
+inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
+census_age<-readr::read_csv (inFile)
+census_age$'LSOA11CD'<- census_age$'geography code'
+census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
+head(census_age)
+names(census_age)
+message("Original Proportion Over 65:")
+summary(census_age$`Proportion Over 65`)
+message("New prop_65m:")
+summary(census_age$prop_65m)
+```
+```{r Plotting elec consumption in the over 65s}
+#BROKEN
+#domelec_LSOA_2019$LSOA11CD <-domelec_LSOA_2019$`Local Authority Name`
+#census_age_2019elec <- merge(domelec_LSOA_2019, census_age, by= "LSOA11CD")
+#head(census_age_2019elec)
+#Select varibale we want
+#aggec_2019 <- dplyr::select(census_age_2019elec, LSOA11CD, "Local Authority Name", "Proportion Over 65", mean_de2019, prop_65m )
+#head(aggec_2019)
+domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
+Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
+# select the variables we want for clarity
+
+de_age <- dplyr::select(Census_age_elec2019, LSOA11CD, "Local Authority Name",mean_de2019, "Proportion Over 65", prop_65m)
+head(de_age)
+# table(df$`LA Name`)
+
+de_age$la_name <- de_age$`Local Authority Name` # make a new variable with an easier name
+# select the places we want here
+getSolent <- function(df){
+  # assumes we are filtering on la_name
+  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
+                           la_name == "East Hampshire"|
+                           la_name == "Eastleigh"|
+                           la_name == "Fareham"|
+                           la_name == "Gosport"|
+                           la_name == "Hart"|
+                           la_name == "Havant"|
+                           la_name == "New Forest"|
+                           la_name == "Portsmouth"|
+                           la_name == "Rushmoor"|
+                           la_name == "Southampton"|
+                           la_name == "Test Valley"|
+                           la_name == "Winchester"|
+                           la_name == "Isle of Wight"
+                           )
+return(res)
+}
+Solent_2019 <- getSolent(de_age) # use our function to get just Solent LAs
+nrow(Solent_2019)
+ggplot(Solent_2019, aes(x= 100 * prop_65m, 
+                   y= mean_de2019, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  geom_smooth() + # adds a smoothed best fit line
+  theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "Domestic Electricity COnsumption") +
+  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
+message("Correlation coeficient across all LSOAs (2019)")
+cor(Solent_2019$prop_65m, Solent_2019$mean_de2019)
 ```
@@
 ```
+### Plotting gas usage against proportion of over 65s
+```{r Loading in the Census age data}
+inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
+census_age<-readr::read_csv (inFile)
+census_age$'LSOA11CD'<- census_age$'geography code'
+census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
+head(census_age)
+names(census_age)
+message("Original Proportion Over 65:")
+summary(census_age$`Proportion Over 65`)
+message("New prop_65m:")
+summary(census_age$prop_65m)
+```
+```{r Plotting gas consumption in the over 65s}
+domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
+Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
+# select the variables we want for clarity
+
+de_age <- dplyr::select(Census_age_elec2019, LSOA11CD, "Local Authority Name",mean_de2019, "Proportion Over 65", prop_65m)
+head(de_age)
+# table(df$`LA Name`)
+
+de_age$la_name <- de_age$`Local Authority Name` # make a new variable with an easier name
+# select the places we want here
+getSolent <- function(df){
+  # assumes we are filtering on la_name
+  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
+                           la_name == "East Hampshire"|
+                           la_name == "Eastleigh"|
+                           la_name == "Fareham"|
+                           la_name == "Gosport"|
+                           la_name == "Hart"|
+                           la_name == "Havant"|
+                           la_name == "New Forest"|
+                           la_name == "Portsmouth"|
+                           la_name == "Rushmoor"|
+                           la_name == "Southampton"|
+                           la_name == "Test Valley"|
+                           la_name == "Winchester"|
+                           la_name == "Isle of Wight"
+                           )
+return(res)
+}
+Solent_2019 <- getSolent(de_age) # use our function to get just Solent LAs
+nrow(Solent_2019)
+ggplot(Solent_2019, aes(x= 100 * prop_65m, 
+                   y= mean_de2019, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  geom_smooth() + # adds a smoothed best fit line
+  theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "Domestic Electricity COnsumption") +
+  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
+message("Correlation coeficient across all LSOAs (2019)")
+cor(Solent_2019$prop_65m, Solent_2019$mean_de2019)
+```
 

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
Adding age against gas consumption graph

@@
 ```{r Plotting gas consumption in the over 65s}
-domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
-Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
+domgas_LSOA_2019$LSOA11CD <- domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
+Census_age_gas2019 <- merge(domgas_LSOA_2019, census_age, by = "LSOA11CD")
 # select the variables we want for clarity
 
-de_age <- dplyr::select(Census_age_elec2019, LSOA11CD, "Local Authority Name",mean_de2019, "Proportion Over 65", prop_65m)
-head(de_age)
+dg_age <- dplyr::select(Census_age_gas2019, LSOA11CD, "Local Authority Name",mean_dg2019, "Proportion Over 65", prop_65m)
+head(dg_age)
 # table(df$`LA Name`)
 
-de_age$la_name <- de_age$`Local Authority Name` # make a new variable with an easier name
+dg_age$la_name <- dg_age$`Local Authority Name` # make a new variable with an easier name
 # select the places we want here
@@
 }
-Solent_2019 <- getSolent(de_age) # use our function to get just Solent LAs
-nrow(Solent_2019)
-ggplot(Solent_2019, aes(x= 100 * prop_65m, 
-                   y= mean_de2019, 
+Solent_2019g <- getSolent(dg_age) # use our function to get just Solent LAs
+nrow(Solent_2019g)
+ggplot(Solent_2019g, aes(x= 100 * prop_65m, 
+                   y= mean_dg2019, 
                    colour = la_name)) + # use colour for each LA
@@
   labs(x = "% aged > 65, 2011 Census",
-       y = "Domestic Electricity COnsumption") +
+       y = " Mean Domestic Gas Consumption (kWh per meter)") +
   facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
 message("Correlation coeficient across all LSOAs (2019)")
-cor(Solent_2019$prop_65m, Solent_2019$mean_de2019)
+cor(Solent_2019g$prop_65m, Solent_2019g$mean_dg2019)
 ```

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
Tweaking axis titles

@@
 ```{r Plotting elec consumption in the over 65s}
-#BROKEN
-#domelec_LSOA_2019$LSOA11CD <-domelec_LSOA_2019$`Local Authority Name`
-#census_age_2019elec <- merge(domelec_LSOA_2019, census_age, by= "LSOA11CD")
-#head(census_age_2019elec)
-#Select varibale we want
-#aggec_2019 <- dplyr::select(census_age_2019elec, LSOA11CD, "Local Authority Name", "Proportion Over 65", mean_de2019, prop_65m )
-#head(aggec_2019)
 domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
@@
   labs(x = "% aged > 65, 2011 Census",
-       y = "Domestic Electricity COnsumption") +
+       y = "Mean Domestic Electricity Consumption (kWh per meter)") +
   facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
added OAC codes to elec consumption to check against age plot

--- 2021-09-16 LSOA domestic Elec and Gas.Rmd
@@
 cor(Solent_2019$prop_65m, Solent_2019$mean_de2019)
+```
+
+```{r ageOACAndElec}
+# uses data.table for data load & matching (could be done with readr & dplyr etc)
+library(data.table)
+# you'll need this data (on sharepoint)
+oacDT <- data.table::fread(paste0(dataFolder, "oac/lsoa-oac-data.csv"))
+oacDT$la_name <- oacDT$`LA Name`
+oacDT$LSOA11CD <- oacDT$`SOA Code`
+
+solent_oacDT <- getSolent(oacDT)
+Solent_2019DT <- data.table::as.data.table(Solent_2019)
+setkey(Solent_2019DT, LSOA11CD)
+setkey(solent_oacDT, LSOA11CD)
+
+dt <- Solent_2019DT[solent_oacDT]
+
+ggplot(dt, aes(x= 100 * prop_65m, 
+                   y= mean_de2019, 
+                   colour = la_name)) + # use colour for each LA
+  geom_point() +
+  #theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "Domestic Electricity COnsumption") +
+  facet_wrap(. ~ `Supergroup Name`) # draws a separate plot for each LA (in a different colour)
 ```

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
added OAC codes to elec consumption to check against age plot

@@
 ```{r ageOACAndElec}
-# uses data.table for data load & matching (could be done with readr & dplyr etc)
-library(data.table)
+
 # you'll need this data (on sharepoint)
-oacDT <- data.table::fread(paste0(dataFolder, "oac/lsoa-oac-data.csv"))
-oacDT$la_name <- oacDT$`LA Name`
-oacDT$LSOA11CD <- oacDT$`SOA Code`
+oac_df <- readr::read_csv(paste0(dataFolder, "oac/lsoa-oac-data.csv"))
 
-solent_oacDT <- getSolent(oacDT)
-Solent_2019DT <- data.table::as.data.table(Solent_2019)
-setkey(Solent_2019DT, LSOA11CD)
-setkey(solent_oacDT, LSOA11CD)
+oac_df$la_name <- oac_df$`LA Name`
 
-dt <- Solent_2019DT[solent_oacDT]
+oac_df$LSOA11CD <- oac_df$`SOA Code`
 
-ggplot(dt, aes(x= 100 * prop_65m, 
+solent_oac_df <- getSolent(oac_df)
+
+df <- merge(Solent_2019, oac_df, by = "LSOA11CD")
+
+ggplot(df, aes(x= 100 * prop_65m, 
                    y= mean_de2019, 
-                   colour = la_name)) + # use colour for each LA
+                   colour = `LA Name`)) + # use colour for each LA
   geom_point() +

### 2021-09-17 LSOA domestic Elec and Gas.Rmd
Adding in basic plot for over 65s and electricity soncumsption fhe the whole UK for context
Adding OAC elect consumption and age graph

--- 2021-09-16 LSOA domestic Elec and Gas.Rmd
@@
 cor(Solent_2019$prop_65m, Solent_2019$mean_de2019)
+```
+
+```{r basic plot for over 65s and electricity consumption for whole UK }
+ggplot(de_age, aes(x= 100 * prop_65m, 
+                   y= mean_de2019))+ geom_point()
+```
+```{r over 65s and electricity with OAC codes}
+oac_df <- readr::read_csv(paste0(dataFolder, "oac/lsoa-oac-data.csv"))
+oac_df$la_name <- oac_df$`LA Name`
+oac_df$LSOA11CD <- oac_df$`SOA Code`
+solent_oac_df <- getSolent(oac_df)
+df <- merge(Solent_2019, oac_df, by = "LSOA11CD")
+ggplot(df, aes(x= 100 * prop_65m, 
+                   y= mean_de2019, 
+                   colour = `LA Name`)) + # use colour for each LA
+  geom_point() +
+  #theme(legend.position = "None") + # otherwise we get the colour legend at the side
+  labs(x = "% aged > 65, 2011 Census",
+       y = "Electricity Consumption (kWh per meter)") +
+  facet_wrap(. ~ `Supergroup Name`) # draws a separate plot for each LA (in a different colour)
 ```

### 2021-09-17 LSOA domestic Elec and Gas.Rmd
Knitting

@@
 > So remember: IMD Decile 1 = 10% _most_ deprived; IMD Decile 10 = 10% _least_ deprived
+
+```{r Loading in the Census age data}
+inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
+census_age<-readr::read_csv (inFile)
+census_age$'LSOA11CD'<- census_age$'geography code'
+census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
+head(census_age)
+names(census_age)
+message("Original Proportion Over 65:")
+summary(census_age$`Proportion Over 65`)
+message("New prop_65m:")
+summary(census_age$prop_65m)
+```
 
@@
 ### Plotting over 65s against dom elec consumption 
-```{r Loading in the Census age data}
-inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
-census_age<-readr::read_csv (inFile)
-census_age$'LSOA11CD'<- census_age$'geography code'
-census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
-head(census_age)
-names(census_age)
-message("Original Proportion Over 65:")
-summary(census_age$`Proportion Over 65`)
-message("New prop_65m:")
-summary(census_age$prop_65m)
-```
 ```{r Plotting elec consumption in the over 65s}
@@
 ### Plotting gas usage against proportion of over 65s
-```{r Loading in the Census age data}
-inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
-census_age<-readr::read_csv (inFile)
-census_age$'LSOA11CD'<- census_age$'geography code'
-census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
-head(census_age)
-names(census_age)
-message("Original Proportion Over 65:")
-summary(census_age$`Proportion Over 65`)
-message("New prop_65m:")
-summary(census_age$prop_65m)
-```
 ```{r Plotting gas consumption in the over 65s}

### 2021-09-17 MSOA non domestic Elec and Gas.Rmd
Trying to sort the organisation of the knit file

--- 2021-08-26 MSOA non domestic Elec and Gas.Rmd
@@
 ```
-
-# Mapping the Middle Layer Super Output Areas (MSOA)
-
+# Background Data
 ```{r Loading in the Boundary Data for the MSOA}
@@
 ```
-
-## Mapping Commercial
-### Mapping Electricty
-####2019
+# Mapping Electricty
+##2019
 ```{r Loading in the MSOA electricity consumption data for industry }
@@
 #mapping it
+mean(msoa_merged_sf_nondom$`Mean consumption (kWh per meter)`)
 ```
-####Map Overlay
+###Map Overlay
 ```{r Check leaflet for non dom elec consumption}
@@
 ```
-####Difference from 2010 to 2019
+##Difference from 2010 to 2019
 ```{r Creating the mean electricty consumption from the industrial sector MOSA}
@@
 ```
-####Map with Overlay
+###Map with Overlay
 ```{r Check leaflet for change in non dom elec consumption}
@@
 ```
-
 ```{r Mapping the percentage change in mean electricty consumption from the industrial sector MOSA}
@@
 ```
-#####Cities in more detail
+###Cities in more detail
 ```{r Southampton MSOA difference in non dom Elec}
@@
 ```
-### Mapping Gas
-####2019
+# Mapping Gas
+##2019
 ```{r Loading in the MSOA gas consumption data for industry }
@@
 
-####Mapping the difference in non domestic gas from 2010 to 2019 
+##Mapping the difference in non domestic gas from 2010 to 2019 
 ```{r Creating the difference in non domestic gas consumption in the MSOA}
@@
 ```
-####Map with Overlay
+###Map with Overlay
 ```{r Check leaflet for Change in non dom gas consumption}

### 2021-09-21 LSOA domestic Elec and Gas.Rmd
added fig width to test

--- 2021-09-16 LSOA domestic Elec and Gas.Rmd
@@
 ### Plotting over 65s against dom elec consumption
+
 ```{r Loading in the Census age data}
@@
 ```
+
 ```{r Plotting elec consumption in the over 65s}
@@
 
-```{r ageOACAndElec}
-
+```{r ageOACAndElec, fig.width=6}
 # you'll need this data (on sharepoint)
@@
 ### Plotting gas usage against proportion of over 65s
-```{r Loading in the Census age data}
-inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
-census_age<-readr::read_csv (inFile)
-census_age$'LSOA11CD'<- census_age$'geography code'
-census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
-head(census_age)
-names(census_age)
-message("Original Proportion Over 65:")
-summary(census_age$`Proportion Over 65`)
-message("New prop_65m:")
-summary(census_age$prop_65m)
-```
+
 ```{r Plotting gas consumption in the over 65s}

### 2021-11-01 R/functions.R
added rushmoor back in (beware)

@@ -16,7 +16,7 @@ getSolent <- function(df){
                             la_name == "Havant"|
                             la_name == "New Forest"|
                             la_name == "Portsmouth"|
-                            #la_name == "Rushmoor"| # northern Hampshire - not always considered part of Solent
+                            la_name == "Rushmoor"| # northern Hampshire - not always considered part of Solent
                             la_name == "Southampton"|
                             la_name == "Test Valley"|
                             la_name == "Winchester"|

### 2021-11-01 la_Summaries.R
code to draw pretty plot of LA level (carbon) emissions from BEUS data

@@ -1,0 +1,86 @@
+# uses https://data.gov.uk/dataset/723c243d-2f1a-4d27-8b61-cdb93e5b10ff/uk-local-authority-and-regional-carbon-dioxide-emissions-national-statistics-2005-to-2019
+
+library(data.table)
+library(RColorBrewer)
+library(ggplot2)
+library(plotly)
+
+params <- list()
+
+params$dataPath <- "~/Dropbox/data/beis/laCarbon/"
+
+laDT <- data.table::fread(paste0(params$dataPath, "2005-19_Local_Authority_CO2_emissions.csv"))
+
+names(laDT)
+
+head(laDT)
+
+table(laDT$`LA CO2 Sub-sector`)
+laDT[, subSectorLabel := `LA CO2 Sub-sector`]
+laDT[, subSectorLabel := ifelse(subSectorLabel == "Agriculture",
+     "Industry: Agriculture",
+     subSectorLabel)
+     ]
+laDT[, subSectorLabel := ifelse(subSectorLabel == "Large Industrial Installations",
+     "Industry: Large Industrial Installations",
+     subSectorLabel)
+]
+laDT[, subSectorLabel := ifelse(subSectorLabel == "Road Transport (A roads)",
+     "Transport: (A roads)",
+     subSectorLabel)
+]
+laDT[, subSectorLabel := ifelse(subSectorLabel == "Road Transport (Minor roads)",
+     "Transport: (Minor roads)",
+     subSectorLabel)
+]
+laDT[, subSectorLabel := ifelse(subSectorLabel == "Road Transport (Motorways)",
+     "Transport: (Motorways)",
+     subSectorLabel)
+]
+laDT[, subSectorLabel := ifelse(subSectorLabel == "Diesel Railways",
+     "Transport: Diesel Railways",
+     subSectorLabel)
+]
+table(laDT$subSectorLabel)
+
+subsetDT <- laDT[`Local Authority` %like% "Hampshire"] 
+
+nrow(subsetDT)
+
+# test
+subsetDT[, .(n = .N), keyby = .(`Local Authority`, `Calendar Year`)]
+
+# colours borrowed from https://git.soton.ac.uk/twr1m15/la_emissions_viz/-/blob/master/shiny/app.R
+# for details, use set for each sector
+industry_pal <- brewer.pal(n = 8, name = "Greys")[4:8]    # industry greys, 5 categories incl Agric
[…]

### 2021-11-01 southamptn_epcs.R
added code to skim southampton EPCs

@@ -1,0 +1,14 @@
+library(data.table)
+library(skimr)
+
+cert_DT <- data.table::fread("~/Dropbox/data/EW_epc/domestic-E06000045-Southampton/certificates.csv.gz")
+
+names(cert_DT)
+skimr::skim(cert_DT)
+
+head(cert_DT[CO2_EMISSIONS_CURRENT > 76])
+
+cert_DT <- data.table::fread("~/data/epc_EW/all-domestic-certificates/domestic-E07000244-East-Suffolk/certificates.csv")
+
+names(cert_DT)
+skimr::skim(cert_DT)
